### 2020-01-22 DataWrangling/Images extraction.Rmd
Jan22.2020

# Extract images

```{r Images to Extract}
# write.csv(NoDelft[, c(21:26)], "NoDelft.csv")
# length(unique(NoDelft$TID_OMRS))
# write.csv(MDF[, c(21:26)], "MDF.csv")
# rm(NoDelft)

######### Extraction 1000 ######
# rm(Adult_Valid, CAD3_delft,CAD6_delft, DiffNotReceived, DiffReceived, Multi_TID_60K, Multi_TID_Master, n_occur, NotReceived, QA.BGD, ReceivedValid, ReceivedValid, Master_TID_Received, ExtractLuan, Extract)
# glimpse(Master_TID_Received)

# table(Master_TID_Received$Result.Date)

ExtractBGD1000 <- MDF[order(MDF$Result.Date),]
ExtractBGD1000 <- ExtractBGD1000[!duplicated(ExtractBGD1000$TID_OMRS), ]
ExtractBGD1000 <- subset(ExtractBGD1000, !is.na(ExtractBGD1000$Xpert2Outcome_num))

summary(ExtractBGD1000$Xpert2Outcome_num)

ExtractBGD1000 <- ExtractBGD1000[30263:29264, ]
length(unique(ExtractBGD1000$TID_OMRS))

names(ExtractBGD1000)
write.csv(ExtractBGD1000[, c(1,2,23)], "ExtractBGD1000.csv")

# BGD1000 <- read_csv("BGD1000.csv")
glimpse(ExtractLuan)
length(unique(ExtractLuan$TID_OMRS))
```

### 2020-01-22 DataWrangling/Missing Received.Rmd
Jan22.2020

---
title: "Missing Received"
output: html_document
---

```{r setup, include=FALSE}
BGD8168 <- read.delim("BGD8168List.txt", header = FALSE, sep = " ")
BGD8168 <- as.data.frame(BGD8168[, 13])
colnames(BGD8168)[1] <- "TID"
QA.BGD <- as.data.frame(QA.BGD[, 1])
colnames(QA.BGD)[1] <- "TID"
QAdf2 <- rbind(BGD8168, QA.BGD)

# in delft but not in QAdf2
stillMissing <-  subset(CAD6_delft, !(CAD6_delft$TID_Delft %in% QAdf2$TID))
# in delft but not in QA.BGD
stillMissing2 <-  subset(CAD6_delft, !(CAD6_delft$TID_Delft %in% QA.BGD$TID))
# in missing but not in BGD8168 
stillMissing3 <- subset(Missing, !(Missing$TID_OMRS %in% BGD8168$TID))
length(Missing$TID_OMRS)-length(BGD8168$TID)
```

### 2020-01-22 Draft.Rmd
Jan22.2020

---
title: "Draft"
author: "Zhi Zhen Qin"
output: 
  word_document
    # reference_docx: C:/Users/zhizh/OneDrive - Stop TB Partnership/UNOPS/10 Paper Writing/CAR software/10 Manuscript/3 Nepal_Cameroon/Deep Learning CXR Compare - Submission SR_ZZ.docx

---

```{r Global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=15, fig.height=12, echo=FALSE, warning=FALSE, message=FALSE)
library(moments)
```

# Introduction
The improved theoretical understanding in AI technology, the ubiquity of large annotated datasets, and the advance in computer power have fostered a rapid expansion of the AI industry in medical diagnosis.

Until recently, the most accurate AI methods for image analysis involved painstaking feature engineering, which requires manual image pre-processing, segmenting anatomic structures, and detecting or computing features suggested by an expert. The breakthrough in the ImageNet 2012 Challenges popularized the use of deep learning in neural networks to analyse medical images. Inspired by the human nervous system, neural networks are interconnected functions, each comprised of a weight and a bias coefficient. In deep learning, the networks are trained using large sets of known positive and negative data (ground truth) in multiple hidden layers. The networks “learn” by adjusting the weights and biases of the underlying functions based on the difference between predictions and ground, a process called back-propagation. The increased computational power makes it possible for a complex deep learning network to modify itself using a large training dataset so that the resulting trained algorithms can identify new and unseen data.

These AI algorithms provide opportunities for new solutions to tackle tuberculosis (TB), a disease kills more people world-wide than any single infectious disease. Immediately identifying TB presumptives or patients is critical to prevent further spread of the infection. Chest x-ray is recommended by the World Health Organization (WHO) as a screening and triage test prior to the use of Xpert MTB/RIF. However, there is a lack of qualified radiologists who can quickly read CXR films in many high TB burden countries. Several AI companies have emerged in recent years promising to quickly screen digital chest-radiographs to identify people in need of further diagnostic testing for TB.

However, like most AI algorithms, no one knows how exactly the resulting algorithms work, not even the engineers who developed them, earning AI the “black boxes” reputation. Companies are not eager to share how exactly they built their algorithms as this is extremely valuable and it is a fiercely guarded trade secret. Often the marketed accuracy is done on the same data superset for training, testing and validation and cannot be generalized to other setting. Current scientific evidence is limited and mostly available for one product, CAD4TB (Delft Imaging Systems, Netherlands). However, significant changes have been made to the latest version (v6) of CAD4TB and it has limited publication. There is only one peer-reviewed publication on the performance of other DL systems for detecting TB abnormalities with a relatively small dataset. WHO has not made a recommendation on the use of automated reading systems for TB due to the current lack of evidence [WHO]. In response to this, we evaluated multiple DL systems available for TB screening and triage using a large dataset unseen by any AI developers to help National TB Programmes, medical professionals and patients to assess the true diagnostics accuracy of these algorithms.

# Methods

## Summary of DL Systems 
Through the network and the database of innovators developed under the TB REACH initiatives and the Accelerator for Impact project at Stop TB Partnership, we identified and contacted 15 (? TBC) DL system vendors regarding their interest in participating in the evaluation. Five AI products with stable version control were included in this study: CAD4TB (version 6), qXR (version 1) developed by Qure.ai (India), Lunit INSIGHT for Chest Radiography (Version 4.7.2) developed by Lunit (South Korea), JF CXR-1 developed by JF Healthcare (China) and InferRead®DR by Infervision (China).

We used the latest versions available of the five DL systems in this evaluation. Both CAD4TB and Lunit read DICOM (Digital Imaging and Communications in Medicine) format only, while qXR can parse digital radiographs stored in PNG and JPEG. CAD4TB detects TB-specific abnormalities and outputs continuous abnormality scores ranging from 0 to 100. The greater the abnormality score, the higher probability of having TB. Current versions of qXR and Lunit detect several discrete pulmonary abnormalities, such as calcification, cavitation, opacities etc. Both systems present the final results for TB and the specific clinical abnormalities in binary (“Yes” / “No”) using a pre-defined threshold abnormality score. The abnormality scores for Lunit and qXR range from 0 to 100%. The default threshold abnormality score can be tuned based on screening requirements. All five DL systems can generate heat maps showing abnormalities.

## Study Setting and Population
With funding from the Stop TB Partnership’s TB REACH initiative, three TB Screening Centres (SCs) were established across Dhaka with a referral network of more than 2,000 private providers and 133 NTP facilities. The TB SCs were also open to walk-in clients with no referral history. Adults (> 15 years) presenting at any of the TB SCs were consecutively enrolled and were verbally screened for the presence of TB symptoms between 15 May 2014 and 4 October 2016. After providing informed consent, each participant received a posterior-anterior CXR using digital X-ray machines (Delft EZ DR X-ray) and was asked to submit a sputum sample for a free Xpert test. Xpert test was performed again if the initial test failed (invalid, error, or no result). Demographic, symptom and medical history data were collected using OpenMRS.

A group of 3 Bangladeshi, board-certified radiologists (all with MD/MBSS degree in radiology and X,Y,Z years of experience??) read all of the CXR images remotely. The radiologists were blinded to all testing and clinical (and demographic data?? icddr,b please confirm) data and provided standard radiology reports and graded each CXR as follows (criteria to be attached): a. Highly Suggestive: including highly suggestive of TB only, b. Possibly TB: including abnormality highly suggestive of TB and possibly associated with TB, c. Any Abnormality: including abnormality highly suggestive of TB, possibly associated with TB and non-TB abnormality, d. Normal. Anyone who was unable or unwilling to acquire a CXR was referred to a nearby public-sector health facility. The 5 DL systems scored the images remotely through Secured File Transfer Protocol from the Stop TB repository except for Delft, in which case the data was shared through cloud transfer. All machine reading was performed independently with the developers blinded to all testing, clinical and demographic data.

## Data Analysis
We used bacteriologically-confirmed TB outcomes tested with Xpert MTB/RIF to evaluate the accuracy of the 5 DL systems as well the decisions of the Bangladeshi radiologists. We plotted and describe the distribution of DL systems’ abnormality scores disaggregated by Xpert status and prior history of TB. Mann-Whitney U test was used to compared non-normal distribution.

We compared the performance of the 5 DL system to that of radiologists by selecting AI scores that match the sensitivity of the certified radiologists and compared the difference in specificity. We used the McNemar test on paired proportions to test if the difference in specificity of human readers and the 5 DL systems.

We evaluated and compared the overall performance of the 5 DL systems using threshold-free measurements. In additional to the area under receiver operating characteristic (ROC) curves (AUC), which shows the tradeoff between sensitivity and specificity with varying thresholds, we also calculated and compared the area under Precision-Recall (PRC) curve (PRAUC), which shows precision values for corresponding sensitivity values and is more informative than the ROC curve when evaluating binary classifier on imbalanced datasets. [Saito 2015]. We also plotted sensitivity, specificity, and PPV with varying AI scores to understand the influence of the selection of cutoff threshold scores on programmatic performance. We plotted the proportion of Xpert saved  against sensitivity to understand the sensitivity loss as further testing is triaged

Furthermore, we divided the test set by patient age, prior TB history and referral types to evaluate the performance of the 5 DL systems in each subpopulation in terms of AUC and PRAUC.

## Ethics
All enrolled participants provided informed written consent. The study protocol was reviewed and approved by the Research Review Committee and the Ethical Review Committee at the International Centre for Diarrhoeal Disease Research, Bangladesh (icddr,b).

## Role of the AI Developers
The AI developers had no role in study design, data collection, analysis plan, or writing of the study. The developers only had access to the CXR images, and did not receive any of the demographic, symptom, medical, or testing data of the participants.

# Results

```{r Load, warning=FALSE, results='hide'}
source("Chapter/table1.R")
```

A total of `r  length(MDF$X)` people were consecutively recruited from the three TB SCs. Excluding `r sum(is.na(MDF$rad.abn)==T)` individuals without a CXR and `r sum(MDF$Age<15)` individuals aged 15 or less, a total of `r sum(MDF$Age>=15)`  individuals were included in this analysis. The median age was `r T1$Overall[2]`, and the ratio between female and male participants was `r T1$Overall[3]`. Most participants `r T1$Overall[4]`,  reported coughing more than 14 days (or any cough? icddr,b please check), `r T1$Overall[5]` reported fever, `r T1$Overall[7]` reported weight loss; about half reported shortness of breath `r T1$Overall[6]`; `r  T1$Overall[8]` reported hemoptysis; and `r T1$Overall[10]` had prior TB medication history. Almost all, `r T1$Overall[9]` had at least one TB-related symptom. There are three sources of patients: the greatest proportion of test results came from people who were referred by their private provider (n=`r T1$Overall[24]`);  `r T1$Overall[25]` were referred from NTP facilities after a negative smear; and `r T1$Overall[26]` individuals walked-in / self-presented (Table 1).

Across all referral groups,  `r T1$Overall[11]` MTB-positive TB patients were detected; the prevalence of Xpert positive TB was lowest among walk-ins: `r T1$WalkIn[11]` compared with `r T1$Private[11]` and `r T1$Public[11]` for other referral groups. Among people with MTB-positive results, `r percent(sum(MDF$RIF.Result %in% "Detected")/sum(MDF$Xpert2Outcome_num %in% "1"))` were resistant to rifampicin. The radiologists graded `r T1$Overall[27]` as Highly Suggestive, `r T1$Overall[28]` as Possibly TB, `r T1$Overall[29]` as Any Abnormality. The medians of the abnormality scores in Xpert positive groups were significantly different from those in the Xpert negative groups were (Mann-Whitney U test <0.05) for all 5 DL systems.

### Histogram

![](Results/Histogram.tif){width=900px}

The histograms of the abnormality scores of the 5 DL systems were disaggregated by Xpert outcomes and prior TB history (Figure 1). The distributions of the scores in Xpert positive group were heavily left-skewed with JF CXR-1 having the highest left skewness `r round(skewness(MDF[MDF$Xpert2Outcome_num ==1, 31]),4)` and CAD4TB having the lowest left skewness `r round(skewness(MDF[MDF$Xpert2Outcome_num ==1, 27]),4)`. As expected the distributions in Xpert negative group were right-skewed except for CAD4TB with a left skewness of `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0, 27]),4)`, and Infervision has the highest right skewness of `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0, 33]),4)`. Noticeably, there are many distinct outliers: the far right side of the JF CXR-1's distribution in the Xpert negative group (score 90-100) and qXR in the Xpert negative group (score 70-90), far left sides of Lunit's and JF CXR-1's distribution in the Xpert negative group (score 0-10). Those with TB history but Xpert negative without in generally still have a high AI scores, especially in the case of JF CXR-I (the dark red bar), which we postulated resulted from issues in the algorithms' ability to differentiate between old scarring and active lesion.

### Comparison with human readers
```{r}
source("radiologist.R")
humanAI <- read.csv("Results/HumanAI.csv")
knitr::kable(humanAI[c(1,4,7,10,13, 2,5,8,11,14, 3,6,9,12,15), ], row.names = F)

# Any abnormality
MDF$DL <- "negative"
MDF$DL[MDF$CAD4TB6>= humanAI[humanAI$human.benchmark %in% "Any Abnormality" & humanAI$DL.System %in% "CAD4TB", 5]] <- "positive"
```

If all patients with a chest x-ray graded as highly suggestive of TB by the radiologists had been tested by Xpert, the resulting sensitivity and specificity would be `r paste0(percent(Radiologist$Sens[1]), ", 95CI: (", percent(Radiologist$Sens_L[1]), " - ", percent(Radiologist$Sens_H[1]),")")` and `r paste0(percent(Radiologist$Spec[1]), ", 95CI: (", percent(Radiologist$Spec_L[1]), " - ", percent(Radiologist$Spec_H[1]),")")`. When approximate the sensitivity of this classification made by human readers, all 5 DL systems demonstrated statistically significant improvement in specificity (improvement ranging from 1.48% - 8.96%).

If radiologists' rading of "Possibly TB" had been used to triage the follow-on Xpert testing, the resulting sensitivity would be `r paste0(percent(Radiologist$Sens[2]), ", 95CI: (", percent(Radiologist$Sens_L[2]), " - ", percent(Radiologist$Sens_H[2]), ")")` and the specificity would be `r paste0(percent(Radiologist$Spec[2]), ", 95CI: (", percent(Radiologist$Spec_L[2]), " - ", percent(Radiologist$Spec_H[2]), ")")`. The matching AI classificiation by the 5 DL systems showed statistical improvement in specificty (improvement ranging from 1.34% - 7.62%).

The grading of Possibly TB" would have a sensitivity of `r paste0(percent(Radiologist$Sens[3]), ", 95CI: (", percent(Radiologist$Sens_L[3]), " - ", percent(Radiologist$Sens_H[3]), ")")` and specificity of `r paste0(percent(Radiologist$Spec[3]), ", 95CI: (", percent(Radiologist$Spec_L[3]), " - ", percent(Radiologist$Spec_H[3]), ")")`.

Compared to the the human radiologists' grading encompassing any abnormality, the AI system demonstrated a statistically significant improvement in absolute specificity of 1.2% (95% confidence interval (CI) 0.29%, 2.1%; P = 0.0096 for superiority) and an improvement in absolute sensitivity of 2.7% (95% CI −3%, 8.5%; Extended Data Table 2a).

###  ROC Curves

![](Results/Figure-2 ROCs.tif){width=900px}
The ROC graph shows that regardless of the CAD4TB cut-off value selected, the software’s performance was inferior compared to the radiologist among all referral groups. The area under the curve (AUC) for all referral groups is 0.74 (95% CI: 0.73-0.75). The CAD4TB software performed significantly better among walk-ins (AUC 0.84, 95% CI: 0.81-0.87) compared to people referred from NTP facilities (AUC 0.77, 95% CI: 0.74-0.79) and private providers (AUC 0.72, 95% CI: 0.70-0.73).

###  Precision Recall Curve (Xpert Reference) 
```{r PRC precrec, eval=F}
library(precrec)
library(ggplot2)

score <- as.list(data.frame(t(as.data.frame(matrix(MDF_long$AbnormalityScore, ncol = 24031, byrow = T)))))
label <- as.list(data.frame(t(as.data.frame(matrix(MDF_long$Xpert2Outcome_num, ncol = 24031, byrow = T)))))
# Explicitly specify model names
# msmdat <- mmdata(score, label, modnames = c("CAD4TB", "qXR", "Lunit",  "JF1", "JF2", "Infervision 1", "Infervision 2", "Infervision 3"), dsids = c(1:8))
msmdat <- mmdata(score, label, modnames = c("CAD4TB", "qXR", "Lunit",  "JF CXR-1", "Infervision 2"), dsids = c(1:5))
mmcurves <- evalmod(msmdat)
# Get a data frame with AUC scores
  attr <- attributes(evalmod(scores = MDF$CAD4TB6, labels = MDF$Xpert2Outcome_num))
  print(paste("CAD4TB= ", round(attr$auc[4],3)))
  attr <- attributes(evalmod(scores = MDF$qXRv2, labels = MDF$Xpert2Outcome_num))
  print(paste("qXR= ", round(attr$auc[4],3)))
  attr <- attributes(evalmod(scores = MDF$LunitScore, labels = MDF$Xpert2Outcome_num))
  print(paste("Lunit= ", round(attr$auc[4],3)))
  attr <- attributes(evalmod(scores = MDF$JF1, labels = MDF$Xpert2Outcome_num))
  print(paste("JF1= ", round(attr$auc[4],3)))
  attr <- attributes(evalmod(scores = MDF$IF2, labels = MDF$Xpert2Outcome_num))
  print(paste("Infervision= ", round(attr$auc[4],3)))

autoplot(mmcurves)

# autoplot(mmcurves, show_cb = TRUE)
rm(score, label)
```

![](Results/4 Curves.tif){width=900px}

### Results across age and prior TB history

![](Results/AUC plot.tif){width=900px}

We observe that the performance of XXX PRODUCTS varies across age groups. We also find that all DL systems perform worse on XXX than on, which is consistent with the decreased sensitivity of radiologists for patients... Differences in the model’s performance in benign/not benign classification is larger than in malignant/not malignant classification. We hypothesize that this is due to age and prior TB hisotry there are more abnormality on the chest or old scaring influenced the detection of active TB.

### 2020-01-22 Histogram_ROC.Rmd
Jan22.2020

```{r Global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=10, fig.height=6, echo=FALSE, warning=FALSE, message=FALSE)
```

## Methods
With funding from the Stop TB Partnership’s TB REACH initiative, three TB Screening Centres (SCs) were established across Dhaka. A Delft EZ DR X-ray system was installed in each TB SC along with multiple 4-module GeneXpert systems. A custom-built mHealth application connected to a medical record system (OpenMRS) was deployed to systematically capture demographics and symptom data from all individuals visiting the TB SCs. A referral network of more than 2,000 private providers was established, to refer clients for testing services at one of the three SCs. In addition, 133 NTP facilities were engaged to encourage referral of smear-negative individuals for Xpert testing. The TB SCs were also open to walk-in clients with no referral history.

Adults (> 15 years) presenting at any of the TB SCs were verbally screened for the presence of TB symptoms. Regardless of the CAD4TB abnormality score, symptomatic individuals were asked to submit a sputum sample for a free Xpert test. If the Xpert test failed (invalid, error, or no result), it was performed again to obtain a valid outcome if enough sample remained. A Bangladeshi, board-certified radiologist with 10 years of experience read all of the CXR images offsite. The radiologist was blinded to both the CAD4TB score and the Xpert result. CXRs were graded as normal or abnormal. The radiologist provided a standard radiology report to guide clinical care. Anyone who was unable or unwilling to pay for the CXR was referred to a nearby public-sector health facility.

```{r Load, results='hide'}
source("DataWrangling/GlobalOption.R")

# MDF <- subset(MDF, MDF$Age > 15)
library(tableone)

# Define numeric variables
listVar <- c("Age", "Gender", "Cough", "Fever", "Active.Breathing.Shortness", "Weight.Loss","Haemoptysis", "Symptoms", "TB.Medication.History", "Xpert2Outcome_num", "MTB.Burden", "RIF.Result", "Referral", "rad.highly.TB", "rad.TB", "rad.abn", "CAD4TB6", "qXRv2", "LunitScore", "JF1", "IF1", "IF2")

#Define categorical variables
catVars <- c( "Gender", "Cough", "Fever", "Active.Breathing.Shortness", "Weight.Loss","Haemoptysis", "Symptoms", "TB.Medication.History", "Xpert2Outcome_num", "MTB.Burden", "RIF.Result", "Referral", "rad.highly.TB", "rad.TB", "rad.abn")

table1 <- CreateTableOne(vars = listVar, strata=c("Xpert2Outcome_num"), data = MDF, factorVars = catVars)
table1.all <- CreateTableOne(vars = listVar, data = MDF, factorVars = catVars)

table1 <- print(table1, nonnormal = c("Age", "CAD4TB6", "qXRv2", "LunitScore", "JF1", "IF1", "IF2"), cramVars = "Gender", catDigits = 1, contDigits = 1, noSpaces = TRUE)
table1all <- print(table1.all, nonnormal = c("Age","CAD4TB6", "qXRv2", "LunitScore", "JF1", "IF1", "IF2"), cramVars = "Gender", catDigits = 1, contDigits = 1, noSpaces = TRUE)

```

```{r Table 1}
table1DF <- data.frame(columnNameILike = row.names(table1), table1)
table1allDF <- data.frame(columnNameILike = row.names(table1all), table1all)
T1 <- cbind(table1DF, table1allDF)
T1 <- T1[, c(1, 3, 2, 4, 7)]
colnames(T1) <- c("", "Xpert Positive", "Xpert Negative", "p test", "Overall")

TEMP <- scan(text = "n,Age (median [IQR]),Gender = F/M (%),Cough = Yes (%),Fever = Yes (%),Short of breath = Yes (%),Weight Loss = Yes (%),Haemoptysis = Yes (%),Any symptom(s) = Yes (%),TB History = Yes (%),Xpert positive (%),MTB Burden (%),   ,   High,   Low,   Medium,   Very Low,RIF Result (%),   ,   Detected,   Indeterminate,   Not Detected,Referral Type(%),   Private Provider,   Public DOTS Facilities,   Walk-in,Radiologist = Highly suggestive of TB (%),Radiologist = Possibly TB (%),Radiologist = Any abnormality (%),CAD4TB (median [IQR]),qXR (median [IQR]),Lunit (median [IQR]),JF1 (median [IQR]), IF1, IF2", sep = ",", what = "")

# TEMP <- scan(text = "n,Age (median [IQR]),Gender = F/M (%),Cough = Yes (%),Fever = Yes (%),Short of breath = Yes (%),Weight Loss = Yes (%),Haemoptysis = Yes (%),TB History = Yes (%),Xpert positive (%),MTB Burden (%),   ,   High,   Low,   Medium,   Very Low,RIF Result (%),   ,   Detected,   Indeterminate,   Not Detected,Referral Type(%),   Private Provider,   Public DOTS Facilities,   Walk-in,Radiologist = Highly suggestive of TB (%),Radiologist = Possibly TB (%),Radiologist = Any abnormality (%),CAD4TB (median [IQR]),qXR (median [IQR]),Lunit (median [IQR]),JF1 (median [IQR]), IF1, IF2", sep = ",", what = "")

T1$N <- TEMP
T1 <- T1[, c(6, 2:5)]
rm(TEMP)
write.csv(T1, "Results/Table 1.csv", row.names = FALSE)

knitr::kable(T1, row.names = FALSE, caption = "Table 1 Demographic and Clinical Characteristics of People Screened with Chest X-ray and Xpert MTB/RIF")

rm(table1.all, table1all, table1allDF, table1, table1DF, listVar, catVars)
```

### Results
Between March 2014 and December 2016, a total of `r  length(MDF$X)` people were consecutively recruited from the three TB SCs. There were `r sum(is.na(MDF$rad.abn)==T)` individuals not able to obtain a  CXR. Further excluding `r sum(MDF$Age<15)` individuals aged 15 or less from the analysis, a total of `r sum(MDF$Age>=15)`  individuals were enrolled in the study.

The median age of the rest were `r T1$Overall[2]`, the ratio between female and male participants was `r T1$Overall[3]`. Most participants `r T1$Overall[4]`,  reported coughing more than 14 days (or any cough? icddr,b please check), `r T1$Overall[5]` reported fever, `r T1$Overall[7]` reported weight loss; about half reported short of breath `r T1$Overall[6]`; `r  T1$Overall[8]` reported hemoptysis. Almost all, `r T1$Overall[9]` had at least one TB-related symptom.

There are three sources of patients: the greatest proportion of test results came from people who were referred by their private provider (n=`r T1$Overall[24]`);  `r T1$Overall[25]` were referred from NTP facilities after a negative smear; and `r T1$Overall[26]` individual were walked-in / self-present (Table 1).

#### Histogram 
```{r Histogram, fig.width=8, fig.height=5,}
p <- ggplot(MDF_long,aes(x=AbnormalityScore, fill=Xpert2Outcome_num))+ geom_histogram(position = 'stack', alpha=0.5, breaks=seq(0,100, by=5), aes(y = ..density.., fill = Xpert2Outcome_num)) + xlab("Abnormality Scores of the Deep Learning Systems") + scale_fill_discrete(name ="", labels = c("Xpert Negative", "Xpert Positive"))
hist <- p + facet_wrap(~DeepLearningSystem) + theme_minimal() + theme(legend.position = "bottom")+ scale_color_brewer(palette="Accent")

tiff("Results/Histogram.tif", width = 14, height = 8, units = "in", res = 100)
hist
dev.off()

library(moments)
# skewness(MDF[MDF$Xpert2Outcome_num ==1, 28]) 
# skewness(MDF[MDF$Xpert2Outcome_num ==1, 29]) 
# skewness(MDF[MDF$Xpert2Outcome_num ==1, 30])
# 
# skewness(MDF[MDF$Xpert2Outcome_num ==0, 28]) 
# skewness(MDF[MDF$Xpert2Outcome_num ==0, 29]) 
# skewness(MDF[MDF$Xpert2Outcome_num ==0, 30])
hist
```

###  ROC (Xpert Reference) 
```{r ROC}
source("radiologist.R")

CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE.csv")
CAD_Xpert_plot <- CAD_Xpert_plot[, -1]
# CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% "Lunit", ]

roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, MDF)
roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv2_100, MDF)
roc_Lunit <- ci.auc(Xpert2Outcome_num ~ LunitScore_100, MDF)
roc_JF1 <- ci.auc(Xpert2Outcome_num ~ JF1_100, MDF)
roc_JF2 <- ci.auc(Xpert2Outcome_num ~ JF2_100, MDF)
roc_IF1 <- ci.auc(Xpert2Outcome_num ~ IF1_100, MDF)
roc_IF2 <- ci.auc(Xpert2Outcome_num ~ IF2_100, MDF)

# base <- ggplot(CAD_Xpert_plot, aes(X, Sens, color = DeepLearningSystem)) + geom_path()+ geom_ribbon(aes(x = X, ymin = Sens_L, ymax = Sens_H), fill = "red", alpha= 0.2)

base <- ggplot(CAD_Xpert_plot, aes(X, Sens)) + geom_path(aes(color = DeepLearningSystem)) + 
  geom_ribbon(aes(x = X, ymin = Sens_L, ymax = Sens_H, color = DeepLearningSystem), fill = "steelblue", alpha= 0.2)

ggROC <- base + theme_minimal() + geom_abline(slope=1, intercept = 0, linetype = "dashed", alpha=0.7, color = "grey") + coord_equal()+ annotate("text", x = .75, y = .15, 
            label = paste(" CAD4TB: ", round(roc_CAD6[2],2), " (95% CI:", round(roc_CAD6[1],2), "-", round(roc_CAD6[3],2), ")", "\n",
      "Lunit: ", round(roc_Lunit[2],2), " (95% CI:", round(roc_Lunit[1],2), "-", round(roc_Lunit[3],2), ")", "\n",
      "JF1: ", round(roc_JF1[2],2), " (95% CI:", round(roc_JF1[1],2), "-", round(roc_JF1[3],2), ")", "\n",
       "JF2: ", round(roc_JF2[2],2), " (95% CI:", round(roc_JF2[1],2), "-", round(roc_JF2[3],2), ")", "\n",
       "IF1: ", round(roc_IF1[2],2), " (95% CI:", round(roc_IF1[1],2), "-", round(roc_IF1[3],2), ")", "\n",
       "IF2: ", round(roc_IF2[2],2), " (95% CI:", round(roc_IF2[1],2), "-", round(roc_IF2[3],2), ")", "\n",
      "qXR: ", round(roc_qure[2],2), " (95% CI:", round(roc_qure[1],2), "-", round(roc_qure[3],2), ")", "\n", sep = ""), size = 3) +
  labs(x = "1-Specificity", y= "Sensitivity", subtitle = paste0("Figure X: The ROC curves of CAD4TB (v6), JF (v1) and qXR (v2) using Xpert results as the reference (n=", length(MDF$PID_OMRS), ")"))

ggROC <- ggROC + geom_point(data = Radiologist, mapping = aes(X, Sens, shape = RadiologistCategory)) 
# + geom_ribbon(Radiologist, aes(x=X, ymin = Sens_L, ymax = Sens_H), fill = "red", alpha = 0.2)

tiff("Results/Figure-2 ROCs.tif", width = 10, height = 7.9, units = "in", res = 100)
ggROC
dev.off()

ggROC1 <- ggROC + coord_cartesian(xlim = c(0.1, 0.5), ylim = c(0.90, 1) ) +
  ggtitle("Figure 2b: Zoomed-in view of the square marked part of Fig. 2a")+theme_light()

tiff("Results/Figure-2 Zoomed-in.tif", width = 12, height = 4, units = "in", res = 100)
ggROC1
dev.off()
ggROC
ggROC1

rm(ggROC, ggROC1, Highly, hist, accuracy, accuracy_both, Any, base, CAD_Xpert_select, CAD_Xpert, Probably, mylist, rval, table1, table1.all, roc_CAD6, roc_JF1, roc_JF2, roc_qure, roc_Lunit)
```

###  Precision Recall Curve (Xpert Reference) 
```{r PR Curve}
CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% "JF2", ]

# roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, MDF)
# roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv2_100, MDF)
# roc_Lunit <- ci.auc(Xpert2Outcome_num ~ LunitScore_100, MDF)
# roc_JF1 <- ci.auc(Xpert2Outcome_num ~ JF1_100, MDF)
# roc_JF2 <- ci.auc(Xpert2Outcome_num ~ JF2_100, MDF)
#

# base <- ggplot(CAD_Xpert_plot, aes(X, Sens, color = DeepLearningSystem)) + geom_path()+ geom_ribbon(aes(x = X, ymin = Sens_L, ymax = Sens_H), fill = "red", alpha= 0.2)

base <- ggplot(CAD_Xpert_plot, aes(Sens, ppv)) + geom_path(aes(color = DeepLearningSystem)) + geom_ribbon(aes(x = Sens, ymin = PPV_L, ymax = PPV_H, color = DeepLearningSystem), fill = "steelblue", alpha= 0.2)

PRCurve <- base + theme_minimal() + geom_abline(slope=1, intercept = 0, linetype = "dashed", alpha=0.7, color = "grey") + coord_equal()
# + annotate("text", x = .75, y = .15, 
#             label = paste(" CAD4TB: ", round(roc_CAD6[2],2), " (95% CI:", round(roc_CAD6[1],2), "-", round(roc_CAD6[3],2), ")", "\n",
#       "Lunit: ", round(roc_Lunit[2],2), " (95% CI:", round(roc_Lunit[1],2), "-", round(roc_Lunit[3],2), ")", "\n",
#       "JF1: ", round(roc_JF1[2],2), " (95% CI:", round(roc_JF1[1],2), "-", round(roc_JF1[3],2), ")", "\n",
#        "JF2: ", round(roc_JF2[2],2), " (95% CI:", round(roc_JF2[1],2), "-", round(roc_JF2[3],2), ")", "\n",
#       "qXR: ", round(roc_qure[2],2), " (95% CI:", round(roc_qure[1],2), "-", round(roc_qure[3],2), ")", "\n", sep = ""), size = 3) +
#   labs(x = "1-Specificity", y= "Sensitivity", subtitle = "Figure X: The ROC curves of CAD4TB (v6), JF (v1) and qXR (v2) using Xpert results as the reference (n=23,618)")

# ggROC <- ggROC + geom_point(data = Radiologist, mapping = aes(X, Sens, shape = RadiologistCategory)) 
# + geom_ribbon(Radiologist, aes(x=X, ymin = Sens_L, ymax = Sens_H), fill = "red", alpha = 0.2)

tiff("Results/Figure-3 PR Curves.tif", width = 10, height = 7.9, units = "in", res = 100)
PRCurve
dev.off()

```

### 2020-01-22 ROCs.Rmd
Jan22.2020

```{r Global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=10, fig.height=6, echo=FALSE, warning=FALSE, message=FALSE)

Sys.setenv(LANG = "en")
library(ggplot2)
library(scales)
library(epiR)
library(ggthemes)
library(RColorBrewer)
library(plyr)
library(reshape2)
library(pROC)
library(tidyverse)
library(dplyr)
library(lubridate)
library(readxl)
library(plotROC)
library(flextable)

# as.numeric.factor <- function(x) {as.numeric(levels(x))[x]}
```

```{r}
Adult_Valid <- read_csv('Adult_Valid.csv')
```

### Histogram 
```{r Histogram, fig.width=8, fig.height=5,}
# make it long
Adult_Valid$qXRv2_100 <- Adult_Valid$qXRv2*100

Adult_Valid_long <- gather(Adult_Valid, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv2_100)

# p <- ggplot(Adult_Valid,aes(CAD4TB6))
# p <- ggplot(Adult_Valid,aes(qXRv2))
# p <- ggplot(Adult_Valid,aes(DrCADxScore))

Adult_Valid_long$Xpert2Outcome_num <- as.factor(Adult_Valid_long$Xpert2Outcome_num)

p <- ggplot(Adult_Valid_long,aes(x=AbnormalityScore, fill=Xpert2Outcome_num))+ geom_histogram(position = 'identity', alpha=0.5, binwidth = 10, aes(y = ..density.., fill = Xpert2Outcome_num)) + xlab("Abnormality Scores of the Deep Learning Systems") + scale_fill_discrete(name ="", labels = c("Xpert Negative", "Xpert Positive"))
p + facet_wrap(~DeepLearningSystem) + theme_minimal() + theme(legend.position = "bottom")+ scale_color_brewer(palette="Accent")

# p + facet_grid(Country ~ DeepLearningSystem, switch = "both") + theme_minimal() + theme(legend.position = "bottom")

# ggplot(Adult_Valid_long, aes(x=DL.Score, fill=DL.System)) + geom_histogram(position = 'identity', alpha = 0.5, bindwidth = 10, aes(y=..density.., fill=DL.System))

# density plot
# ggplot(Adult_Valid_long,aes(x=DL.Score, fill=Xpert2Outcome_num))+ geom_density(position = 'identity', alpha=0.5, binwidth = 10)

# pooled 
# p + geom_histogram(position = 'identity', alpha=0.5, aes(y = ..density.., fill = Xpert2Outcome_num), bins = 20) + stat_density(position = 'identity',aes(colour = Xpert2Outcome_num)) # Pooled

# library(moments)
# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==1, 28]) #28 CAD4TB6, 29 qXRv2, 33 Lunit
# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==1, 29]) #29 qXRv2, 33 Lunit
# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==1, 33]) #33 Lunit
# 
# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==0, 28]) #28 CAD4TB6, 29 qXRv2, 33 Lunit
# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==0, 29]) #29 qXRv2, 33 Lunit
# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==0, 33]) #33 Lunit

```

###  Multi-ROC (Xpert Reference) 
```{r Multi-ROC_All_Xpert}
# make it long
Adult_Valid$qXRv2_100 <- Adult_Valid$qXRv2*100

Adult_Valid_long <- gather(Adult_Valid, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv2_100)

############# Pooled ###############
roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, Adult_Valid)
roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv2_100, Adult_Valid)
# roc_Lunit <- ci.auc(Xpert2Outcome_num ~ Lunit, Adult_Valid)
# Adult_Valid_long$DeepLearningSystem[Adult_Valid_long$DeepLearningSystem %in% "Lunit_100"] <- "Lunit"

Adult_Valid_long$DeepLearningSystem[Adult_Valid_long$DeepLearningSystem %in% "CAD4TB6"] <- "CAD4TB"
Adult_Valid_long$DeepLearningSystem[Adult_Valid_long$DeepLearningSystem %in% "qXRv2_100"] <- "qXR"

Adult_Valid_long$DeepLearningSystem <- as.factor(Adult_Valid_long$DeepLearningSystem)

# Multi-ROC
ggROC <- ggplot(Adult_Valid_long, aes(d = Xpert2Outcome_num, m = AbnormalityScore, color = DeepLearningSystem)) + geom_roc(cutoffs.at = c(10,20,30,40,50,60,70,80,90)) + style_roc(xlab = "1 - Specificity", ylab = "Sensitivity")

ggROC <- ggROC + annotate("text", x = .75, y = .15, 
            label = paste(" CAD4TB: ", round(roc_CAD6[2],2), " (95% CI:", round(roc_CAD6[1],2), "-", round(roc_CAD6[3],2), ")", "\n",
      # "Lunit: ", round(roc_Lunit[2],2), " (95% CI:", round(roc_Lunit[1],2), "-", round(roc_Lunit[3],2), ")", "\n",
      "qXR: ", round(roc_qure[2],2), " (95% CI:", round(roc_qure[1],2), "-", round(roc_qure[3],2), ")", "\n", sep = ""), size = 4.5)+
  ggtitle("The ROC curves of CAD4TB (v6) and qXR (v2) using Xpert results as the reference (n=18682)")

ggROC
ggROC1 <- ggROC + coord_cartesian(xlim = c(0.1, 0.4), ylim = c(0.90, 1) ) +
  ggtitle("Figure 2b: Zoomed-in view of the square marked part of Fig. 2a")+theme_light()
ggROC1

# plot_interactive_roc(ggROC, width =12, height = 9.5)
# plot_interactive_roc(ggROC1, width =12, height = 4)
```

### Radiologist Accuracy (highly)
```{r Accuracy of Radiologist1}
TP <- sum(Adult_Valid$raiolgogy_highly %in% "1" & Adult_Valid$Xpert2Outcome_num==1)
FP <- sum(Adult_Valid$raiolgogy_highly %in% 1 & Adult_Valid$Xpert2Outcome_num==0)
TN <- sum(Adult_Valid$raiolgogy_highly %in% 0 & Adult_Valid$Xpert2Outcome_num==0)
FN <- sum(Adult_Valid$raiolgogy_highly %in% 0 & Adult_Valid$Xpert2Outcome_num==1)

dat <- as.table(matrix(c(TP, FP, FN, TN), nrow=2, byrow=TRUE))
colnames(dat) <- c("Xpert+","Xpert-")
rownames(dat) <- c("CXR+","CXR-")
rval <- epi.tests(dat, conf.level = 0.95)
rval
# print(rval$elements[c(47, 43,39,35)] ) 
rm(TP, FP, TN, FN)
```

### Radiologist Accuracy (possible)
```{r Accuracy of Radiologist2}
TP <- sum(Adult_Valid$raiolgogy_possible %in% "1" & Adult_Valid$Xpert2Outcome_num==1)
FP <- sum(Adult_Valid$raiolgogy_possible %in% 1 & Adult_Valid$Xpert2Outcome_num==0)
TN <- sum(Adult_Valid$raiolgogy_possible %in% 0 & Adult_Valid$Xpert2Outcome_num==0)
FN <- sum(Adult_Valid$raiolgogy_possible %in% 0 & Adult_Valid$Xpert2Outcome_num==1)

dat <- as.table(matrix(c(TP, FP, FN, TN), nrow=2, byrow=TRUE))
colnames(dat) <- c("Xpert+","Xpert-")
rownames(dat) <- c("CXR+","CXR-")
rval <- epi.tests(dat, conf.level = 0.95)
rval
# print(rval$elements[c(47, 43,39,35)] ) 
rm(TP, FP, TN, FN)
```

### Radiologist Accuracy (any abnormality)
```{r Accuracy of Radiologist3}
TP <- sum(Adult_Valid$any_abnormality %in% "1" & Adult_Valid$Xpert2Outcome_num==1)
FP <- sum(Adult_Valid$any_abnormality %in% 1 & Adult_Valid$Xpert2Outcome_num==0)
TN <- sum(Adult_Valid$any_abnormality %in% 0 & Adult_Valid$Xpert2Outcome_num==0)
FN <- sum(Adult_Valid$any_abnormality %in% 0 & Adult_Valid$Xpert2Outcome_num==1)

dat <- as.table(matrix(c(TP, FP, FN, TN), nrow=2, byrow=TRUE))
colnames(dat) <- c("Xpert+","Xpert-")
rownames(dat) <- c("CXR+","CXR-")
rval <- epi.tests(dat, conf.level = 0.95)
rval
# print(rval$elements[c(47, 43,39,35)] ) 
rm(TP, FP, TN, FN)
```

## Cutoff Table (Full)
```{r cutoff table}
###### Qure.AI Score by 0.01 #########
qure_ai_score <- seq(0.01,1, by = 0.01)

mylist <- NULL
mylist <- as.list(mylist)

for (i in 1:100){
myfunction <- function(CountryX, car.cutoff){
a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
colnames(dat) <- c("Dis+","Dis-")
rownames(dat) <- c("Test+","Test-")
rval <- epi.tests(dat, conf.level = 0.95)
sensitivity <- as.vector(round((rval$elements$sensitivity),2)) 
specificity <- as.vector(round((rval$elements$specificity),2))
pv.positive <- as.vector(round((rval$elements$pv.positive),2))
pv.negative <- as.vector(round((rval$elements$pv.negative),2))
correct.rate <- round((a+d)/length(CountryX$Xpert2Outcome_num), 2)

perc_above_CAR_Score<- sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
Score <- qure_ai_score[i]

accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_above_CAR_Score, Score, correct.rate)

return(accuracy)
}

accuracy <- myfunction(Adult_Valid, qure_ai_score[i])
mylist[[i]] <- list(accuracy)

}

QureDF_both <- data.frame(matrix(unlist(mylist), nrow=100, byrow=T))
QureDF_both$Country <- paste("Pooled")

QureDF <- QureDF_both
QureDF$Sen_95CI <- paste(QureDF[, 2], "-", QureDF[, 3], sep = "")
QureDF$Spe_95CI <- paste(QureDF[, 5], "-", QureDF[, 6], sep = "")
QureDF$PPV_95CI <- paste(QureDF[, 8], "-", QureDF[, 9], sep = "")
QureDF$NPV_95CI <- paste(QureDF[, 11], "-", QureDF[, 12], sep = "")
QureDF$CAD_System <- paste("qXR")
# write.csv(QureDF, "qure.ai by 0.01.csv")
# rm(qure_ai_score)

#### CAD6 Score by 1 ######
CAD6 <- seq(1,99, by = 1)

mylist <- NULL
mylist <- as.list(mylist)

for (i in 1:99){
myfunction <- function(CountryX, car.cutoff){
a <- sum(CountryX$CAD4TB6 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
b <- sum(CountryX$CAD4TB6 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
c <- sum(CountryX$CAD4TB6 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
d <- sum(CountryX$CAD4TB6 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
colnames(dat) <- c("Dis+","Dis-")
rownames(dat) <- c("Test+","Test-")
rval <- epi.tests(dat, conf.level = 0.95)
sensitivity <- as.vector(round((rval$elements$sensitivity),2))
specificity <- as.vector(round((rval$elements$specificity),2))
pv.positive <- as.vector(round((rval$elements$pv.positive),2))
pv.negative <- as.vector(round((rval$elements$pv.negative),2))
correct.rate <- round((a+d)/length(CountryX$Xpert2Outcome_num), 2)

perc_above_CAR_Score<- sum(CountryX$CAD4TB6 >= car.cutoff)/length(CountryX$TID_OMRS)
Score <- CAD6[i]

accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_above_CAR_Score, Score, correct.rate)

return(accuracy)
}

accuracy_both <- myfunction(Adult_Valid, CAD6[i])
mylist[[i]] <- list(accuracy_both)
}
CAD6DF_both <- data.frame(matrix(unlist(mylist), nrow=99, byrow=T))
CAD6DF_both$Country <- paste("Pooled")

CAD6DF <- CAD6DF_both
CAD6DF$Sen_95CI <- paste(CAD6DF[, 2], "-", CAD6DF[, 3], sep = "")
CAD6DF$Spe_95CI <- paste(CAD6DF[, 5], "-", CAD6DF[, 6], sep = "")
CAD6DF$PPV_95CI <- paste(CAD6DF[, 8], "-", CAD6DF[, 9], sep = "")
CAD6DF$NPV_95CI <- paste(CAD6DF[, 11], "-", CAD6DF[, 12], sep = "")
CAD6DF$CAD_System <- paste("CAD4TB")

# #### Lunit Score by 0.01  ######
# Lunit <- seq(0,1, by = 0.01)
# 
# mylist <- NULL
# mylist <- as.list(mylist)
# 
# for (i in 1:101){
# myfunction <- function(CountryX, car.cutoff){
# a <- sum(CountryX$Lunit >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
# b <- sum(CountryX$Lunit >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
# c <- sum(CountryX$Lunit < car.cutoff & CountryX$Xpert2Outcome_num =="1")
# d <- sum(CountryX$Lunit < car.cutoff & CountryX$Xpert2Outcome_num =="0")
# dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
# colnames(dat) <- c("Dis+","Dis-")
# rownames(dat) <- c("Test+","Test-")
# rval <- epi.tests(dat, conf.level = 0.95)
# sensitivity <- as.vector(round((rval$elements$sensitivity),2))
# specificity <- as.vector(round((rval$elements$specificity),2))
# pv.positive <- as.vector(round((rval$elements$pv.positive),2))
# pv.negative <- as.vector(round((rval$elements$pv.negative),2))
# correct.rate <- round((a+d)/length(CountryX$Xpert2Outcome_num), 2)
# 
# 
# perc_above_CAR_Score<- sum(CountryX$Lunit >= car.cutoff)/length(CountryX$TID_OMRS)
# Score <- Lunit[i]
# 
# accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_above_CAR_Score, Score, correct.rate)
# 
# return(accuracy)
# }
# 
# accuracy_both <- myfunction(Adult_Valid, Lunit[i])
# mylist[[i]] <- list(accuracy_both)
# }
# 
# LunitDF_both <- data.frame(matrix(unlist(mylist), nrow=101, byrow=T))
# LunitDF_both$Country <- paste("Pooled")
# 
# LunitDF <- LunitDF_both
# LunitDF$Sen_95CI <- paste(LunitDF[, 2], "-", LunitDF[, 3], sep = "")
# LunitDF$Spe_95CI <- paste(LunitDF[, 5], "-", LunitDF[, 6], sep = "")
# LunitDF$PPV_95CI <- paste(LunitDF[, 8], "-", LunitDF[, 9], sep = "")
# LunitDF$NPV_95CI <- paste(LunitDF[, 11], "-", LunitDF[, 12], sep = "")
# LunitDF$CAD_System <- paste("Lunit")

######### Merge DFs ######
CAD_Xpert <- rbind(CAD6DF, QureDF)
colnames(CAD_Xpert)[1] <- "Sens"
colnames(CAD_Xpert)[2] <- "Sens_L"
colnames(CAD_Xpert)[3] <- "Sens_H"
colnames(CAD_Xpert)[4] <- "Spec"
colnames(CAD_Xpert)[5] <- "Spec_L"
colnames(CAD_Xpert)[6] <- "Spec_H"
colnames(CAD_Xpert)[7] <- "ppv"
colnames(CAD_Xpert)[8] <- "PPV_L"
colnames(CAD_Xpert)[9] <- "PPV_H"
colnames(CAD_Xpert)[10] <- "npv"
colnames(CAD_Xpert)[11] <- "NPV_L"
colnames(CAD_Xpert)[12] <- "NPV_H"
colnames(CAD_Xpert)[13] <- "% Above"
colnames(CAD_Xpert)[14] <- "Score"
colnames(CAD_Xpert)[15] <- "Correct.rate"
CAD_Xpert$Sensitivity <- paste(CAD_Xpert$Sens, "(", CAD_Xpert$Sen_95CI, ")", sep = "")
CAD_Xpert$Specificity <- paste(CAD_Xpert$Spec, "(", CAD_Xpert$Spe_95CI, ")", sep = "")
CAD_Xpert$PPV <- paste(CAD_Xpert$ppv, "(", CAD_Xpert$PPV_95CI, ")", sep = "")
CAD_Xpert$NPV <- paste(CAD_Xpert$npv, "(", CAD_Xpert$NPV_95CI, ")", sep = "")
CAD_Xpert$`% Above` <- round(CAD_Xpert$`% Above`, 2)

CAD_Xpert <- CAD_Xpert[, c(16, 21, 14, 13, 15, 22:25)]

# write.csv(CAD_Xpert, "Supp_table.csv")
```

### 2020-01-22 Rename.Rmd
Jan22.2020

# Clean the wrong file name with DICOM tag

```{r Import DICOM Ex}
###### Match by filename
DICOM_extract <- read_excel("DICOM extract.xlsx")

LabelbyFileName <- merge(DICOM_extract, MDF, by.x = 'File name', by.y = 'TID_OMRS', all.x = T)

View(LabelbyFileName[, c(1,2,3,4,5,6,7,12,13)])
LabelbyFileName$Age <- as.numeric(LabelbyFileName$Age)
LabelbyFileName$AgeDICOM <- as.numeric(LabelbyFileName$AgeDICOM)

LabelbyFileName$agediff <- LabelbyFileName$Age - LabelbyFileName$AgeDICOM
summary(LabelbyFileName$agediff)
hist(LabelbyFileName$agediff, breaks = 100)

sum(LabelbyFileName$agediff %in% "0")

sum(LabelbyFileName$Gender %in%  LabelbyFileName$PatientSex & LabelbyFileName$Match %in% "FALSE")

###### Match by DICOM Tag
LabelbyDICOMName <- merge(DICOM_extract, MDF, by.x = 'PatientID', by.y = 'TID_OMRS', all.x = T)

View(LabelbyDICOMName[, c(1,2,3,4,5,6,7,12,13)])
LabelbyDICOMName$Age <- as.numeric(LabelbyDICOMName$Age)
LabelbyDICOMName$AgeDICOM <- as.numeric(LabelbyDICOMName$AgeDICOM)

LabelbyDICOMName$agediff <- LabelbyDICOMName$Age - LabelbyDICOMName$AgeDICOM
summary(LabelbyDICOMName$agediff)
hist(LabelbyDICOMName$agediff, breaks = 100)

sum(LabelbyDICOMName$agediff %in% "0")

sum(LabelbyDICOMName$Gender %in% LabelbyDICOMName$PatientSex & LabelbyDICOMName$Match %in% "FALSE")

#### 4 Luan #####
###### Match by filename

DICOMTag_Luan <- read_excel("DICOMTag Luan.xlsx")
LabelbyFileName <- merge(DICOMTag_Luan, MDF_Delft, by.x = 'FileName', by.y = 'TID_OMRS', all.x = T)

View(LabelbyFileName[, c(1,2,3,4,5,6,7,8, 14, 15)])
summary(LabelbyFileName$Match)

LabelbyFileName$Age <- as.numeric(LabelbyFileName$Age)
LabelbyFileName$AgeDICOM <- as.numeric(LabelbyFileName$AgeDICOM)

LabelbyFileName$agediff <- LabelbyFileName$Age - LabelbyFileName$AgeDICOM
summary(LabelbyFileName$agediff)
hist(LabelbyFileName$agediff, breaks = 100)

sum(LabelbyFileName$agediff %in% "0")

sum(LabelbyFileName$Gender %in%  LabelbyFileName$PatientSex & LabelbyFileName$Match %in% "FALSE")

###### Match by DICOM Tag
LabelbyDICOMName <- merge(DICOM_extract, MDF, by.x = 'PatientID', by.y = 'TID_OMRS', all.x = T)

View(LabelbyDICOMName[, c(1,2,3,4,5,6,7,12,13)])
LabelbyDICOMName$Age <- as.numeric(LabelbyDICOMName$Age)
LabelbyDICOMName$AgeDICOM <- as.numeric(LabelbyDICOMName$AgeDICOM)

LabelbyDICOMName$agediff <- LabelbyDICOMName$Age - LabelbyDICOMName$AgeDICOM
summary(LabelbyDICOMName$agediff)
hist(LabelbyDICOMName$agediff, breaks = 100)

sum(LabelbyDICOMName$agediff %in% "0")

sum(LabelbyDICOMName$Gender %in% LabelbyDICOMName$PatientSex & LabelbyDICOMName$Match %in% "FALSE")

```

```{r Cleaning Validated}
validated <- read_csv("validated.csv")
n_occur <- data.frame(table(validated$ValidedTID))
table(n_occur$Freq)
validated <- as.data.frame(n_occur$Var1[n_occur$Freq<2])
colnames(validated)[1] <- "TID"
n_occur <- data.frame(table(validated$TID))
table(n_occur$Freq)

validated_merge <- merge(validated, Master_df, by.x="TID", by.y = "TID_OMRS")
n_occur <- data.frame(table(validated_merge$TID))
table(n_occur$Freq)
validated_merge <- as.data.frame(n_occur$Var1[n_occur$Freq<2])
colnames(validated_merge)[1] <- "TID"
write.csv(validated_merge, "corrected_merge.csv")

missing <- subset(Master_df, !(Master_df$TID_OMRS %in% validated_merge$TID))
# write.csv(missing, "missing.csv")
transferred <- read_excel("transferred.xlsx")
missing <- subset(validated_merge, !(validated_merge$TID %in% transferred$Transferred))

write.csv(missing, "missing.csv")

rm(n_occur)
```

### 2020-01-22 SubGroup.Rmd
Jan22.2020

```{r Global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=15, fig.height=12, echo=FALSE, warning=FALSE, message=FALSE)
```

```{r eval=F}
source("DataWrangling/GlobalOption.R")
source("radiologist.R")
Radiologist <- Radiologist[Radiologist$Referral %in% "MDF", ]

New <- MDF[MDF$TB.Medication.History %in% "No",]
Old <- MDF[MDF$TB.Medication.History %in% "Yes",]

Young <- MDF[MDF$AgeGroup %in% "[15,25)",]
Middle <- MDF[MDF$AgeGroup %in% "[25,60)",]
Senior <- MDF[MDF$AgeGroup %in% "[60,108]",]

Private <- subset(MDF, MDF$Referral %in% "Private Provider")
Public <- subset(MDF, MDF$Referral %in% "Public DOTS Facilities")
WalkIn <- subset(MDF, MDF$Referral %in% "Walk-in")
Missing <- subset(MDF, is.na(MDF$Referral)==T)

New_long <- MDF_long[MDF_long$TB.Medication.History %in% "No",]
Old_long <- MDF_long[MDF_long$TB.Medication.History %in% "Yes",]
Young_long <- MDF_long[MDF_long$AgeGroup %in% "[15,25)",]
Middle_long <- MDF_long[MDF_long$AgeGroup %in% "[25,60)",]
Senior_long <- MDF_long[MDF_long$AgeGroup %in% "[60,108]",]
Private_long <- subset(MDF_long, MDF_long$Referral %in% "Private Provider")
Public_long <- subset(MDF_long, MDF_long$Referral %in% "Public DOTS Facilities")
WalkIn_long <- subset(MDF_long, MDF_long$Referral %in% "Walk-in")
Missing_long <- subset(MDF_long, is.na(MDF_long$Referral)==T)

# source("Chapter/Subgroup Table/Young.R")
# source("Chapter/Subgroup Table/Middle.R")
# source("Chapter/Subgroup Table/Senior.R")
# source("Chapter/Subgroup Table/Private.R")
# source("Chapter/Subgroup Table/Public.R")
# # write.csv(CAD_Xpert_plot_Middle, "Chapter/Subgroup Table/CAD_Xpert_plot_Middle.csv")
# # write.csv(CAD_Xpert_plot_Young, "Chapter/Subgroup Table/CAD_Xpert_plot_Young.csv")
# # write.csv(CAD_Xpert_plot_Senior, "Chapter/Subgroup Table/CAD_Xpert_plot_Senior.csv")
# # write.csv(CAD_Xpert_plot_Private, "Chapter/Subgroup Table/CAD_Xpert_plot_Private.csv")
# # write.csv(CAD_Xpert_plot_Public, "Chapter/Subgroup Table/CAD_Xpert_plot_Public.csv")
# 
# source("Chapter/Subgroup Table/WalkIn.R")
# source("Chapter/Subgroup Table/Missing.R")
# source("Chapter/Subgroup Table/New.R")
# source("Chapter/Subgroup Table/Old.R")
# 
# 
# # save(CAD_Xpert_plot_Young, "Young.rdata")
# SubgroupTable <- rbind(CAD_Xpert_plot_New, CAD_Xpert_plot_Old, CAD_Xpert_plot_Young, CAD_Xpert_plot_Middle, CAD_Xpert_plot_Senior, CAD_Xpert_plot_Private, CAD_Xpert_plot_Public, CAD_Xpert_plot_WalkIn, CAD_Xpert_plot_Missing)
# write.csv(SubgroupTable, "Chapter/Subgroup Table/SubgroupTable.csv")
```

## Subgroup Curves
```{r subgroup curves, eval=F}
# subgroup 4 curves
SubgroupPlot <- read.csv("Chapter/Subgroup Table/SubgroupTable.csv")
SubgroupPlot <- SubgroupPlot[, -1]
SubgroupPlot$Score[SubgroupPlot$DeepLearningSystem %in% "CAD4TB"] <- SubgroupPlot$Score[SubgroupPlot$DeepLearningSystem %in% "CAD4TB"]/100
SubgroupPlotOrigin <- SubgroupPlot

# Choose the DL System
# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "CAD4TB", ]
# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "IF2", ]
# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "JF1", ]
# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "Lunit", ]
SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "qXR", ]

### GO TO AND RUN source("Chapter/Subgroup Table/SubGroupPlot.R")

```

```{r Bar chart}
aucTable <- read.csv("Results/aucTable.csv")
aucTable <- aucTable[, -1]

### AUC
age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young", "Middle", "Senior"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

referral<-ggplot(aucTable[aucTable$Subgroup %in% c("Private", "Public", "WalkIn", "Missing"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

history<-ggplot(aucTable[aucTable$Subgroup %in% c("New", "Old"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

### PRC
agePC<-ggplot(aucTable[aucTable$Subgroup %in% c("Young", "Middle", "Senior"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("Private", "Public", "WalkIn", "Missing"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

historyPC<-ggplot(aucTable[aucTable$Subgroup %in% c("New", "Old"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

tiff("Results/AUC plot.tif", width = 18, height = 8, units = "in", res = 100)
require(gridExtra)
grid.arrange(age, referral, history, agePC, referralPC, historyPC, ncol=3)

dev.off()
```

### 2020-01-22 AUC_CI_DeLong.py

@@ -1,0 +1,229 @@
+import numpy as np
+import scipy.stats
+from scipy import stats
+
+# AUC comparison adapted from
+# https://github.com/Netflix/vmaf/
+def compute_midrank(x):
+    """Computes midranks.
+    Args:
+       x - a 1D numpy array
+    Returns:
+       array of midranks
+    """
+    J = np.argsort(x)
+    Z = x[J]
+    N = len(x)
+    T = np.zeros(N, dtype=np.float)
+    i = 0
+    while i < N:
+        j = i
+        while j < N and Z[j] == Z[i]:
+            j += 1
+        T[i:j] = 0.5*(i + j - 1)
+        i = j
+    T2 = np.empty(N, dtype=np.float)
+    # Note(kazeevn) +1 is due to Python using 0-based indexing
+    # instead of 1-based in the AUC formula in the paper
+    T2[J] = T + 1
+    return T2
+
+
+def compute_midrank_weight(x, sample_weight):
+    """Computes midranks.
+    Args:
+       x - a 1D numpy array
+    Returns:
+       array of midranks
+    """
+    J = np.argsort(x)
+    Z = x[J]
+    cumulative_weight = np.cumsum(sample_weight[J])
+    N = len(x)
+    T = np.zeros(N, dtype=np.float)
+    i = 0
+    while i < N:
+        j = i
+        while j < N and Z[j] == Z[i]:
+            j += 1
+        T[i:j] = cumulative_weight[i:j].mean()
+        i = j
+    T2 = np.empty(N, dtype=np.float)
+    T2[J] = T
+    return T2
+
+
+def fastDeLong(predictions_sorted_transposed, label_1_count, sample_weight):
+    if sample_weight is None:
+        return fastDeLong_no_weights(predictions_sorted_transposed, label_1_count)
+    else:
+        return fastDeLong_weights(predictions_sorted_transposed, label_1_count, sample_weight)
+
+
+def fastDeLong_weights(predictions_sorted_transposed, label_1_count, sample_weight):
+    """
+    The fast version of DeLong's method for computing the covariance of
+    unadjusted AUC.
+    Args:
+       predictions_sorted_transposed: a 2D numpy.array[n_classifiers, n_examples]
+          sorted such as the examples with label "1" are first
+    Returns:
+       (AUC value, DeLong covariance)
+    Reference:
+     @article{sun2014fast,
[…]

### 2020-01-22 BGD_cleaning.py

@@ -1,0 +1,27 @@
+import numpy as np
+import pandas as pd
+pd.set_option('display.max_columns', 60)
+import matplotlib.pylab as plt
+from pandas import Series, DataFrame
+
+## Importing MDF.csv ---------------------------------------------------------------------------------------
+address = 'C:/Users/zhizh/OneDrive - Stop TB Partnership/UNOPS/10 Paper Writing/CAR software/02 Bangladesh/CAR-Bangladesh/CAR_BGD/MDF.csv'
+
+# Making a list of missing value types
+missing_values = ["n/a", "na", "--", "N/A", "-"]
+BGD = pd.read_csv(address, na_values= missing_values)
+BGD = BGD.drop(['Given', 'FamilyName', 'Patient.BD', 'Filename', 'Radiology.Result.Date'], axis=1)
+print(BGD.info())
+
+## checking missing symptom values ---------------------------------------------------------------------------------------
+print (BGD['Cough'].isnull())
+print(BGD.isnull().sum())
+# Not much symptom variable with NA value, it is fair to assume that the NA were missed entry. Based on this assumption, we will replace all the NA with 'No"
+BGD['Cough'].fillna('No', inplace=True)
+BGD['Fever'].fillna('No', inplace=True)
+BGD['Active Breathing Shortness'].fillna('No', inplace=True)
+BGD['Weight Loss'].fillna('No', inplace=True)
+BGD['Haemoptysis'].fillna('No', inplace=True)
+
+## Adding Xpert + by symptoms --------------------------------------------------------------------------------------------
+BGD.groupby('Symptoms').aggregate(sum)

### 2020-01-22 Chapter/3D.R

@@ -1,0 +1,21 @@
+library(scatterplot3d)
+CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE 4 digits.csv")
+CAD_Xpert_plot <- CAD_Xpert_plot[, -1]
+
+CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% c("IF1", "JF2", "IF2"), ]
+CAD_Xpert_plot$DeepLearningSystem <- as.factor(as.character(CAD_Xpert_plot2$DeepLearningSystem))
+
+CAD_Xpert_plot$Score[CAD_Xpert_plot$DeepLearningSystem %in% "CAD4TB"] <- CAD_Xpert_plot$Score[CAD_Xpert_plot$DeepLearningSystem %in% "CAD4TB"]/100
+
+colors <- c("#A7226E", "#EC2049", "#2F9599", "#F7DB4F", "#56B4E9")
+colors <- colors[as.numeric(CAD_Xpert_plot$DeepLearningSystem)]
+
+# 2. Empty 3D scatter plot using pch=""
+s3d <- scatterplot3d(CAD_Xpert_plot$Score, CAD_Xpert_plot$Sens, CAD_Xpert_plot$Spec, color = colors, grid=FALSE, box=FALSE)
+legend("top", legend = levels(CAD_Xpert_plot$DeepLearningSystem),
+       col =  c("#A7226E", "#EC2049", "#2F9599", "#F7DB4F", "#56B4E9"), pch = 16,  inset = -0.1, xpd = TRUE,horiz = TRUE)
+
+# 3. Add grids
+source("DataWrangling/addgrids3d.R")
+addgrids3d(CAD_Xpert_plot$Score, CAD_Xpert_plot$Sens, CAD_Xpert_plot$Spec, grid = c("xy", "xz", "yz"))
+

### 2020-01-22 Chapter/4 Curves.R

@@ -1,0 +1,65 @@
+source("DataWrangling/GlobalOption.R")
+
+CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE 4 digits.csv")
+CAD_Xpert_plot <- CAD_Xpert_plot[, -1]
+CAD_Xpert_plot$NNT <- 1/CAD_Xpert_plot$ppv
+CAD_Xpert_plot$NNT_H <- 1/CAD_Xpert_plot$PPV_L
+CAD_Xpert_plot$NNT_L <- 1/CAD_Xpert_plot$PPV_H
+
+
+CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% c("IF1", "JF2", "IF3"), ]
+CAD_Xpert_plot$Score[CAD_Xpert_plot$DeepLearningSystem %in% "CAD4TB"] <- CAD_Xpert_plot$Score[CAD_Xpert_plot$DeepLearningSystem %in% "CAD4TB"]/100
+
+### Sensitivity vs Score --------------------
+base <- ggplot(CAD_Xpert_plot, aes(Score, Sens)) + geom_path(aes(color = DeepLearningSystem)) + 
+  geom_ribbon(aes(x = Score, ymin = Sens_L, ymax = Sens_H, color = DeepLearningSystem, fill = DeepLearningSystem), alpha= 0.2) 
+
+sensCurve <- base + theme_light() + coord_equal() + labs(x = "Abnormality Score", y= "Sensitivity", subtitle = paste0("The Sensitivity vs abnormality score (n=", length(MDF$PID_OMRS), ")")) +theme(legend.position = c(0.05,0.05),legend.justification = c("left", "bottom")) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_x_continuous(minor_breaks = seq(0 , 1, 0.1), breaks = seq(0, 1, 0.1))+ scale_y_continuous(minor_breaks = seq(0 , 1, 0.1), breaks = seq(0, 1, 0.1)) + geom_vline(xintercept = c(0.75, 0.5), linetype="dotted", color = "blue", size=1) +theme(legend.position = "none")
+# sensCurveZoomIn <- sensCurve + coord_cartesian(xlim = c(0.5, 0.9), ylim = c(0.90, 1) ) +
+# ggtitle("Figure 2b: Zoomed-in view of the square marked part of Fig. 2a")+theme_light()
+
+
+
+### NNT --------------------
[…]

### 2020-01-22 Chapter/Optimal_cutoff Xpert.R

@@ -1,0 +1,11 @@
+
+library(OptimalCutpoints)
+
+BestCutoff <- optimal.cutpoints(X = "AbnormalityScore", status = "Xpert2Outcome_num", tag.healthy = 0, methods = "ROC01", data = MDF_long, pop.prev = NULL, categorical.cov = "DeepLearningSystem", control = control.cutpoints(valueSe=0.95, maxSp=TRUE), ci.fit = FALSE, conf.level = 0.95, trace = FALSE)
+summary(BestCutoff)
+
+BestCutoff <- optimal.cutpoints(X = "AbnormalityScore", status = "Xpert2Outcome_num", tag.healthy = 0, methods = "MinValueSe", data = MDF_long, pop.prev = NULL, categorical.cov = "DeepLearningSystem", control = control.cutpoints(valueSe=0.98, maxSp=TRUE), ci.fit = FALSE, conf.level = 0.95, trace = FALSE)
+summary(BestCutoff)
+
+# plot(BestCutoff)
+rm(BestCutoff)

### 2020-01-22 Chapter/PPV.R

@@ -1,0 +1,21 @@
+source("DataWrangling/GlobalOption.R")
+
+CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE 4 digits.csv")
+CAD_Xpert_plot <- CAD_Xpert_plot[, -1]
+
+CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% c("IF1", "JF2", "IF3"), ]
+CAD_Xpert_plot$Score[CAD_Xpert_plot$DeepLearningSystem %in% "CAD4TB"] <- CAD_Xpert_plot$Score[CAD_Xpert_plot$DeepLearningSystem %in% "CAD4TB"]/100
+
+base <- ggplot(CAD_Xpert_plot, aes(Score, ppv)) + geom_path(aes(color = DeepLearningSystem)) + 
+  geom_ribbon(data = CAD_Xpert_plot %>% filter(Score <0.90), aes(x = Score, ymin = PPV_L, ymax = PPV_H, color = DeepLearningSystem, fill = DeepLearningSystem), alpha= 0.2) 
+
+ppvCurve <- base + theme_light() + coord_equal() + labs(x = "Abnormality Score", y= "PPV", subtitle = paste0("The PPV of CAD4TB(v6), Infervision(v2), JF CXR-1, Lunit(4.9.0) and qXR(v2) using Xpert results as the reference (n=", length(MDF$PID_OMRS), ")")) 
+ppvCurve
+
+tiff("Results/ppvCurve.tif", width = 10, height = 7.9, units = "in", res = 100)
+ppvCurve
+dev.off()
+
+# scoreCurveZoomIn <- scoreCurve + coord_cartesian(xlim = c(0.5, 0.9), ylim = c(0.90, 1) ) +
+# ggtitle("Figure 2b: Zoomed-in view of the square marked part of Fig. 2a")+theme_light()
+

### 2020-01-22 Chapter/Subgroup Table/Middle.R

@@ -1,0 +1,505 @@
+## Cutoff Table (Full)
+source("DataWrangling/GlobalOption.R")
+source("radiologist.R")
+Radiologist <- Radiologist[c(1:3), ]
+
+
+
+###### Qure.AI Score by 0.0001 #########
+qure_ai_score <- seq(0,1, by = 0.0001)
+
+mylist <- NULL
+mylist <- as.list(mylist)
+
+for (i in 1:10001){
+  myfunction <- function(CountryX, car.cutoff){
+    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
+    colnames(dat) <- c("Dis+","Dis-")
+    rownames(dat) <- c("Test+","Test-")
+    rval <- epi.tests(dat, conf.level = 0.95)
+    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
+    specificity <- as.vector(round((rval$elements$specificity),4))
+    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
+    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
+    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
+    
+    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
+    Score <- qure_ai_score[i]
+    
+    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
+    
+    return(accuracy)
+  }
+  
+  accuracy <- myfunction(Middle, qure_ai_score[i])
+  mylist[[i]] <- list(accuracy)
+  
+}
+
+QureDF <- data.frame(matrix(unlist(mylist), nrow=10001, byrow=T))
+QureDF$Country <- paste("Bangladesh")
+
[…]

### 2020-01-22 Chapter/Subgroup Table/Missing.R

@@ -1,0 +1,509 @@
+## Cutoff Table (Full)
+source("DataWrangling/GlobalOption.R")
+source("radiologist.R")
+Radiologist <- Radiologist[c(1:3), ]
+Private <- subset(MDF, MDF$Referral %in% "Private Provider")
+Public <- subset(MDF, MDF$Referral %in% "Public DOTS Facilities")
+WalkIn <- subset(MDF, MDF$Referral %in% "Walk-in")
+Missing <- subset(MDF, is.na(MDF$Referral)==T)
+
+
+
+###### Qure.AI Score by 0.0001 #########
+qure_ai_score <- seq(0,1, by = 0.0001)
+
+mylist <- NULL
+mylist <- as.list(mylist)
+
+for (i in 1:10001){
+  myfunction <- function(CountryX, car.cutoff){
+    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
+    colnames(dat) <- c("Dis+","Dis-")
+    rownames(dat) <- c("Test+","Test-")
+    rval <- epi.tests(dat, conf.level = 0.95)
+    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
+    specificity <- as.vector(round((rval$elements$specificity),4))
+    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
+    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
+    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
+    
+    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
+    Score <- qure_ai_score[i]
+    
+    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
+    
+    return(accuracy)
+  }
+  
[…]

### 2020-01-22 Chapter/Subgroup Table/New.R

@@ -1,0 +1,504 @@
+## Cutoff Table (Full)
+source("DataWrangling/GlobalOption.R")
+source("radiologist.R")
+Radiologist <- Radiologist[c(1:3), ]
+
+
+###### Qure.AI Score by 0.0001 #########
+qure_ai_score <- seq(0,1, by = 0.0001)
+
+mylist <- NULL
+mylist <- as.list(mylist)
+
+for (i in 1:10001){
+  myfunction <- function(CountryX, car.cutoff){
+    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
+    colnames(dat) <- c("Dis+","Dis-")
+    rownames(dat) <- c("Test+","Test-")
+    rval <- epi.tests(dat, conf.level = 0.95)
+    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
+    specificity <- as.vector(round((rval$elements$specificity),4))
+    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
+    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
+    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
+    
+    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
+    Score <- qure_ai_score[i]
+    
+    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
+    
+    return(accuracy)
+  }
+  
+  accuracy <- myfunction(New, qure_ai_score[i])
+  mylist[[i]] <- list(accuracy)
+  
+}
+
+QureDF <- data.frame(matrix(unlist(mylist), nrow=10001, byrow=T))
+QureDF$Country <- paste("Bangladesh")
+
[…]

### 2020-01-22 Chapter/Subgroup Table/Old.R

@@ -1,0 +1,505 @@
+## Cutoff Table (Full)
+source("DataWrangling/GlobalOption.R")
+source("radiologist.R")
+Radiologist <- Radiologist[c(1:3), ]
+
+
+
+###### Qure.AI Score by 0.0001 #########
+qure_ai_score <- seq(0,1, by = 0.0001)
+
+mylist <- NULL
+mylist <- as.list(mylist)
+
+for (i in 1:10001){
+  myfunction <- function(CountryX, car.cutoff){
+    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
+    colnames(dat) <- c("Dis+","Dis-")
+    rownames(dat) <- c("Test+","Test-")
+    rval <- epi.tests(dat, conf.level = 0.95)
+    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
+    specificity <- as.vector(round((rval$elements$specificity),4))
+    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
+    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
+    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
+    
+    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
+    Score <- qure_ai_score[i]
+    
+    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
+    
+    return(accuracy)
+  }
+  
+  accuracy <- myfunction(Old, qure_ai_score[i])
+  mylist[[i]] <- list(accuracy)
+  
+}
+
+QureDF <- data.frame(matrix(unlist(mylist), nrow=10001, byrow=T))
+QureDF$Country <- paste("Bangladesh")
+
[…]

### 2020-01-22 Chapter/Subgroup Table/Private.R

@@ -1,0 +1,506 @@
+source("DataWrangling/GlobalOption.R")
+source("radiologist.R")
+Radiologist <- Radiologist[c(1:3), ]
+Private <- subset(MDF, MDF$Referral %in% "Private Provider")
+Public <- subset(MDF, MDF$Referral %in% "Public DOTS Facilities")
+WalkIn <- subset(MDF, MDF$Referral %in% "Walk-in")
+Missing <- subset(MDF, is.na(MDF$Referral)==T)
+
+###### Qure.AI Score by 0.0001 #########
+qure_ai_score <- seq(0,1, by = 0.0001)
+
+mylist <- NULL
+mylist <- as.list(mylist)
+
+for (i in 1:10001){
+  myfunction <- function(CountryX, car.cutoff){
+    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
+    colnames(dat) <- c("Dis+","Dis-")
+    rownames(dat) <- c("Test+","Test-")
+    rval <- epi.tests(dat, conf.level = 0.95)
+    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
+    specificity <- as.vector(round((rval$elements$specificity),4))
+    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
+    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
+    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
+    
+    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
+    Score <- qure_ai_score[i]
+    
+    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
+    
+    return(accuracy)
+  }
+  
[…]

### 2020-01-22 Chapter/Subgroup Table/Public.R

@@ -1,0 +1,504 @@
+source("DataWrangling/GlobalOption.R")
+source("radiologist.R")
+Radiologist <- Radiologist[c(1:3), ]
+Public <- subset(MDF, MDF$Referral %in% "Public DOTS Facilities")
+
+
+###### Qure.AI Score by 0.0001 #########
+qure_ai_score <- seq(0,1, by = 0.0001)
+
+mylist <- NULL
+mylist <- as.list(mylist)
+
+for (i in 1:10001){
+  myfunction <- function(CountryX, car.cutoff){
+    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
+    colnames(dat) <- c("Dis+","Dis-")
+    rownames(dat) <- c("Test+","Test-")
+    rval <- epi.tests(dat, conf.level = 0.95)
+    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
+    specificity <- as.vector(round((rval$elements$specificity),4))
+    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
+    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
+    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
+    
+    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
+    Score <- qure_ai_score[i]
+    
+    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
+    
+    return(accuracy)
+  }
+  
+  accuracy <- myfunction(Public, qure_ai_score[i])
+  mylist[[i]] <- list(accuracy)
+  
+}
+
+QureDF <- data.frame(matrix(unlist(mylist), nrow=10001, byrow=T))
[…]

### 2020-01-22 Chapter/Subgroup Table/Senior.R

@@ -1,0 +1,505 @@
+## Cutoff Table (Full)
+source("DataWrangling/GlobalOption.R")
+source("radiologist.R")
+Radiologist <- Radiologist[c(1:3), ]
+
+
+
+###### Qure.AI Score by 0.0001 #########
+qure_ai_score <- seq(0,1, by = 0.0001)
+
+mylist <- NULL
+mylist <- as.list(mylist)
+
+for (i in 1:10001){
+  myfunction <- function(CountryX, car.cutoff){
+    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
+    colnames(dat) <- c("Dis+","Dis-")
+    rownames(dat) <- c("Test+","Test-")
+    rval <- epi.tests(dat, conf.level = 0.95)
+    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
+    specificity <- as.vector(round((rval$elements$specificity),4))
+    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
+    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
+    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
+    
+    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
+    Score <- qure_ai_score[i]
+    
+    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
+    
+    return(accuracy)
+  }
+  
+  accuracy <- myfunction(Senior, qure_ai_score[i])
+  mylist[[i]] <- list(accuracy)
+  
+}
+
+QureDF <- data.frame(matrix(unlist(mylist), nrow=10001, byrow=T))
+QureDF$Country <- paste("Bangladesh")
+
[…]

### 2020-01-22 Chapter/Subgroup Table/WalkIn.R

@@ -1,0 +1,506 @@
+source("DataWrangling/GlobalOption.R")
+source("radiologist.R")
+Radiologist <- Radiologist[c(1:3), ]
+Private <- subset(MDF, MDF$Referral %in% "Private Provider")
+Public <- subset(MDF, MDF$Referral %in% "Public DOTS Facilities")
+WalkIn <- subset(MDF, MDF$Referral %in% "Walk-in")
+Missing <- subset(MDF, is.na(MDF$Referral)==T)
+
+###### Qure.AI Score by 0.0001 #########
+qure_ai_score <- seq(0,1, by = 0.0001)
+
+mylist <- NULL
+mylist <- as.list(mylist)
+
+for (i in 1:10001){
+  myfunction <- function(CountryX, car.cutoff){
+    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
+    colnames(dat) <- c("Dis+","Dis-")
+    rownames(dat) <- c("Test+","Test-")
+    rval <- epi.tests(dat, conf.level = 0.95)
+    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
+    specificity <- as.vector(round((rval$elements$specificity),4))
+    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
+    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
+    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
+    
+    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
+    Score <- qure_ai_score[i]
+    
+    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
+    
+    return(accuracy)
+  }
+  
[…]

### 2020-01-22 Chapter/Subgroup Table/Young.R

@@ -1,0 +1,505 @@
+## Cutoff Table (Full)
+source("DataWrangling/GlobalOption.R")
+source("radiologist.R")
+Radiologist <- Radiologist[c(1:3), ]
+
+
+
+###### Qure.AI Score by 0.0001 #########
+qure_ai_score <- seq(0,1, by = 0.0001)
+
+mylist <- NULL
+mylist <- as.list(mylist)
+
+for (i in 1:10001){
+  myfunction <- function(CountryX, car.cutoff){
+    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
+    colnames(dat) <- c("Dis+","Dis-")
+    rownames(dat) <- c("Test+","Test-")
+    rval <- epi.tests(dat, conf.level = 0.95)
+    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
+    specificity <- as.vector(round((rval$elements$specificity),4))
+    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
+    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
+    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
+    
+    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
+    Score <- qure_ai_score[i]
+    
+    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
+    
+    return(accuracy)
+  }
+  
+  accuracy <- myfunction(Young, qure_ai_score[i])
+  mylist[[i]] <- list(accuracy)
+  
+}
+
+QureDF <- data.frame(matrix(unlist(mylist), nrow=10001, byrow=T))
+QureDF$Country <- paste("Bangladesh")
+
[…]

### 2020-01-22 Chapter/Xpert saving.R

@@ -1,0 +1,28 @@
+source("DataWrangling/GlobalOption.R")
+CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE 4 digits.csv")
+CAD_Xpert_plot <- CAD_Xpert_plot[, -1]
+
+CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% c("IF1", "JF2", "IF3"), ]
+CAD_Xpert_plot$Score[CAD_Xpert_plot$DeepLearningSystem %in% "CAD4TB"] <- CAD_Xpert_plot$Score[CAD_Xpert_plot$DeepLearningSystem %in% "CAD4TB"]/100
+
+### Xpert saving vs Score
+base <- ggplot(CAD_Xpert_plot, aes(Score, X.XpertSaved)) + geom_path(aes(color = DeepLearningSystem)) 
+
+XpertSavingCurve <- base + theme_light() + coord_equal() + labs(x = "Abnormality Score", y= "Xpert Saving", subtitle = paste0("The Xpert Saving of CAD4TB(v6), Infervision(v2), JF CXR-1, Lunit(4.9.0) and qXR(v2) using Xpert results as the reference (n=", length(MDF$PID_OMRS), ")")) 
+
+### Sens vs Xpert saving
+base <- ggplot(CAD_Xpert_plot, aes(Sens, X.XpertSaved)) + geom_path(aes(color = DeepLearningSystem)) 
+
+XpertSens <- base + theme_light() + coord_equal() + labs(x = "Sensitivity", y= "Xpert Saving", subtitle = paste0("The Xpert Saving vs Sens of CAD4TB(v6), Infervision(v2), JF CXR-1, Lunit(4.9.0) and qXR(v2) using Xpert results as the reference (n=", length(MDF$PID_OMRS), ")")) 
+
+
+
+tiff("Results/XpertSavingCurve.tif", width = 10, height = 7.9, units = "in", res = 200)
+require(gridExtra)
+grid.arrange(XpertSavingCurve, XpertSens, ncol=2)
+dev.off()
+
+
+
+
+

### 2020-01-22 Chapter/histogram.R

@@ -1,0 +1,59 @@
+source("DataWrangling/GlobalOption.R")
+MDF_long$XpertHistory <- ""
+MDF_long$XpertHistory[MDF_long$TB.Medication.History %in% "No" & MDF_long$Xpert2Outcome_num %in% "0"] <- "Xpert Negative - no TB History"
+MDF_long$XpertHistory[MDF_long$TB.Medication.History %in% "Yes" & MDF_long$Xpert2Outcome_num %in% "0"] <- "Xpert Negative - with TB History"
+
+MDF_long$XpertHistory[MDF_long$TB.Medication.History %in% "No" & MDF_long$Xpert2Outcome_num %in% "1"] <- "Xpert Positive - no TB History"
+MDF_long$XpertHistory[MDF_long$TB.Medication.History %in% "Yes" & MDF_long$Xpert2Outcome_num %in% "1"] <- "Xpert Positive - with TB History"
+
+
+## Histogram
+p <- ggplot(MDF_long,aes(x=AbnormalityScore, fill=XpertHistory,))+ geom_histogram(position = 'stack', alpha=0.5, breaks=seq(0,100, by=5), aes(y = ..count.., fill = XpertHistory)) + xlab("Abnormality Scores of the Deep Learning Systems") 
+hist <- p + facet_wrap(~DeepLearningSystem) + theme_minimal() + theme(legend.position = "top") +scale_fill_manual(values=c("#f7f7f7", "#fbb4b9", "#91003f", "#a1dab4", "#006d2c"))
+
+
+tiff("Results/Histogram.tif", width = 14, height = 8, units = "in", res = 100)
+hist
+dev.off()
+
+## Density plot
+p <- ggplot(MDF_long,aes(x=AbnormalityScore, fill=XpertHistory,))+ geom_histogram(position = 'identity', alpha=0.5, breaks=seq(0,100, by=5), aes(y = ..density.., fill = XpertHistory)) + xlab("Abnormality Scores of the Deep Learning Systems") 
+density <- p + facet_wrap(~DeepLearningSystem) + theme_minimal() + theme(legend.position = "top") +scale_fill_manual(values=c("#f7f7f7", "#fbb4b9", "#91003f", "#a1dab4", "#006d2c"))
+density
+
+tiff("Results/density.tif", width = 14, height = 8, units = "in", res = 100)
+density
[…]

### 2020-01-22 Chapter/roc.R

@@ -1,0 +1,52 @@
+source("radiologist.R")
+
+Radiologist <- Radiologist[Radiologist$Referral %in% "MDF", ]
+
+CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE 4 digits.csv")
+CAD_Xpert_plot <- CAD_Xpert_plot[, -1]
+
+CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% c("IF1", "JF2", "IF3"), ]
+
+roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, MDF)
+roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv2_100, MDF)
+roc_Lunit <- ci.auc(Xpert2Outcome_num ~ LunitScore_100, MDF)
+roc_JF1 <- ci.auc(Xpert2Outcome_num ~ JF1_100, MDF)
+roc_JF2 <- ci.auc(Xpert2Outcome_num ~ JF2_100, MDF)
+roc_IF1 <- ci.auc(Xpert2Outcome_num ~ IF1_100, MDF)
+roc_IF2 <- ci.auc(Xpert2Outcome_num ~ IF2_100, MDF)
+roc_IF3 <- ci.auc(Xpert2Outcome_num ~ IF3_100, MDF)
+
+
+# base <- ggplot(CAD_Xpert_plot, aes(X, Sens, color = DeepLearningSystem)) + geom_path()+ geom_ribbon(aes(x = X, ymin = Sens_L, ymax = Sens_H), fill = "red", alpha= 0.2)
+
+base <- ggplot(CAD_Xpert_plot, aes(X, Sens)) + geom_path(aes(color = DeepLearningSystem)) + 
+  geom_ribbon(aes(x = X, ymin = Sens_L, ymax = Sens_H, color = DeepLearningSystem, fill = DeepLearningSystem), alpha= 0.2) 
+
+
+ggROC <- base + theme_minimal() + geom_abline(slope=1, intercept = 0, linetype = "dashed", alpha=0.7, color = "grey") + coord_equal()+ annotate("text", x = .75, y = .15, 
+                                                                                                                                                label = paste(" CAD4TB: ", round(roc_CAD6[2],2), " (95% CI:", round(roc_CAD6[1],2), "-", round(roc_CAD6[3],2), ")", "\n",
[…]

### 2020-01-22 Chapter/table1.R

@@ -1,0 +1,45 @@
+source("DataWrangling/GlobalOption.R")
+
+# MDF <- subset(MDF, MDF$Age > 15)
+library(tableone)
+
+# Define numeric variables
+listVar <- c("Age", "Gender", "Cough", "Fever", "Active.Breathing.Shortness", "Weight.Loss","Haemoptysis", "Symptoms", "TB.Medication.History", "Xpert2Outcome_num", "MTB.Burden", "RIF.Result", "Referral", "rad.highly.TB", "rad.TB", "rad.abn", "CAD4TB6", "qXRv2", "LunitScore", "JF1", "IF1", "IF2")
+
+#Define categorical variables
+catVars <- c( "Gender", "Cough", "Fever", "Active.Breathing.Shortness", "Weight.Loss","Haemoptysis", "Symptoms", "TB.Medication.History", "Xpert2Outcome_num", "MTB.Burden", "RIF.Result", "Referral", "rad.highly.TB", "rad.TB", "rad.abn")
+
+
+table1 <- CreateTableOne(vars = listVar, strata=c("Xpert2Outcome_num"), data = MDF, factorVars = catVars)
+tableType <- CreateTableOne(vars = listVar, strata=c("Referral"), data = MDF, factorVars = catVars)
+
+table1.all <- CreateTableOne(vars = listVar, data = MDF, factorVars = catVars)
+
+
+table1 <- print(table1, nonnormal = c("Age", "CAD4TB6", "qXRv2", "LunitScore", "JF1", "IF1", "IF2"), cramVars = "Gender", catDigits = 1, contDigits = 1, noSpaces = TRUE)
+tabletype <- print(tableType, nonnormal = c("Age", "CAD4TB6", "qXRv2", "LunitScore", "JF1", "IF1", "IF2"), cramVars = "Gender", catDigits = 1, contDigits = 1, noSpaces = TRUE)
+table1all <- print(table1.all, nonnormal = c("Age","CAD4TB6", "qXRv2", "LunitScore", "JF1", "IF1", "IF2"), cramVars = "Gender", catDigits = 1, contDigits = 1, noSpaces = TRUE)
+
+table1DF <- data.frame(columnNameILike = row.names(table1), table1)
+table1allDF <- data.frame(columnNameILike = row.names(table1all), table1all)
+tabletypeDF <- data.frame(columnNameILike = row.names(tabletype), tabletype)
[…]

### 2020-01-22 DataWrangling/Clean_ImageReceived.R

@@ -1,0 +1,30 @@
+### Clean Image Received
+### Image Received ###
+ReceviedIndex <- read.csv(file = "Image index received.csv")
+colnames(ReceviedIndex)[1] <- "TID"
+ReceviedIndex$TID <- as.character(ReceviedIndex$TID)
+ReceviedIndex$FileFolder <- paste(ReceviedIndex$TID, ReceviedIndex$Folder, sep = "_")
+
+# File Received
+ReceviedIndex$Center <- 0 
+ReceviedIndex$Center[ReceviedIndex$Folder %in% "1st Batch\\Dhanmondi_TBSTC"] <- "Dhanmondi"
+ReceviedIndex$Center[ReceviedIndex$Folder %in% "1st Batch\\Golapbagh_TBSTC"] <- "Golapbagh"
+ReceviedIndex$Center[ReceviedIndex$Folder %in% "1st Batch\\Mohakhali_TBSTC"] <- "Mohakhali"
+ReceviedIndex$Center[ReceviedIndex$Folder %in% "2nd Batch\\Dhanmondi2"] <- "Dhanmondi"
+ReceviedIndex$Center[ReceviedIndex$Folder %in% "2nd Batch\\Golapbagh2"] <- "Golapbagh"
+ReceviedIndex$Center[ReceviedIndex$Folder %in% "2nd Batch\\Mohakhali2"] <- "Mohakhali"
+
+##### Image Received:: Duplicated TID ##### --> Solved
+n_occur <- data.frame(table(ReceviedIndex$TID))
+Multi_TID_Received <- (ReceviedIndex[ReceviedIndex$TID %in% n_occur$Var1[n_occur$Freq >1], ]) 
+# Remove the duplicated records from the 2nd Batch
+Uni1Batch <- Multi_TID_Received[!duplicated(Multi_TID_Received[c("TID", "Center")]), ]
+TID_2ndBatch_Remove <- subset(Multi_TID_Received, !(Multi_TID_Received$FileFolder %in% Uni1Batch$FileFolder))
+# write.csv(TID_2ndBatch_Remove, "TID_2ndBatch_Remove.csv")
+
+rm(n_occur, TID_2ndBatch_Remove, Multi_TID_Received, Uni1Batch)
+
+ReceviedIndex <- ReceviedIndex[!duplicated(ReceviedIndex["TID"]), ]
[…]

### 2020-01-22 DataWrangling/Cleaning.R

@@ -1,0 +1,188 @@
+Sys.setenv(LANG = "en")
+library(ggplot2)
+library(scales)
+library(epiR)
+library(ggthemes)
+library(RColorBrewer)
+library(plyr)
+library(reshape2)
+library(pROC) # contain function roc
+library(tidyverse)
+library(dplyr)
+library(lubridate)
+library(readxl)
+library(plotROC)
+library(flextable)
+library(DataExplorer)
+library("readxl")
+as.numeric.factor <- function(x) {as.numeric(levels(x))[x]}
+
+Master_df <- read.table(file = "DataWrangling/Master_60K_OpenMRS_08_11_2018.csv", header=T, sep=",")
+Master_df$Result.Date <- mdy(Master_df$Radiology.Result.Date)
+Master_df$Result.Year <- quarter(Master_df$Result.Date)
+
+Master_df$Xpert2Outcome_num <- as.character(Master_df$GXP.Result)
+Master_df$Xpert2Outcome_num[Master_df$GXP.Result %in% "MTB Detected"] <- "1"
+Master_df$Xpert2Outcome_num[Master_df$GXP.Result %in% "MTB Not Detected"] <- "0"
+Master_df$Xpert2Outcome_num <- as.numeric(Master_df$Xpert2Outcome_num)
+
+Master_df <- Master_df %>%
+  filter(Result.Date < as.Date("2017-01-01"))
+
+SymptomData <- read_excel("DataWrangling/ScreeningData.xlsx")
+
+Master_df <- merge(Master_df, SymptomData, by.x = "PID_OMRS", by.y = "OpenMRS Identification Number", all.x = TRUE)
+
+
+CAD6_delft <- read.table(file = "DataWrangling/CAD_delft_2018.csv", sep = ",", header = T, fill = T) 
+colnames(CAD6_delft)[7] <- "TID_Delft"
+CAD6_delft <- CAD6_delft[, -2]
+CAD6_delft <- CAD6_delft[, c(1, 2, 6, 9, 10)]
+
+QA.BGD <- read.csv(file = "./AI Scores/qXRv2.csv", header=T, sep=",")
+
+#### Radiologist TB, not TB ####
[…]

### 2020-01-22 DataWrangling/GlobalOption.R

@@ -1,0 +1,44 @@
+Sys.setenv(LANG = "en")
+knitr::opts_chunk$set(fig.width=8, fig.height=6, 
+                      echo=FALSE, warning=FALSE, message=FALSE)
+library(ggplot2)
+library(scales)
+library(epiR)
+library(ggthemes)
+library(RColorBrewer)
+library(plyr)
+library(reshape2)
+library(pROC)
+library(tidyverse)
+library(dplyr)
+library(lubridate)
+library(readxl)
+library(plotROC)
+library(flextable)
+library(DataExplorer)
+library("readxl")
+as.numeric.factor <- function(x) {as.numeric(levels(x))[x]}
+Mode <- function(x) {
+  ux <- unique(x)
+  ux[which.max(tabulate(match(x, ux)))]
+}
+
+MDF <- read.csv("DataWrangling/MDF.csv")
+
+# Make it long
+# MDF_long <- gather(MDF, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv2_100, IF1_100, IF2_100)
+# MDF_long <- gather(MDF, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv2_100, LunitScore_100, JF1_100, JF2_100, IF1_100, IF2_100, IF3_100)
+MDF_long <- gather(MDF, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv2_100, LunitScore_100, JF1_100, IF2_100)
+
+MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "CAD4TB6"] <- "CAD4TB"
+MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "qXRv2_100"] <- "qXR"
+MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "LunitScore_100"] <- "Lunit"
+MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "JF1_100"] <- "JF CXR-1"
+MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "JF2_100"] <- "JF2"
+MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "IF1_100"] <- "Infervision_TB 1 (product name??)"
+MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "IF2_100"] <- "Infervision"
[…]

### 2020-01-22 DataWrangling/Lunit dcm incomplete list.R

@@ -1,0 +1,19 @@
+dcm_list <- read.delim2("AI Scores/dcm_list_BD.txt", header = FALSE, sep = "/")
+dcm_list$V3 <- gsub(".dcm", "", dcm_list$V3)
+
+
+Lunit <- read_csv("AI Scores/result.csv")
+Lunit <- unique(Lunit)
+Lunit <- Lunit[, -c(1, 3:8)]
+colnames(Lunit)[2] <- "LunitScore"
+Lunit <- Lunit[is.na(Lunit$LunitScore)==F, ]
+Lunit$PatientID <- as.factor(Lunit$PatientID)
+
+dcm_list$complete <- Lunit$LunitScore[match(dcm_list$V3, Lunit$PatientID)]
+dcm_list <- dcm_list[, -c(1,2)]
+dcm_list <- dcm_list[is.na(dcm_list$complete), ]
+dcm_list$incomplete <- paste0("dicom_dir_BD/24K/", dcm_list$V3, ".dcm")
+
+dcm_list <- dcm_list[, -c(1,2)]
+
+write.table(dcm_list, file = "dcm_list_BD_IC.txt", sep = ",",row.names = FALSE, col.names = FALSE)

### 2020-01-22 Extreme AI score.R

@@ -1,0 +1,162 @@
+library(tableone)
+
+MDF[MDF$Xpert2Outcome_num %in% "1" & MDF$qXRv2_100 <0, c(1, 3, 7, 9, 14:19, 26:29)]
+
+LowQXR <- MDF[MDF$Xpert2Outcome_num %in% "1" & MDF$qXRv2_100 <45, c(1, 3, 7, 9, 14:19, 26:29)]
+# LowLunit <- MDF[MDF$Xpert2Outcome_num %in% "1" & MDF$LunitScore_100 <20, c(1, 5, 9,11, 16:21, 28, 31, 32)]
+LowCAD4TB <- MDF[MDF$Xpert2Outcome_num %in% "1" & MDF$CAD4TB6 <45, c(1, 3, 7, 9, 14:19, 26:29)]
+HighJF <- MDF[MDF$Xpert2Outcome_num %in% "0" & MDF$qXRv2_100 >80, c(1, 3, 7, 9, 14:19, 26:29)]
+
+
+## High JF score, false positive ------------------
+MDF$HighJF <- "Normal"
+MDF$HighJF[MDF$Xpert2Outcome_num %in% "0" & MDF$qXRv2_100 >80] <- "FP"
+
+# Define numeric variables
+listVar <- c("Age", "Gender",  "Xpert2Outcome_num", "MTB.Burden", "RIF.Result", "Radiology.Result", "rad.highly.TB", "rad.TB", "rad.abn", "CAD4TB6", "qXRv2", "LunitScore", "JF1", "HighJF")
+
+#Define categorical variables
+catVars <- c("Gender", "MTB.Burden", "Xpert2Outcome_num","RIF.Result",  "Radiology.Result", "rad.highly.TB", "rad.TB", "rad.abn", "HighJF")
+table1 <- CreateTableOne(vars = listVar, strata=c("HighJF"), data = MDF, factorVars = catVars)
+print(table1)
+
+
+# Every 5 point incremental ----------------
+MDF$CAD4TB_C <- cut(MDF$CAD4TB6, breaks = 50)
+MDF$qXR_C <- cut(MDF$qXRv2_100, breaks = 50)
+MDF$Lunit_C <- cut(MDF$LunitScore_100, breaks = 50)
+MDF$JF1_C <- cut(MDF$JF1_100, breaks = 50)
+MDF$JF2_C <- cut(MDF$JF2_100, breaks = 50)
+
+
[…]

### 2020-01-22 IDs.R

@@ -1,0 +1,5 @@
+BGD.PID.TID <- read.csv(file = "./Bangladesh PID_TID.csv", header=T, sep=",")
+
+summary(BGD.PID.TID)
+BGD.PID.TID$PID[BGD.PID.TID$Test.ID..DICOM.IMAGE.ID. %in% "#N/A"]
+BGD.PID.TID$PID[BGD.PID.TID$Test.ID..DICOM.IMAGE.ID. %in% "2010100001-4"]

### 2020-01-22 Logistic Regression.R

@@ -1,0 +1,35 @@
+```
+
+
+library(caTools)
+# set.seed(88)
+# split <- sample.split(MDF$Xpert2Outcome_num, SplitRatio = 0.75)
+# #get training and test data
+# MDF_train <- subset(MDF, split == TRUE)
+# MDF_test <- subset(MDF, split == FALSE)
+# NC.reg <- MDF
+# NC.reg <- subset(MDF, MDF$Country %in% "Nepal")
+
+
+model.null = glm(Xpert2Outcome_num ~ 1, 
+                 data=NC.reg,
+                 family = binomial(link="logit")
+)
+
+model.full <- glm (Xpert2Outcome_num ~ Age + Sex + Cough + Fever + WeightLoss + NightSweat + highLunit + TBHistory, 
+                   data = NC.reg, 
+                   family = binomial(link="logit"))
+
+
+step(model.null,
+     scope = list(upper=model.full),
+     direction="both",
+     test="Chisq",
+     data=NC.reg)
+
+final.model <- logistic.regression.or.ci(glm(formula = Xpert2Outcome_num ~ highLunit + Age + Cough + Sex + WeightLoss + Fever, family = binomial(link = "logit"), data = NC.reg))
+
+adjOR <- final.model$OR.ci
+adjOR <- round(cbind(final.model$OR, adjOR), 2)
+adjOR
+# OR <- paste(adjOR[,1], "(", adjOR[,2], "-", adjOR[,3], ")")

### 2020-01-22 SampleROC.py

@@ -1,0 +1,67 @@
+import numpy as np
+from scipy import interp
+import matplotlib.pyplot as plt
+
+from sklearn import svm, datasets
+from sklearn.metrics import auc
+from sklearn.metrics import plot_roc_curve
+from sklearn.model_selection import StratifiedKFold
+
+# #############################################################################
+# Data IO and generation
+
+# Import some data to play with
+iris = datasets.load_iris()
+X = iris.data
+y = iris.target
+X, y = X[y != 2], y[y != 2]
+n_samples, n_features = X.shape
+
+# Add noisy features
+random_state = np.random.RandomState(0)
+X = np.c_[X, random_state.randn(n_samples, 200 * n_features)]
+
+# #############################################################################
+# Classification and ROC analysis
+
+# Run classifier with cross-validation and plot ROC curves
+cv = StratifiedKFold(n_splits=6)
+classifier = svm.SVC(kernel='linear', probability=True,
+                     random_state=random_state)
+
+tprs = []
+aucs = []
+mean_fpr = np.linspace(0, 1, 100)
+
+fig, ax = plt.subplots()
+for i, (train, test) in enumerate(cv.split(X, y)):
+    classifier.fit(X[train], y[train])
+    viz = plot_roc_curve(classifier, X[test], y[test],
+                         name='ROC fold {}'.format(i),
+                         alpha=0.3, lw=1, ax=ax)
+    interp_tpr = interp(mean_fpr, viz.fpr, viz.tpr)
+    interp_tpr[0] = 0.0
+    tprs.append(interp_tpr)
+    aucs.append(viz.roc_auc)
+
+ax.plot([0, 1], [0, 1], linestyle='--', lw=2, color='r',
+        label='Chance', alpha=.8)
+
+mean_tpr = np.mean(tprs, axis=0)
+mean_tpr[-1] = 1.0
+mean_auc = auc(mean_fpr, mean_tpr)
+std_auc = np.std(aucs)
+ax.plot(mean_fpr, mean_tpr, color='b',
+        label=r'Mean ROC (AUC = %0.2f $\pm$ %0.2f)' % (mean_auc, std_auc),
+        lw=2, alpha=.8)
+
+std_tpr = np.std(tprs, axis=0)
+tprs_upper = np.minimum(mean_tpr + std_tpr, 1)
+tprs_lower = np.maximum(mean_tpr - std_tpr, 0)
[…]

### 2020-01-22 SubGroup.R

@@ -1,0 +1,81 @@
+## All
+
+library(precrec)
+library(ggplot2)
+
+ROCPRC <- function(dataset, dataset_long){
+  attr <- attributes(evalmod(scores = dataset$CAD4TB6, labels = dataset$Xpert2Outcome_num))
+  aucT1 <- c("CAD4TB ", round(attr$auc[4],3))
+  
+  attr <- attributes(evalmod(scores = dataset$qXRv2, labels = dataset$Xpert2Outcome_num))
+  aucT2 <- c("qXR ", round(attr$auc[4],3))
+  
+  attr <- attributes(evalmod(scores = dataset$LunitScore, labels = dataset$Xpert2Outcome_num))
+  aucT3 <- c("Lunit  ", round(attr$auc[4],3))
+  
+  attr <- attributes(evalmod(scores = dataset$JF1, labels = dataset$Xpert2Outcome_num))
+  aucT4 <- c("JF1 ", round(attr$auc[4],3))
+  
+  attr <- attributes(evalmod(scores = dataset$IF2, labels = dataset$Xpert2Outcome_num))
+  aucT5 <- c("Infervision ", round(attr$auc[4],3))
+  
+  # return(mmcurves)
+  # return(autoplot(mmcurves))
+  aucT <- c(aucT1, aucT2, aucT3, aucT4, aucT5)
+  return(aucT)
+}
+
+l <- ROCPRC(MDF, MDF_long)
+all <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+all$subgroup <- "all"
+
+
+## New only
+l <- ROCPRC(New, New_long)
+New <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+New$subgroup <- "New"
+
+## Old only
+l <- ROCPRC(Old, Old_long)
+Old <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+Old$subgroup <- "Old"
+
+## Young
+l <- ROCPRC(Young, Young_long)
+Young <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+Young$subgroup <- "Young"
+
+## Middle
+l <- ROCPRC(Middle, Middle_long)
+Middle <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+Middle$subgroup <- "Middle"
+
+## Senior
+l <- ROCPRC(Senior, Senior_long)W
[…]

### 2020-01-22 SubGroupPlotWithoutCI.R

@@ -1,0 +1,45 @@
+### Sensitivity vs Score
+base <- ggplot(SubgroupPlot, aes(Score, Sens)) + geom_path(aes(color = subgroup)) 
+
+sensCurve <- base + theme_light() + coord_equal() + labs(x = "Abnormality Score", y= "Sensitivity", subtitle = paste0("The Sensitivity vs abnormality score of ", unique(SubgroupPlot$DeepLearningSystem, " in different subgroups"))) +theme(legend.position = c(0.05,0.05), legend.justification = c("left", "bottom"))
+
+
+
+### PPV
+base <- ggplot(SubgroupPlot, aes(Score, ppv)) + geom_path(aes(color = subgroup)) 
+
+ppvCurve <- base + theme_light() + coord_equal() + labs(x = "Abnormality Score", y= "PPV", subtitle = paste0("The PPV vs abnormality score of ", unique(SubgroupPlot$DeepLearningSystem, " in different subgroups"))) +theme(legend.position = c(0.05,0.95), legend.justification = c("left", "top"))
+
+
+### Xpert Saved vs Score
+base <- ggplot(SubgroupPlot, aes(Score, X.XpertSaved)) + geom_path(aes(color = subgroup)) 
+
+XpertSavingCurve <- base + theme_light() + coord_equal() + labs(x = "Abnormality Score", y= "Xpert Saved", subtitle = paste0("The Xpert Saved vs abnormality score of ", unique(SubgroupPlot$DeepLearningSystem, " in different subgroups"))) +theme(legend.position = c(0.05,0.95), legend.justification = c("left", "top"))
+
+### Sens vs Xpert Saved
+base <- ggplot(SubgroupPlot, aes(X.XpertSaved, Sens)) + geom_path(aes(color = subgroup)) 
+
+XpertSens <- base + theme_light() + coord_equal() + labs(y = "Sensitivity", x= "Xpert Saved", subtitle = paste0("The Xpert Saved vs sensitivity of ", unique(SubgroupPlot$DeepLearningSystem, " in different subgroups"))) +theme(legend.position = c(0.05,0.05), legend.justification = c("left", "bottom"))
+
+### Specificity vs Score
+base <- ggplot(SubgroupPlot, aes(Score, Spec)) + geom_path(aes(color = subgroup))  
+
[…]

### 2020-01-22 baseZZ.py

@@ -1,0 +1,125 @@
+# Aim: To determine the sample set for which the sample confidence interval is within an expanded population confidence interval
+# for different arrangements of a sequential dataset
+
+from sklearn import metrics # for ROC and AUC calculations
+import pandas as pd # to work with csv files
+from scipy.stats import sem, t # for confidence intervals
+from scipy import mean
+import scipy.stats
+from scipy import stats
+from scipy.stats import norm
+import numpy as np
+import AUC_CI_DeLong
+confidence = 0.95
+
+# Create dataframe to store AUCs (Area Under R O Curve)
+dfAUC = pd.DataFrame(columns = ['AUC'])
+
+
+# # Make dataframe from csv file ---------------------------------------------------------------------------------------
+#df = pd.read_csv("C:/Users/zhizh/OneDrive - Stop TB Partnership/UNOPS/10 Paper Writing/CAR software/02 Bangladesh/CAR-Bangladesh/ProjectMachineBGD/Nepal_Cameroon.csv", usecols = ['ResearchID.x', 'XPERT_pos', 'CAD4TB6', 'qXR2', 'Lunit', 'Result.Date'])
+df = pd.read_csv("C:/Users/tasneemn/OneDrive - Stop TB Partnership/Documents/GitHub/ProjectMachine/Nepal_Cameroon.csv", usecols = ['ResearchID.x', 'XPERT_pos', 'CAD4TB6', 'qXR2', 'Lunit', 'Result.Date'])
+# Sort dataframe by result date and store
+df = df.sort_values(by = 'Result.Date')
+df.to_csv(r'C:/Users/tasneemn/OneDrive - Stop TB Partnership/Documents/GitHub/ProjectMachine/Nepal_Cameroon_sorted.csv')
+print(df)
+# ----------------------------------------------------------------------------------------------------------------------
+
+# Extract population AUC & CI: CAD4TB6
+# Extract true results and AI software scores from csv file and store in dataframe
+Data = pd.read_csv("Nepal_Cameroon_sorted.csv", usecols = ['XPERT_pos', 'CAD4TB6'])
+print(Data)
+
+data = Data
+count = 0
+
+# Calculate population confidence interval--------------------------------------------------------------------------
+alpha = .95
+y_pred = data['CAD4TB6']  # AI Scores
+y_true = data['XPERT_pos']  # True results
+
+# Calculate AUC
[…]

### 2020-01-22 pROC (old code) 06.11.rmd.R

@@ -1,0 +1,160 @@
+```{r ROC curving, echo= T}
+# ## CAD V3 score comparing with Xpert ####
+# roc(Xpert2Outcome_num ~ CAD4TB3, Master_df_complete)
+# ci.auc(Xpert2Outcome_num ~ CAD4TB3, Master_df_complete)
+# roc_all <- roc(Master_df_complete$Xpert2Outcome_num,
+#                Master_df_complete$CAD4TB3, percent=TRUE,
+#                plot=TRUE, auc.polygon=FALSE, max.auc.polygon=FALSE, grid=TRUE,
+#                print.auc=TRUE, show.thres=TRUE)
+# 
+# #### CAD V5 score (2016) comparing with Xpert ####
+# roc(Xpert2Outcome_num ~ CAD4TB5.old, Master_df_complete)
+# ci.auc(Xpert2Outcome_num ~ CAD4TB5.old, Master_df_complete)
+# 
+# roc_all <- roc(Master_df_complete$Xpert2Outcome_num,
+#                Master_df_complete$CAD4TB5.old, percent=TRUE,
+#                plot=TRUE, auc.polygon=FALSE, max.auc.polygon=FALSE, grid=TRUE,
+#                print.auc=TRUE, show.thres=TRUE)
+
+#### CAD V5 score (2018) comparing with Xpert ####
+roc(Xpert2Outcome_num ~ CAD4TB5, Master_df_complete)
+ci.auc(Xpert2Outcome_num ~ CAD4TB5, Master_df_complete)
+
+roc_all <- roc(Master_df_complete$Xpert2Outcome_num,
+               Master_df_complete$CAD4TB5, percent=TRUE,
+               plot=TRUE, auc.polygon=FALSE, max.auc.polygon=FALSE, grid=TRUE,
+               print.auc=TRUE, show.thres=TRUE)
+
+#### CAD V6 score (2018) comparing with Xpert ####
+roc(Xpert2Outcome_num ~ CAD4TB6, Master_df_complete)
+ci.auc(Xpert2Outcome_num ~ CAD4TB6, Master_df_complete)
+
+roc_all <- roc(Master_df_complete$Xpert2Outcome_num,
+               Master_df_complete$CAD4TB6, percent=TRUE,
+               plot=TRUE, auc.polygon=FALSE, max.auc.polygon=FALSE, grid=TRUE,
+               print.auc=TRUE, show.thres=TRUE)
+
[…]

### 2020-01-24 Draft.Rmd
t

@@
 # Methods
+With funding from the Stop TB Partnership’s TB REACH initiative, three TB Screening Centres (SCs) were established across Dhaka with a referral network of more than 2,000 private providers and 133 NTP facilities.
+Health providers in the network refer presumptive TB patients to the SCs to screen and test for TB.
+Public health facilities only refer the people with a negative smear microscopy but still suspected of having TB to the SCs.
+The TB SCs also receive walk-in clients with no referral history.
 
-## Summary of DL Systems 
-Through the network and the database of innovators developed under the TB REACH initiatives and the Accelerator for Impact project at Stop TB Partnership, we identified and contacted 15 (?
-TBC) DL system vendors regarding their interest in participating in the evaluation.
-Five AI products with stable version control were included in this study: CAD4TB (version 6), qXR (version 1) developed by Qure.ai (India), Lunit INSIGHT for Chest Radiography (Version 4.7.2) developed by Lunit (South Korea), JF CXR-1 developed by JF Healthcare (China) and InferRead®DR by Infervision (China).
-
-We used the latest versions available of the five DL systems in this evaluation.
-Both CAD4TB and Lunit read DICOM (Digital Imaging and Communications in Medicine) format only, while qXR can parse digital radiographs stored in PNG and JPEG.
-CAD4TB detects TB-specific abnormalities and outputs continuous abnormality scores ranging from 0 to 100.
-The greater the abnormality score, the higher probability of having TB.
-Current versions of qXR and Lunit detect several discrete pulmonary abnormalities, such as calcification, cavitation, opacities etc.
-Both systems present the final results for TB and the specific clinical abnormalities in binary (“Yes” / “No”) using a pre-defined threshold abnormality score.
-The abnormality scores for Lunit and qXR range from 0 to 100%.
-The default threshold abnormality score can be tuned based on screening requirements.
-All five DL systems can generate heat maps showing abnormalities.
-
-## Study Setting and Population
-With funding from the Stop TB Partnership’s TB REACH initiative, three TB Screening Centres (SCs) were established across Dhaka with a referral network of more than 2,000 private providers and 133 NTP facilities.
-The TB SCs were also open to walk-in clients with no referral history.
-Adults (> 15 years) presenting at any of the TB SCs were consecutively enrolled and were verbally screened for the presence of TB symptoms between 15 May 2014 and 4 October 2016.
-After providing informed consent, each participant received a posterior-anterior CXR using digital X-ray machines (Delft EZ DR X-ray) and was asked to submit a sputum sample for a free Xpert test.
+We consecutively enrolled all adults (> 15 years) presenting at any of the TB SCs between 15 May 2014 and 4 October 2016.
+After providing informed consent, each participant was verbally screened for symptoms and received a posterior-anterior CXR using digital X-ray machines (Delft EZ DR X-ray) and was asked to submit a sputum sample for a free Xpert test.
 Xpert test was performed again if the initial test failed (invalid, error, or no result).
-Demographic, symptom and medical history data were collected using OpenMRS.
-
+The final Xpert results were used as the bacteriological evidence and the refernece standard in this evaluation.
 A group of 3 Bangladeshi, board-certified radiologists (all with MD/MBSS degree in radiology and X,Y,Z years of experience??) read all of the CXR images remotely.
@@
 Anyone who was unable or unwilling to acquire a CXR was referred to a nearby public-sector health facility.
+
+Through the network and the database of innovators developed under the TB REACH initiatives and the Accelerator for Impact project at Stop TB Partnership, we identified and selected five DL systems with stable version control to be included included in this study: CAD4TB (version 6), qXR (version 1) developed by Qure.ai (India), Lunit INSIGHT for Chest Radiography (Version 4.7.2) developed by Lunit (South Korea), JF CXR-1 developed by JF Healthcare (China) and InferRead®DR by Infervision version 2 (China).We used the latest versions available of the five DL systems in this evaluation.
+Current versions of qXR and Lunit detect several discrete pulmonary abnormalities, such as calcification, cavitation, opacities etc.
+(to be updated with landscaping results).
+All five DL systems can generate heat maps showing abnormalities.
 The 5 DL systems scored the images remotely through Secured File Transfer Protocol from the Stop TB repository except for Delft, in which case the data was shared through cloud transfer.
@@
 
-## Data Analysis
-We used bacteriologically-confirmed TB outcomes tested with Xpert MTB/RIF to evaluate the accuracy of the 5 DL systems as well the decisions of the Bangladeshi radiologists.
-We plotted and describe the distribution of DL systems’ abnormality scores disaggregated by Xpert status and prior history of TB.
+All DL systems produce a continuous score (from 0 to 100 or from 0% to 100%) presenting the probability of presence of TB based on their DL algorithms.
+We assess the 5 DL systems firstly by describing the distribution of AI scores disaggregated by Xpert status and by prior history of TB.
 Mann-Whitney U test was used to compared non-normal distribution.
-
-We compared the performance of the 5 DL system to that of radiologists by selecting AI scores that match the sensitivity of the certified radiologists and compared the difference in specificity.
-We used the McNemar test on paired proportions to test if the difference in specificity of human readers and the 5 DL systems.
+Some vendors provide binary (“Yes” / “No”) for TB using a pre-defined threshold score.
+We choose the threshold cutoff to be comparative to the three categories used by the human readers (reading criteria described below).
+For example, for highly suggestive of TB, we chose the cutoff score to produce the same dichotomized screening decisions in terms of sensitivity and we compare the difference in specificity using McNemar test for paired proportions.
 
@@
 
-The histograms of the abnormality scores of the 5 DL systems were disaggregated by Xpert outcomes and prior TB history (Figure 1).
-The distributions of the scores in Xpert positive group were heavily left-skewed with JF CXR-1 having the highest left skewness `r round(skewness(MDF[MDF$Xpert2Outcome_num ==1, 31]),4)` and CAD4TB having the lowest left skewness `r round(skewness(MDF[MDF$Xpert2Outcome_num ==1, 27]),4)`.
-As expected the distributions in Xpert negative group were right-skewed except for CAD4TB with a left skewness of `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0, 27]),4)`, and Infervision has the highest right skewness of `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0, 33]),4)`.
+The distributions of the 5 DL systems' scores disaggregated by Xpert outcomes and prior TB history (Figure 1) were distinct, suggesting the algorithms are constructed differently.
+In terms of the segregation of Xpert positive and negative individuals, JF CXR-1's scores of Xpert positive were heavily left-skewed (skewness = `r round(skewness(MDF[MDF$Xpert2Outcome_num ==1, 31]),3)`, the green bars in Figure 1); whereas the Xpert positive individuals' CAD4TB scores were lest left skewed (skewness= `r round(skewness(MDF[MDF$Xpert2Outcome_num ==1, 27]),3)`), but still almost all above 50%.
+There were some noticeable outliers in the Xpert positive group whose AI scores were unexpectedly low, which represents true positive patients being missed or reduced sensitivity.
+
+There were many Xpert negative individuals have relatively high probablity scores. Noticeably some unexpectively had very high score (90-100) when read by JF CXR-1. 
+As expected the distributions in Xpert negative group were right-skewed except for CAD4TB with a left skewness of `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0, 27]),4)`, and Infervision has the highest right skewness of `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0, 33]),3)`.
+
 Noticeably, there are many distinct outliers: the far right side of the JF CXR-1's distribution in the Xpert negative group (score 90-100) and qXR in the Xpert negative group (score 70-90), far left sides of Lunit's and JF CXR-1's distribution in the Xpert negative group (score 0-10).
@@
 
-### Comparison with human readers
+### Comparison of sensitivity and specificity between human reading and the predictions of the DL systems
 ```{r}
 source("radiologist.R")
-humanAI <- read.csv("Results/HumanAI.csv")
-knitr::kable(humanAI[c(1,4,7,10,13, 2,5,8,11,14, 3,6,9,12,15), ], row.names = F)
+humanAI <- read.csv("Results/HumanAI.csv", )
+humanAI <- humanAI[c(3,6,9,12,15, 2,5,8,11,14, 1,4,7,10,13), -c(7, 9, 10)]
 
-# Any abnormality
-MDF$DL <- "negative"
-MDF$DL[MDF$CAD4TB6>= humanAI[humanAI$human.benchmark %in% "Any Abnormality" & humanAI$DL.System %in% "CAD4TB", 5]] <- "positive"
+knitr::kable(humanAI, row.names = F)
 ```
+
+Thresholds were chosen to match or exceed the performance of each human reader’s categories.
 
@@
 ###  Precision Recall Curve (Xpert Reference)
-```{r PRC precrec, eval=F}
-library(precrec)
-library(ggplot2)
-
-score <- as.list(data.frame(t(as.data.frame(matrix(MDF_long$AbnormalityScore, ncol = 24031, byrow = T)))))
-label <- as.list(data.frame(t(as.data.frame(matrix(MDF_long$Xpert2Outcome_num, ncol = 24031, byrow = T)))))
-# Explicitly specify model names
-# msmdat <- mmdata(score, label, modnames = c("CAD4TB", "qXR", "Lunit",  "JF1", "JF2", "Infervision 1", "Infervision 2", "Infervision 3"), dsids = c(1:8))
-msmdat <- mmdata(score, label, modnames = c("CAD4TB", "qXR", "Lunit",  "JF CXR-1", "Infervision 2"), dsids = c(1:5))
-mmcurves <- evalmod(msmdat)
-# Get a data frame with AUC scores
-  attr <- attributes(evalmod(scores = MDF$CAD4TB6, labels = MDF$Xpert2Outcome_num))
-  print(paste("CAD4TB= ", round(attr$auc[4],3)))
-  attr <- attributes(evalmod(scores = MDF$qXRv2, labels = MDF$Xpert2Outcome_num))
-  print(paste("qXR= ", round(attr$auc[4],3)))
-  attr <- attributes(evalmod(scores = MDF$LunitScore, labels = MDF$Xpert2Outcome_num))
-  print(paste("Lunit= ", round(attr$auc[4],3)))
-  attr <- attributes(evalmod(scores = MDF$JF1, labels = MDF$Xpert2Outcome_num))
-  print(paste("JF1= ", round(attr$auc[4],3)))
-  attr <- attributes(evalmod(scores = MDF$IF2, labels = MDF$Xpert2Outcome_num))
-  print(paste("Infervision= ", round(attr$auc[4],3)))
-
-autoplot(mmcurves)
-
-# autoplot(mmcurves, show_cb = TRUE)
-rm(score, label)
-```
 

### 2020-02-20 SubGroup.Rmd
subgroup changes

@@
 SubgroupPlotOrigin <- SubgroupPlot
+SubgroupPlot <- SubgroupPlotOrigin
+SubgroupPlot$subgroup <- as.character(SubgroupPlot$subgroup)
+
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "New"] <- "1.Without prior TB history"
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Old"] <- "2.With prior TB history"
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Young"] <- "3.Young [15,25)"
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Middle"] <- "4.Middle age [25,60)"
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Senior"] <- "5.Old age [60,108]"
+# SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% ""] <-
+# SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% ""] <-
+SubgroupPlot$subgroup <- as.factor(SubgroupPlot$subgroup)
 

### 2020-02-20 Chapter/4 Curves.R

@@ -14,7 +14,7 @@ CAD_Xpert_plot$Score[CAD_Xpert_plot$DeepLearningSystem %in% "CAD4TB"] <- CAD_Xpe
 base <- ggplot(CAD_Xpert_plot, aes(Score, Sens)) + geom_path(aes(color = DeepLearningSystem)) + 
   geom_ribbon(aes(x = Score, ymin = Sens_L, ymax = Sens_H, color = DeepLearningSystem, fill = DeepLearningSystem), alpha= 0.2) 
 
-sensCurve <- base + theme_light() + coord_equal() + labs(x = "Abnormality Score", y= "Sensitivity", subtitle = paste0("The Sensitivity vs abnormality score (n=", length(MDF$PID_OMRS), ")")) +theme(legend.position = c(0.05,0.05),legend.justification = c("left", "bottom")) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_x_continuous(minor_breaks = seq(0 , 1, 0.1), breaks = seq(0, 1, 0.1))+ scale_y_continuous(minor_breaks = seq(0 , 1, 0.1), breaks = seq(0, 1, 0.1)) + geom_vline(xintercept = c(0.75, 0.5), linetype="dotted", color = "blue", size=1) +theme(legend.position = "none")
+sensCurve <- base + theme_light() + coord_equal() + labs(x = "Abnormality Score", y= "Sensitivity", subtitle = paste0("The Sensitivity vs abnormality score (n=", length(MDF$PID_OMRS), ")")) +theme(legend.position = c(0.05,0.05),legend.justification = c("left", "bottom")) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_x_continuous(minor_breaks = seq(0 , 1, 0.1), breaks = seq(0, 1, 0.1))+ scale_y_continuous(minor_breaks = seq(0 , 1, 0.1), breaks = seq(0, 1, 0.1)) + geom_vline(xintercept = c(0.8, 0.7, 0.6), linetype="dotted", color = "blue", size=1) +theme(legend.position = "none")
 # sensCurveZoomIn <- sensCurve + coord_cartesian(xlim = c(0.5, 0.9), ylim = c(0.90, 1) ) +
 # ggtitle("Figure 2b: Zoomed-in view of the square marked part of Fig. 2a")+theme_light()
 
[…]

### 2020-02-20 DataWrangling/Cleaning.R

@@ -180,6 +180,8 @@ MDF <- MDF[, -c(3,4)]
 Master_df <- read.csv("AI Scores/Master_df.csv")
 MDF$Referral <- Master_df$type[match(MDF$PID_OMRS, Master_df$PID)]
 
+# Referral <- read.csv("DataWrangling/referral_source.csv")
+
 write.csv(MDF, "DataWrangling/MDF.csv")
 # rm(DOTS, Master_df_V5, Master_df_valid, Private_provider, Self, V5_only, CAD.cost, Radiologist.cost, Xpert.cost)
 

### 2020-03-11 Draft.Rmd
update

@@
 The improved theoretical understanding in AI technology, the ubiquity of large annotated datasets, and the advance in computer power have fostered a rapid expansion of the AI industry in medical diagnosis.
-
-Until recently, the most accurate AI methods for image analysis involved painstaking feature engineering, which requires manual image pre-processing, segmenting anatomic structures, and detecting or computing features suggested by an expert.
+Until recently, the most accurate AI methods for image analysis require feature manual segmentation of anatomic structures, detection or computation of specific features annotated by experts.
 The breakthrough in the ImageNet 2012 Challenges popularized the use of deep learning in neural networks to analyse medical images.
@@
 # Methods
-With funding from the Stop TB Partnership’s TB REACH initiative, three TB Screening Centres (SCs) were established across Dhaka with a referral network of more than 2,000 private providers and 133 NTP facilities.
-Health providers in the network refer presumptive TB patients to the SCs to screen and test for TB.
-Public health facilities only refer the people with a negative smear microscopy but still suspected of having TB to the SCs.
-The TB SCs also receive walk-in clients with no referral history.
-
-We consecutively enrolled all adults (> 15 years) presenting at any of the TB SCs between 15 May 2014 and 4 October 2016.
+In this retrospective study, we used data consecutively from all adults (> 15 years) presented any of the three TB Screening Centres (SCs), which were established by icddr,b with funding from the Stop TB Partnership's TB REACH Initiative, between 15 May 2014 and 4 October 2016.
+The three SCs cover a vast network of more than 2,000 private providers and 133 NTP facilities across Dhaka.
 After providing informed consent, each participant was verbally screened for symptoms and received a posterior-anterior CXR using digital X-ray machines (Delft EZ DR X-ray) and was asked to submit a sputum sample for a free Xpert test.
 Xpert test was performed again if the initial test failed (invalid, error, or no result).
-The final Xpert results were used as the bacteriological evidence and the refernece standard in this evaluation.
+The final Xpert results were used as the bacteriological evidence and the reference standard in this evaluation.
 A group of 3 Bangladeshi, board-certified radiologists (all with MD/MBSS degree in radiology and X,Y,Z years of experience??) read all of the CXR images remotely.
@@
 
-Through the network and the database of innovators developed under the TB REACH initiatives and the Accelerator for Impact project at Stop TB Partnership, we identified and selected five DL systems with stable version control to be included included in this study: CAD4TB (version 6), qXR (version 1) developed by Qure.ai (India), Lunit INSIGHT for Chest Radiography (Version 4.7.2) developed by Lunit (South Korea), JF CXR-1 developed by JF Healthcare (China) and InferRead®DR by Infervision version 2 (China).We used the latest versions available of the five DL systems in this evaluation.
-Current versions of qXR and Lunit detect several discrete pulmonary abnormalities, such as calcification, cavitation, opacities etc.
-(to be updated with landscaping results).
-All five DL systems can generate heat maps showing abnormalities.
+Through the network and the database of innovators developed under the TB REACH initiatives and the Accelerator for Impact project at Stop TB Partnership, we identified and selected five DL systems, all have stable version control, to be included in this study: CAD4TB (v6), qXR (v2) developed by Qure.ai (India), Lunit INSIGHT for Chest Radiography (v4.7.2) developed by Lunit (South Korea), JF CXR-1 (v2) developed by JF Healthcare (China) and InferRead®DR (v2) by Infervision (China).
 The 5 DL systems scored the images remotely through Secured File Transfer Protocol from the Stop TB repository except for Delft, in which case the data was shared through cloud transfer.
 All machine reading was performed independently with the developers blinded to all testing, clinical and demographic data.
-
-All DL systems produce a continuous score (from 0 to 100 or from 0% to 100%) presenting the probability of presence of TB based on their DL algorithms.
+All DL systems produce a continuous abnormality score (from 0 to 100 or from 0% to 100%) presenting the probability of presence of TB.
 We assess the 5 DL systems firstly by describing the distribution of AI scores disaggregated by Xpert status and by prior history of TB.
 Mann-Whitney U test was used to compared non-normal distribution.
-Some vendors provide binary (“Yes” / “No”) for TB using a pre-defined threshold score.
-We choose the threshold cutoff to be comparative to the three categories used by the human readers (reading criteria described below).
+
+Instead of depending on the pre-defined threshold scored selected by some vendors, we choose the threshold cutoff to be comparative to the three categories used by the human readers (reading criteria described below).
 For example, for highly suggestive of TB, we chose the cutoff score to produce the same dichotomized screening decisions in terms of sensitivity and we compare the difference in specificity using McNemar test for paired proportions.
@@
 
-A total of `r  length(MDF$X)` people were consecutively recruited from the three TB SCs.
-Excluding `r sum(is.na(MDF$rad.abn)==T)` individuals without a CXR and `r sum(MDF$Age<15)` individuals aged 15 or less, a total of `r sum(MDF$Age>=15)`  individuals were included in this analysis.
-The median age was `r T1$Overall[2]`, and the ratio between female and male participants was `r T1$Overall[3]`.
-Most participants `r T1$Overall[4]`,  reported coughing more than 14 days (or any cough?
-icddr,b please check), `r T1$Overall[5]` reported fever, `r T1$Overall[7]` reported weight loss; about half reported shortness of breath `r T1$Overall[6]`; `r  T1$Overall[8]` reported hemoptysis; and `r T1$Overall[10]` had prior TB medication history.
-Almost all, `r T1$Overall[9]` had at least one TB-related symptom.
-There are three sources of patients: the greatest proportion of test results came from people who were referred by their private provider (n=`r T1$Overall[24]`);  `r T1$Overall[25]` were referred from NTP facilities after a negative smear; and `r T1$Overall[26]` individuals walked-in / self-presented (Table 1).
+A total of 24,031 people were consecutively recruited from the three TB SCs.
+Excluding 17 individuals without a CXR and 107 individuals aged 15 or less, a total of `r sum(MDF$Age>=15)`  individuals were included in this analysis.
+The median age was `r T1$Overall[2]`, and `r paste0(substr(as.character(T1$Overall[[3]]), 13,16), "%")` were female, and almost all (`r paste0(substr(as.character(T1$Overall[[9]]), 8,11), "%")`) had at least one TB-related symptom.
+The most common symptoms are cough (`r paste0(substr(as.character(T1$Overall[[4]]), 8,11), "%")`), fever (`r paste0(substr(as.character(T1$Overall[[5]]), 8,11), "%")`), weight loss  (`r paste0(substr(as.character(T1$Overall[[7]]), 8,11), "%")`), and shorteness of breath (`r paste0(substr(as.character(T1$Overall[[6]]), 8,11), "%")`).
+Hemoptysis was only reported in `r paste0(substr(as.character(T1$Overall[[8]]), 8,11), "%")` participants.
+Noticeably, there were `r paste0(substr(as.character(T1$Overall[[10]]), 7,10), "%")` participants suspected of having TB already had prior TB history.
+The prevalence of bacteriologically-confirmed (Bac+) TB, confirmed by Xpert, in this population overall was `r paste0(substr(as.character(T1$Overall[[11]]), 7,10), "%")`.
+Among Bac+ individuals, `r percent(sum(MDF$RIF.Result %in% "Detected")/sum(MDF$Xpert2Outcome_num %in% "1"))` were resistant to rifampicin.
+The radiologists graded `r T1$Overall[25]` as Highly Suggestive, `r T1$Overall[26]` as Possibly TB, `r T1$Overall[27]` as Any Abnormality.
+The medians of the abnormality scores in Bac+ group were significantly different from those in the Xpert negative group were (Mann-Whitney U test <0.05) for all 5 DL systems.
 
-Across all referral groups,  `r T1$Overall[11]` MTB-positive TB patients were detected; the prevalence of Xpert positive TB was lowest among walk-ins: `r T1$WalkIn[11]` compared with `r T1$Private[11]` and `r T1$Public[11]` for other referral groups.
-Among people with MTB-positive results, `r percent(sum(MDF$RIF.Result %in% "Detected")/sum(MDF$Xpert2Outcome_num %in% "1"))` were resistant to rifampicin.
-The radiologists graded `r T1$Overall[27]` as Highly Suggestive, `r T1$Overall[28]` as Possibly TB, `r T1$Overall[29]` as Any Abnormality.
-The medians of the abnormality scores in Xpert positive groups were significantly different from those in the Xpert negative groups were (Mann-Whitney U test <0.05) for all 5 DL systems.
+There are three sources of patients: the greatest proportion of test results came from people who were referred by either public sector or private sector health providers (n=`r T1$Overall[22]`);  `r T1$Overall[23]` individuals were tested in NTP DOTS facilities after an inital negative smear; and `r T1$Overall[24]` individuals walked-in / self-presented (Table 1).
+Across all referral groups,  `r T1$Overall[11]` MTB-positive TB patients were detected; the prevalence of Xpert positive TB was lowest among walk-ins: `r T1$WalkIn[11]`, highest in the NTP DOTS retested subgroup (`r T1[6, 11]`).
 
 ### Histogram 
+![](Results/density.tif){width=900px}
 
-![](Results/Histogram.tif){width=900px}
-
-The distributions of the 5 DL systems' scores disaggregated by Xpert outcomes and prior TB history (Figure 1) were distinct, suggesting the algorithms are constructed differently.
-In terms of the segregation of Xpert positive and negative individuals, JF CXR-1's scores of Xpert positive were heavily left-skewed (skewness = `r round(skewness(MDF[MDF$Xpert2Outcome_num ==1, 31]),3)`, the green bars in Figure 1); whereas the Xpert positive individuals' CAD4TB scores were lest left skewed (skewness= `r round(skewness(MDF[MDF$Xpert2Outcome_num ==1, 27]),3)`), but still almost all above 50%.
-There were some noticeable outliers in the Xpert positive group whose AI scores were unexpectedly low, which represents true positive patients being missed or reduced sensitivity.
-
-There were many Xpert negative individuals have relatively high probablity scores. Noticeably some unexpectively had very high score (90-100) when read by JF CXR-1. 
-As expected the distributions in Xpert negative group were right-skewed except for CAD4TB with a left skewness of `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0, 27]),4)`, and Infervision has the highest right skewness of `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0, 33]),3)`.
-
-Noticeably, there are many distinct outliers: the far right side of the JF CXR-1's distribution in the Xpert negative group (score 90-100) and qXR in the Xpert negative group (score 70-90), far left sides of Lunit's and JF CXR-1's distribution in the Xpert negative group (score 0-10).
-Those with TB history but Xpert negative without in generally still have a high AI scores, especially in the case of JF CXR-I (the dark red bar), which we postulated resulted from issues in the algorithms' ability to differentiate between old scarring and active lesion.
+The stacked density plot in Fig-X shows the distributions of the 5 DL systems' scores disaggregated by Xpert outcomes and by prior TB history.
+The dark and light red bars were Bac negative and the dark and light green bars were Bac positive.
+An ideal test should have a density plot with all the red bars left skewed (positive skew) and all green bars right skewed with no overlap.
+Lunit's, qXR's and InferReadDR's density plot showed the dichomization pattern.
+Although almost all Bac positive patients received high abnormality scores (95-100) from JF CXR-1, so were many Bac negative patients, of which, mostly were healthy people but with a prior TB history (dark red), leading to excessive recall.
+When separately examine the distribution of the abnormality scores from the health people but with priro TB history, the distrbutions of all DL systems were right skewed, instead of left skewed (InferReadDR: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 33]),3)`,  qXR: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 28]),3)`, Lunit INSIGHT CXR: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 29]),3)`, CAD4TB: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 27]),3)`, and JF CXR-1: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 30]),3)`), which we postulated resulted from issues in the algorithms' ability to differentiate between old scarrings and active lesions.
 
@@
 humanAI <- read.csv("Results/HumanAI.csv", )
-humanAI <- humanAI[c(3,6,9,12,15, 2,5,8,11,14, 1,4,7,10,13), -c(7, 9, 10)]
-
 knitr::kable(humanAI, row.names = F)
@@
 
-Thresholds were chosen to match or exceed the performance of each human reader’s categories.
+To compare the DL systems withthe group of Bangladeshi radiologists, we choose thresholds to match the sensitivity of each grading made by the human readers.
+The grading of "highly suggestive of TB" had a low sensitivity of `r paste0(percent(Radiologist$Sens[1]), " (95%CI: ", percent(Radiologist$Sens_L[1]), " - ", percent(Radiologist$Sens_H[1]),")")` but a high specificity of `r paste0(percent(Radiologist$Spec[1]), " (95%CI: ", percent(Radiologist$Spec_L[1]), " - ", percent(Radiologist$Spec_H[1]),")")`.
+All 5 DL systems demonstrated statistically significant improvement in specificity.
+The increases in specificities range from 1.48% (CAD4TB) to 8.96% (Lunit INSIGHT CXR).
 
-If all patients with a chest x-ray graded as highly suggestive of TB by the radiologists had been tested by Xpert, the resulting sensitivity and specificity would be `r paste0(percent(Radiologist$Sens[1]), ", 95CI: (", percent(Radiologist$Sens_L[1]), " - ", percent(Radiologist$Sens_H[1]),")")` and `r paste0(percent(Radiologist$Spec[1]), ", 95CI: (", percent(Radiologist$Spec_L[1]), " - ", percent(Radiologist$Spec_H[1]),")")`.
-When approximate the sensitivity of this classification made by human readers, all 5 DL systems demonstrated statistically significant improvement in specificity (improvement ranging from 1.48% - 8.96%).
+If radiologists' rading of "Possibly TB" had been used to triage the follow-on Xpert testing, the resulting sensitivity would be `r paste0(percent(Radiologist$Sens[2]), " (95%CI: ", percent(Radiologist$Sens_L[2]), " - ", percent(Radiologist$Sens_H[2]), ")")` and the specificity would be `r paste0(percent(Radiologist$Spec[2]), " (95%CI: ", percent(Radiologist$Spec_L[2]), " - ", percent(Radiologist$Spec_H[2]), ")")`.
+The matching AI classificiation by the 5 DL systems continued showing statistical improvement in specificty.
+The increases in specificities range from 1.34% (JF CXR-1) to 7.62% (Lunit INSIGHT CXR).
 
-If radiologists' rading of "Possibly TB" had been used to triage the follow-on Xpert testing, the resulting sensitivity would be `r paste0(percent(Radiologist$Sens[2]), ", 95CI: (", percent(Radiologist$Sens_L[2]), " - ", percent(Radiologist$Sens_H[2]), ")")` and the specificity would be `r paste0(percent(Radiologist$Spec[2]), ", 95CI: (", percent(Radiologist$Spec_L[2]), " - ", percent(Radiologist$Spec_H[2]), ")")`.
-The matching AI classificiation by the 5 DL systems showed statistical improvement in specificty (improvement ranging from 1.34% - 7.62%).
+The grading of "any abnormality" has high sensitivity, `r paste0(percent(Radiologist$Sens[3]), " (95%CI: ", percent(Radiologist$Sens_L[3]), " - ", percent(Radiologist$Sens_H[3]), ")")`, but a reduced specificity, `r paste0(percent(Radiologist$Spec[3]), " (95%CI: ", percent(Radiologist$Spec_L[3]), " - ", percent(Radiologist$Spec_H[3]), ")")`.
+The matching AI classification statistically outperform in terms of specificity.
+qXR gained the highest in specificity (`r paste0(humanAI$Diff.specificity[12], " (95%CI: ", humanAI$CI[12], ")")`).
 
-The grading of Possibly TB" would have a sensitivity of `r paste0(percent(Radiologist$Sens[3]), ", 95CI: (", percent(Radiologist$Sens_L[3]), " - ", percent(Radiologist$Sens_H[3]), ")")` and specificity of `r paste0(percent(Radiologist$Spec[3]), ", 95CI: (", percent(Radiologist$Spec_L[3]), " - ", percent(Radiologist$Spec_H[3]), ")")`.
-
-Compared to the the human radiologists' grading encompassing any abnormality, the AI system demonstrated a statistically significant improvement in absolute specificity of 1.2% (95% confidence interval (CI) 0.29%, 2.1%; P = 0.0096 for superiority) and an improvement in absolute sensitivity of 2.7% (95% CI −3%, 8.5%; Extended Data Table 2a).
-
-###  ROC Curves
+###  Overall performance of 5 DL products
 
 ![](Results/Figure-2 ROCs.tif){width=900px}
-The ROC graph shows that regardless of the CAD4TB cut-off value selected, the software’s performance was inferior compared to the radiologist among all referral groups.
+We summarized the ROC curves by computing the area under the curve (AUC).
+
 The area under the curve (AUC) for all referral groups is 0.74 (95% CI: 0.73-0.75).
@@
 
-###  Precision Recall Curve (Xpert Reference)
+To rule out normal cases with high confidence, we used a very-low decision threshold. For the UK data, we achieved a negative predictive value (NPV) of 99.99% while retaining a specificity of 41.15%.
+
+###  Threthold Selection
 
 ![](Results/4 Curves.tif){width=900px}
+
+To rule out normal cases with high confidence, we used a very-low decision threshold. For the UK data, we achieved a negative predictive value (NPV) of 99.99% while retaining a specificity of 41.15%.
 
@@
 
-We observe that the performance of XXX PRODUCTS varies across age groups.
+We compared that the performance of 5 DL systems varies across age groups.
 We also find that all DL systems perform worse on XXX than on, which is consistent with the decreased sensitivity of radiologists for patients...
@@
 We hypothesize that this is due to age and prior TB hisotry there are more abnormality on the chest or old scaring influenced the detection of active TB.
+
+# Discussion
+
+The study show that the 5 DL prdocuts had clinical potential.
+The classificaitions made by the DL system coul be used to when skilled radiologists are scare in high TB burden countries which improve the standard of care.
+The AI system could also be used to provide automated, immediate feedback in the screening setting.

### 2020-03-11 Presentation.Rmd
update

---
title: "International Evaluation of AI Products for Tuberculosis Screening and Precision Diagnosis"
subtitle: "Zhi Zhen Qin"
date: "`r format(Sys.time(), '%d %B %Y')`"
email: "zhizhen.qin@gmail.com"

output: 
    # slidy_presentation:
    ioslides_presentation:
      widescreen: true
      css: 'scrollable_slides.css'
      # smaller: true
      # logo: StopTB-TBREACHLogo_RGB_140px.png

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=15, fig.height=12, echo=FALSE, warning=FALSE, message=FALSE)
```

## AI in Healthcare
AI is not a new concept - first coined in 1956 by John McCarthy, AI involves machines that can perform tasks that are characteristic of human intelligence.

Since then, AI has been in finance, insurance, marketing, etc, but has made few contributions to healthcare until recently.

ImageNet 2012 Challenge's breakthrough significantly improved performance of computer automated detection (CAD) technology to analyse large medical images.

Visual detection tools powered by AI such as CAD has a huge potential in medical practices.

## Challenge - Tuberculosis detection 
4 million people with TB are not diagnosed and reported annually, but can be detected by CXR screening.

    Identify more people to be tested (asymptomatic individuals).
    Cut down on the number of expensive Xpert tests that are needed - especially 
    when used in active / systematic case finding.

Several scientific articles found that trained radiologists are not available in places where TB is more prevalent.

CAD technology can identify TB-related abnormalities to triage people for testing.

![](Chapter/screening guideline.png){width=200px}

## Separating Reality from Hype

Several CAD solutions are available for TB, however, often the marketed accuracy is done on the same data superset for training, testing and validation and cannot be generalized to other setting.

All CAD solutions are limited as visual tools. But when we embed clinical relevant data along with CAD reading into predictive algorithms, computers can extract information and apply it to recommend the most appropriate differential diagnosis.

We conducted multi-site evaluation of the 5 CAD according the Standards for Reporting of Diagnostic Accuracy (STARD) Initiative on design and conduct of diagnostic accuracy evaluation.

## Evaluation Setup

<div class="black">
![](Results/Study Setup.png){width=1000px}

<center>
</center>

</div>

## Density Plots {.smaller}

<!-- ![](Results/Histogram.tif){width=900px}  -->

![](Results/density.png){width=900px}

</div>

<center>
</center>

## Human vs Machine{.smaller}

<center>
![](Results/HumanvsMachine.png){width=1000px}

</center>

## Which product to choose?

![](Chapter/PRC & ROC.png){width=1000px}

## Which product to choose in reality?
![](Chapter/Vendor Selection.png){width=1000px}

## Predictive Algorithms 
![](Chapter/AUCs - subgroup.png){width=1000px}

## Predictive Algorithms 
![](Chapter/Precision.png){width=800px}

## Precision Diagnosis
![](Chapter/algorithsm.png){width=650px}

# Thank you! 
Acknowledgement:

Stop TB Partnership/UNOPS

### 2020-03-11 SubGroup.Rmd
update

--- 2020-01-22 SubGroup.Rmd
@@
 
-Private <- subset(MDF, MDF$Referral %in% "Private Provider")
-Public <- subset(MDF, MDF$Referral %in% "Public DOTS Facilities")
-WalkIn <- subset(MDF, MDF$Referral %in% "Walk-in")
-Missing <- subset(MDF, is.na(MDF$Referral)==T)
+Referral <- subset(MDF, MDF$UseCase %in% "PrivatePublicReferral")
+DOTS <- subset(MDF, MDF$UseCase %in% "PublicDOTSRetesting")
+WalkIn <- subset(MDF, MDF$UseCase %in% "WalkIn")
+# Missing <- subset(MDF, is.na(MDF$UseCase)==T)
 
@@
 Senior_long <- MDF_long[MDF_long$AgeGroup %in% "[60,108]",]
-Private_long <- subset(MDF_long, MDF_long$Referral %in% "Private Provider")
-Public_long <- subset(MDF_long, MDF_long$Referral %in% "Public DOTS Facilities")
-WalkIn_long <- subset(MDF_long, MDF_long$Referral %in% "Walk-in")
-Missing_long <- subset(MDF_long, is.na(MDF_long$Referral)==T)
+
+Referral_long  <- subset(MDF_long, MDF_long$UseCase %in% "PrivatePublicReferral")
+DOTS_long  <- subset(MDF_long, MDF_long$UseCase %in% "PublicDOTSRetesting")
+WalkIn_long  <- subset(MDF_long, MDF_long$UseCase %in% "WalkIn")
+# Missing_long  <- subset(MDF, is.na(MDF$UseCase)==T)
 
@@
 # source("Chapter/Subgroup Table/Senior.R")
-# source("Chapter/Subgroup Table/Private.R")
-# source("Chapter/Subgroup Table/Public.R")
-# # write.csv(CAD_Xpert_plot_Middle, "Chapter/Subgroup Table/CAD_Xpert_plot_Middle.csv")
-# # write.csv(CAD_Xpert_plot_Young, "Chapter/Subgroup Table/CAD_Xpert_plot_Young.csv")
-# # write.csv(CAD_Xpert_plot_Senior, "Chapter/Subgroup Table/CAD_Xpert_plot_Senior.csv")
-# # write.csv(CAD_Xpert_plot_Private, "Chapter/Subgroup Table/CAD_Xpert_plot_Private.csv")
-# # write.csv(CAD_Xpert_plot_Public, "Chapter/Subgroup Table/CAD_Xpert_plot_Public.csv")
-# 
-# source("Chapter/Subgroup Table/WalkIn.R")
-# source("Chapter/Subgroup Table/Missing.R")
-# source("Chapter/Subgroup Table/New.R")
-# source("Chapter/Subgroup Table/Old.R")
-# 
-# 
-# # save(CAD_Xpert_plot_Young, "Young.rdata")
-# SubgroupTable <- rbind(CAD_Xpert_plot_New, CAD_Xpert_plot_Old, CAD_Xpert_plot_Young, CAD_Xpert_plot_Middle, CAD_Xpert_plot_Senior, CAD_Xpert_plot_Private, CAD_Xpert_plot_Public, CAD_Xpert_plot_WalkIn, CAD_Xpert_plot_Missing)
-# write.csv(SubgroupTable, "Chapter/Subgroup Table/SubgroupTable.csv")
+# source("Chapter/Subgroup Table/Referral.R")
+# source("Chapter/Subgroup Table/DOTS.R")
+# write.csv(CAD_Xpert_plot_Middle, "Chapter/Subgroup Table/CAD_Xpert_plot_Middle.csv")
+# write.csv(CAD_Xpert_plot_Young, "Chapter/Subgroup Table/CAD_Xpert_plot_Young.csv")
+# write.csv(CAD_Xpert_plot_Senior, "Chapter/Subgroup Table/CAD_Xpert_plot_Senior.csv")
+# write.csv(CAD_Xpert_plot_Referral, "Chapter/Subgroup Table/CAD_Xpert_plot_Referral.csv")
+# write.csv(CAD_Xpert_plot_DOTS, "Chapter/Subgroup Table/CAD_Xpert_plot_DOTS.csv")
+# write.csv(CAD_Xpert_plot_WalkIn, "Chapter/Subgroup Table/CAD_Xpert_plot_WalkIn.csv")
+# write.csv(CAD_Xpert_plot_New, "Chapter/Subgroup Table/CAD_Xpert_plot_New.csv")
+# write.csv(CAD_Xpert_plot_Old, "Chapter/Subgroup Table/CAD_Xpert_plot_Old.csv")
+
+CAD_Xpert_plot_Middle <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Middle.csv")
+CAD_Xpert_plot_Young <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Young.csv")
+CAD_Xpert_plot_Senior <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Senior.csv")
+CAD_Xpert_plot_DOTS <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_DOTS.csv")
+CAD_Xpert_plot_WalkIn <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_WalkIn.csv")
+CAD_Xpert_plot_Referral <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Referral.csv")
+CAD_Xpert_plot_New <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_New.csv")
+CAD_Xpert_plot_Old <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Old.csv")
+
+SubgroupTable <- rbind(CAD_Xpert_plot_New, CAD_Xpert_plot_Old, CAD_Xpert_plot_Young, CAD_Xpert_plot_Middle, CAD_Xpert_plot_Senior, CAD_Xpert_plot_Referral, CAD_Xpert_plot_DOTS, CAD_Xpert_plot_WalkIn)
+write.csv(SubgroupTable, "Chapter/Subgroup Table/SubgroupTable.csv", row.names = F)
+rm(list=(ls()))
+```
+
+```{r AUC}
+## All
+
+library(precrec)
+library(ggplot2)
+
+ROCPRC <- function(dataset, dataset_long){
+  attr <- attributes(evalmod(scores = dataset$CAD4TB6, labels = dataset$Xpert2Outcome_num))
+  aucT1 <- c("CAD4TB ", round(attr$auc[4],3))
+
+  attr <- attributes(evalmod(scores = dataset$qXRv2, labels = dataset$Xpert2Outcome_num))
+  aucT2 <- c("qXR ", round(attr$auc[4],3))
+
+  attr <- attributes(evalmod(scores = dataset$LunitScore, labels = dataset$Xpert2Outcome_num))
+  aucT3 <- c("Lunit INSIGHT CXR  ", round(attr$auc[4],3))
+
+  attr <- attributes(evalmod(scores = dataset$JF1, labels = dataset$Xpert2Outcome_num))
+  aucT4 <- c("JF CXR-1 ", round(attr$auc[4],3))
+
+  attr <- attributes(evalmod(scores = dataset$IF2, labels = dataset$Xpert2Outcome_num))
+  aucT5 <- c("InferReadDR ", round(attr$auc[4],3))
+
+  # return(mmcurves)
+  # return(autoplot(mmcurves))
+  aucT <- c(aucT1, aucT2, aucT3, aucT4, aucT5)
+  return(aucT)
+}
+
+l <- ROCPRC(MDF, MDF_long)
+all <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+all$subgroup <- "all"
+
+## New only
+l <- ROCPRC(New, New_long)
+New <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+New$subgroup <- "New"
+
+## Old only
+l <- ROCPRC(Old, Old_long)
+Old <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+Old$subgroup <- "Old"
+
+## Young
+l <- ROCPRC(Young, Young_long)
+Young <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+Young$subgroup <- "Young"
+
+## Middle
+l <- ROCPRC(Middle, Middle_long)
+Middle <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+Middle$subgroup <- "Middle"
+
+## Senior
+l <- ROCPRC(Senior, Senior_long)
+Senior <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+Senior$subgroup <- "Senior"
+
+## Referral only
+l <- ROCPRC(Referral, Referral_long)
+Referral <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+Referral$subgroup <- "Referral"
+
+## DOTS only
+l <- ROCPRC(DOTS, DOTS_long)
+DOTS <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+DOTS$subgroup <- "DOTS"
+
+## Walk-in only
+l <- ROCPRC(WalkIn, WalkIn_long)
+WalkIn <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+WalkIn$subgroup <- "WalkIn"
+
+# ## Missing 
+# l <- ROCPRC(Missing, Missing_long)
+# Missing <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+# Missing$subgroup <- "Missing"
+
+aucTable <- rbind(all, New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn)
+colnames(aucTable) <- c("DL System", "AUC", "PCAUC", "Subgroup")
+write.csv(aucTable, "Results/aucTable.csv")
+rm(list=(ls()))
+
 ```
@@
 # subgroup 4 curves
+
 SubgroupPlot <- read.csv("Chapter/Subgroup Table/SubgroupTable.csv")
@@
 SubgroupPlot$Score[SubgroupPlot$DeepLearningSystem %in% "CAD4TB"] <- SubgroupPlot$Score[SubgroupPlot$DeepLearningSystem %in% "CAD4TB"]/100
+SubgroupPlot$subgroup <- as.character(SubgroupPlot$subgroup)
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "New"] <- "1.New Case"
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Old"] <- "2.Previously Treated Case"
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Young"] <- "3.Young age [15,25)"
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Middle"] <- "4.Middle age [25,60)"
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Senior"] <- "5.Old age [60,108]"
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "DOTS"] <- "7.Public DOTS Retesting"
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Referral"] <-"6.Private Public Referral"
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "WalkIn"] <-"8.Walk In"
+SubgroupPlot$subgroup <- as.factor(SubgroupPlot$subgroup)
+
 SubgroupPlotOrigin <- SubgroupPlot
-
+# SubgroupPlot <- SubgroupPlotOrigin
 # Choose the DL System
@@
 ### AUC
-age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young", "Middle", "Senior"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young", "Middle", "Senior"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
 
-referral<-ggplot(aucTable[aucTable$Subgroup %in% c("Private", "Public", "WalkIn", "Missing"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+referral<-ggplot(aucTable[aucTable$Subgroup %in% c("Referral", "DOTS", "WalkIn"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
 
-history<-ggplot(aucTable[aucTable$Subgroup %in% c("New", "Old"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+history<-ggplot(aucTable[aucTable$Subgroup %in% c("New", "Old"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
 
 ### PRC
-agePC<-ggplot(aucTable[aucTable$Subgroup %in% c("Young", "Middle", "Senior"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
+agePC<-ggplot(aucTable[aucTable$Subgroup %in% c("Young", "Middle", "Senior"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
 
-referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("Private", "Public", "WalkIn", "Missing"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
+referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("Referral", "DOTS", "WalkIn"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
 
-historyPC<-ggplot(aucTable[aucTable$Subgroup %in% c("New", "Old"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
+historyPC<-ggplot(aucTable[aucTable$Subgroup %in% c("New", "Old"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
 
@@
 dev.off()
+rm(age, referral, history, agePC, referralPC, historyPC)
 ```

### 2020-03-11 Chapter/4 Curves.R

@@ -1,14 +1,10 @@
 source("DataWrangling/GlobalOption.R")
 
-CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE 4 digits.csv")
-CAD_Xpert_plot <- CAD_Xpert_plot[, -1]
-CAD_Xpert_plot$NNT <- 1/CAD_Xpert_plot$ppv
-CAD_Xpert_plot$NNT_H <- 1/CAD_Xpert_plot$PPV_L
-CAD_Xpert_plot$NNT_L <- 1/CAD_Xpert_plot$PPV_H
+CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE.csv")
+# CAD_Xpert_plot <- CAD_Xpert_plot[, -1]
 
 
-CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% c("IF1", "JF2", "IF3"), ]
-CAD_Xpert_plot$Score[CAD_Xpert_plot$DeepLearningSystem %in% "CAD4TB"] <- CAD_Xpert_plot$Score[CAD_Xpert_plot$DeepLearningSystem %in% "CAD4TB"]/100
+CAD_Xpert_plot <- subset(CAD_Xpert_plot, CAD_Xpert_plot$Site %in% "BGD")
 
 ### Sensitivity vs Score --------------------
 base <- ggplot(CAD_Xpert_plot, aes(Score, Sens)) + geom_path(aes(color = DeepLearningSystem)) + 
@@ -55,19 +51,19 @@ CAD_Xpert_plot$X_H <- 1-CAD_Xpert_plot$Spec_L
 base <- ggplot(CAD_Xpert_plot, aes(X, Sens)) + geom_path(aes(color = DeepLearningSystem)) + geom_ribbon(aes(x = X, ymin = Sens_L, ymax = Sens_H, color = DeepLearningSystem, fill = DeepLearningSystem), alpha= 0.2) 
 # + geom_ribbon(aes(y = Sens, xmin = X_L, xmax = X_H, color = DeepLearningSystem, fill = DeepLearningSystem), alpha= 0.2) 
 
[…]

### 2020-03-11 Chapter/Subgroup Table/DOTS.R

@@ -1,0 +1,507 @@
+source("DataWrangling/GlobalOption.R")
+source("radiologist.R")
+Radiologist <- Radiologist[c(1:3), ]
+
+Referral <- subset(MDF, MDF$UseCase %in% "PrivatePublicReferral")
+DOTS <- subset(MDF, MDF$UseCase %in% "PublicDOTSRetesting")
+WalkIn <- subset(MDF, MDF$UseCase %in% "WalkIn")
+# Missing <- subset(MDF, is.na(MDF$UseCase)==T)
+
+###### Qure.AI Score by 0.0001 #########
+qure_ai_score <- seq(0,1, by = 0.0001)
+
+mylist <- NULL
+mylist <- as.list(mylist)
+
+for (i in 1:10001){
+  myfunction <- function(CountryX, car.cutoff){
+    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
+    colnames(dat) <- c("Dis+","Dis-")
+    rownames(dat) <- c("Test+","Test-")
+    rval <- epi.tests(dat, conf.level = 0.95)
+    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
+    specificity <- as.vector(round((rval$elements$specificity),4))
+    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
+    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
+    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
+    
+    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
+    Score <- qure_ai_score[i]
+    
+    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
+    
+    return(accuracy)
+  }
+  
[…]

### 2020-03-11 Chapter/Subgroup Table/Private.R

@@ -1,506 +1,0 @@
-source("DataWrangling/GlobalOption.R")
-source("radiologist.R")
-Radiologist <- Radiologist[c(1:3), ]
-Private <- subset(MDF, MDF$Referral %in% "Private Provider")
-Public <- subset(MDF, MDF$Referral %in% "Public DOTS Facilities")
-WalkIn <- subset(MDF, MDF$Referral %in% "Walk-in")
-Missing <- subset(MDF, is.na(MDF$Referral)==T)
-
-###### Qure.AI Score by 0.0001 #########
-qure_ai_score <- seq(0,1, by = 0.0001)
-
-mylist <- NULL
-mylist <- as.list(mylist)
-
-for (i in 1:10001){
-  myfunction <- function(CountryX, car.cutoff){
-    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
-    colnames(dat) <- c("Dis+","Dis-")
-    rownames(dat) <- c("Test+","Test-")
-    rval <- epi.tests(dat, conf.level = 0.95)
-    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
-    specificity <- as.vector(round((rval$elements$specificity),4))
-    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
-    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
-    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
-    
-    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
-    Score <- qure_ai_score[i]
-    
-    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
-    
-    return(accuracy)
-  }
-  
[…]

### 2020-03-11 Chapter/Subgroup Table/Public.R

@@ -1,504 +1,0 @@
-source("DataWrangling/GlobalOption.R")
-source("radiologist.R")
-Radiologist <- Radiologist[c(1:3), ]
-Public <- subset(MDF, MDF$Referral %in% "Public DOTS Facilities")
-
-
-###### Qure.AI Score by 0.0001 #########
-qure_ai_score <- seq(0,1, by = 0.0001)
-
-mylist <- NULL
-mylist <- as.list(mylist)
-
-for (i in 1:10001){
-  myfunction <- function(CountryX, car.cutoff){
-    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
-    colnames(dat) <- c("Dis+","Dis-")
-    rownames(dat) <- c("Test+","Test-")
-    rval <- epi.tests(dat, conf.level = 0.95)
-    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
-    specificity <- as.vector(round((rval$elements$specificity),4))
-    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
-    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
-    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
-    
-    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
-    Score <- qure_ai_score[i]
-    
-    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
-    
-    return(accuracy)
-  }
-  
-  accuracy <- myfunction(Public, qure_ai_score[i])
-  mylist[[i]] <- list(accuracy)
-  
-}
-
-QureDF <- data.frame(matrix(unlist(mylist), nrow=10001, byrow=T))
[…]

### 2020-03-11 Chapter/Subgroup Table/Referral.R

@@ -1,0 +1,508 @@
+source("DataWrangling/GlobalOption.R")
+source("radiologist.R")
+Radiologist <- Radiologist[c(1:3), ]
+
+Referral <- subset(MDF, MDF$UseCase %in% "PrivatePublicReferral")
+DOTS <- subset(MDF, MDF$UseCase %in% "PublicDOTSRetesting")
+WalkIn <- subset(MDF, MDF$UseCase %in% "WalkIn")
+# Missing <- subset(MDF, is.na(MDF$UseCase)==T)
+
+
+###### Qure.AI Score by 0.0001 #########
+qure_ai_score <- seq(0,1, by = 0.0001)
+
+mylist <- NULL
+mylist <- as.list(mylist)
+
+for (i in 1:10001){
+  myfunction <- function(CountryX, car.cutoff){
+    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
+    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
+    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
+    colnames(dat) <- c("Dis+","Dis-")
+    rownames(dat) <- c("Test+","Test-")
+    rval <- epi.tests(dat, conf.level = 0.95)
+    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
+    specificity <- as.vector(round((rval$elements$specificity),4))
+    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
+    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
+    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
+    
+    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
+    Score <- qure_ai_score[i]
+    
+    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
+    
+    return(accuracy)
+  }
+  
[…]

### 2020-03-11 Chapter/Subgroup Table/SubGroupPlot.R

@@ -1,51 +1,71 @@
-### Sensitivity vs Score
+
+SubgroupPlot$NNT <- 1/SubgroupPlot$ppv
+SubgroupPlot$NNT_H <- 1/SubgroupPlot$PPV_L
+SubgroupPlot$NNT_L <- 1/SubgroupPlot$PPV_H
+
+### Sensitivity vs Score --------------------
 base <- ggplot(SubgroupPlot, aes(Score, Sens)) + geom_path(aes(color = subgroup)) + 
   geom_ribbon(aes(x = Score, ymin = Sens_L, ymax = Sens_H, color = subgroup, fill = subgroup), alpha= 0.2) 
 
-sensCurve <- base + theme_light() + coord_equal() + labs(x = "Abnormality Score", y= "Sensitivity", subtitle = paste0("The Sensitivity vs abnormality score of ", unique(SubgroupPlot$DeepLearningSystem, " in different subgroups"))) +theme(legend.position = c(0.05,0.05), legend.justification = c("left", "bottom"))
+sensCurve <- base + theme_light() + coord_equal() + labs(x = "Abnormality Score", y= "Sensitivity", subtitle = paste0("The Sensitivity vs abnormality score (n=", length(MDF$PID_OMRS), ")")) +theme(legend.position = c(0.05,0.05),legend.justification = c("left", "bottom")) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_x_continuous(minor_breaks = seq(0 , 1, 0.1), breaks = seq(0, 1, 0.1))+ scale_y_continuous(minor_breaks = seq(0 , 1, 0.1), breaks = seq(0, 1, 0.1)) + geom_vline(xintercept = c(0.8, 0.7, 0.6), linetype="dotted", color = "blue", size=1) +theme(legend.position = "none")
+# sensCurveZoomIn <- sensCurve + coord_cartesian(xlim = c(0.5, 0.9), ylim = c(0.90, 1) ) +
+# ggtitle("Figure 2b: Zoomed-in view of the square marked part of Fig. 2a")+theme_light()
 
 
 
-### PPV
-base <- ggplot(SubgroupPlot, aes(Score, ppv)) + geom_path(aes(color = subgroup)) + 
-  geom_ribbon(data = SubgroupPlot %>% filter(Score <0.95), aes(x = Score, ymin = PPV_L, ymax = PPV_H, color = subgroup, fill = subgroup), alpha= 0.2) 
+### NNT --------------------
[…]

### 2020-03-11 Chapter/Subgroup Table/WalkIn.R

@@ -3,7 +3,7 @@ source("radiologist.R")
 Radiologist <- Radiologist[c(1:3), ]
 Private <- subset(MDF, MDF$Referral %in% "Private Provider")
 Public <- subset(MDF, MDF$Referral %in% "Public DOTS Facilities")
-WalkIn <- subset(MDF, MDF$Referral %in% "Walk-in")
+WalkIn <- subset(MDF, MDF$Referral %in% "Walkin")
 Missing <- subset(MDF, is.na(MDF$Referral)==T)
 
 ###### Qure.AI Score by 0.0001 #########

### 2020-03-11 Chapter/Subgroup Table/Young.R

@@ -1,6 +1,6 @@
 ## Cutoff Table (Full)
-source("DataWrangling/GlobalOption.R")
-source("radiologist.R")
+# source("DataWrangling/GlobalOption.R")
+# source("radiologist.R")
 Radiologist <- Radiologist[c(1:3), ]
 
 

### 2020-03-11 Chapter/histogram.R

@@ -1,10 +1,5 @@
 source("DataWrangling/GlobalOption.R")
-MDF_long$XpertHistory <- ""
-MDF_long$XpertHistory[MDF_long$TB.Medication.History %in% "No" & MDF_long$Xpert2Outcome_num %in% "0"] <- "Xpert Negative - no TB History"
-MDF_long$XpertHistory[MDF_long$TB.Medication.History %in% "Yes" & MDF_long$Xpert2Outcome_num %in% "0"] <- "Xpert Negative - with TB History"
 
-MDF_long$XpertHistory[MDF_long$TB.Medication.History %in% "No" & MDF_long$Xpert2Outcome_num %in% "1"] <- "Xpert Positive - no TB History"
-MDF_long$XpertHistory[MDF_long$TB.Medication.History %in% "Yes" & MDF_long$Xpert2Outcome_num %in% "1"] <- "Xpert Positive - with TB History"
 
 
 ## Histogram
@@ -17,8 +12,8 @@ hist
 dev.off()
 
 ## Density plot
-p <- ggplot(MDF_long,aes(x=AbnormalityScore, fill=XpertHistory,))+ geom_histogram(position = 'identity', alpha=0.5, breaks=seq(0,100, by=5), aes(y = ..density.., fill = XpertHistory)) + xlab("Abnormality Scores of the Deep Learning Systems") 
-density <- p + facet_wrap(~DeepLearningSystem) + theme_minimal() + theme(legend.position = "top") +scale_fill_manual(values=c("#f7f7f7", "#fbb4b9", "#91003f", "#a1dab4", "#006d2c"))
+p <- ggplot(MDF_long,aes(x=AbnormalityScore, fill=XpertHistory,))+ geom_histogram(position = 'stack', alpha=0.5, breaks=seq(0,100, by=5), aes(y = ..density.., fill = XpertHistory)) + xlab("Abnormality Scores of the Deep Learning Systems") 
+density <- p + facet_wrap(~DeepLearningSystem) + theme_minimal() + theme(legend.position = "top") +scale_fill_manual(values=c("#f7f7f7", "#fbb4b9", "#91003f", "#a1dab4", "#006d2c"))+ scale_x_continuous(minor_breaks = seq(0 , 100, 10), breaks = seq(0 , 100, 10)) 
 density
 
 tiff("Results/density.tif", width = 14, height = 8, units = "in", res = 100)

### 2020-03-11 Chapter/humanAI.R

@@ -1,0 +1,55 @@
+source("radiologist.R")
+
+########### Human vs AI ####################
+SubgroupPlot <- read.csv("Chapter/Subgroup Table/SubgroupTable.csv")
+SubgroupPlot <- SubgroupPlot[, -1]
+
+CAD_Xpert_plot <- read.csv("Results/CAD_Xpert_Precise.csv")
+
+CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% c("IF1", "JF2", "IF3"), ]
+CAD_Xpert_plot <- CAD_Xpert_plot[CAD_Xpert_plot$Site %in% "BGD", ]
+
+# knitr::kable(Radiologist[(Radiologist$Referral %in% "MDF"), c(8, 10, 11)])
+Human <- Radiologist[(Radiologist$Referral %in% "MDF"), c(8, 10, 11, 4)]
+Human <- Human[c(3,2,1), ]
+Human <- rbind(Human, Human, Human, Human, Human)
+
+
+AI <- CAD_Xpert_plot[CAD_Xpert_plot$Comment !="" , c(17, 14, 4, 24, 25, 18)]
+AI$Subject <- paste(AI$DeepLearningSystem, AI$Comment)
+require(data.table)
+AI <- as.data.table(AI)
+# # knitr::kable(AI[AI[, .I[which.max(Spec)], by=Subject]$V1])
+AI <- AI[AI[, .I[which.max(Spec)], by=Subject]$V1]
+
+AI <- AI[grep("Radiologists' ", AI$Comment), ]
+humanAI <- cbind(Human, AI[, c(1,2,4, 5, 3)])
+humanAI$Diff <- percent(humanAI[, 9]- humanAI[, 4])
+humanAI <- humanAI[, c(1,2,3,5:8, 10, 9,4)]
+colnames(humanAI) <- c("Human Benchmark", "Sensitivity", "Specificy", "DL Product", "Score", "DL Sensitivity", "DL Specificity", "Difference", "specAI", "specH")
+
+
+### McNemar test specificity 
+healthy <- sum(MDF$Xpert2Outcome_num %in% "0")
+
+# library(readr)
+# humanAI <- read_csv("Results/humanAI.csv", 
+#                     col_types = cols(`Diff.specificity` = col_number()))
+humanAI$CI <- ""
+
+for (i in 1:15){
[…]

### 2020-03-11 Chapter/roc.R

@@ -1,9 +1,11 @@
 source("radiologist.R")
+CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE.csv")
+
+CAD_Xpert_plot <- subset(CAD_Xpert_plot, CAD_Xpert_plot$Site %in% "BGD")
+
 
 Radiologist <- Radiologist[Radiologist$Referral %in% "MDF", ]
 
-CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE 4 digits.csv")
-CAD_Xpert_plot <- CAD_Xpert_plot[, -1]
 
 CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% c("IF1", "JF2", "IF3"), ]
 
@@ -23,29 +25,26 @@ base <- ggplot(CAD_Xpert_plot, aes(X, Sens)) + geom_path(aes(color = DeepLearnin
   geom_ribbon(aes(x = X, ymin = Sens_L, ymax = Sens_H, color = DeepLearningSystem, fill = DeepLearningSystem), alpha= 0.2) 
 
 
-ggROC <- base + theme_minimal() + geom_abline(slope=1, intercept = 0, linetype = "dashed", alpha=0.7, color = "grey") + coord_equal()+ annotate("text", x = .75, y = .15, 
-                                                                                                                                                label = paste(" CAD4TB: ", round(roc_CAD6[2],2), " (95% CI:", round(roc_CAD6[1],2), "-", round(roc_CAD6[3],2), ")", "\n",
-                                                                                                                                                              "IF2: ", round(roc_IF2[2],2), " (95% CI:", round(roc_IF2[1],2), "-", round(roc_IF2[3],2), ")", "\n",
+ggROC <- base + theme_minimal() + geom_abline(slope=1, intercept = 0, linetype = "dashed", alpha=0.7, color = "grey") + coord_equal()+ annotate("text", x = .75, y = .15, label = paste(" CAD4TB: ", round(roc_CAD6[2],2), " (95% CI:", round(roc_CAD6[1],2), "-", round(roc_CAD6[3],2), ")", "\n", "InferReadDR: ", round(roc_IF2[2],2), " (95% CI:", round(roc_IF2[1],2), "-", round(roc_IF2[3],2), ")", "\n",
[…]

### 2020-03-11 Chapter/table1.R

@@ -4,14 +4,14 @@ source("DataWrangling/GlobalOption.R")
 library(tableone)
 
 # Define numeric variables
-listVar <- c("Age", "Gender", "Cough", "Fever", "Active.Breathing.Shortness", "Weight.Loss","Haemoptysis", "Symptoms", "TB.Medication.History", "Xpert2Outcome_num", "MTB.Burden", "RIF.Result", "Referral", "rad.highly.TB", "rad.TB", "rad.abn", "CAD4TB6", "qXRv2", "LunitScore", "JF1", "IF1", "IF2")
+listVar <- c("Age", "Gender", "Cough", "Fever", "Active.Breathing.Shortness", "Weight.Loss","Haemoptysis", "Symptoms", "TB.Medication.History", "Xpert2Outcome_num", "MTB.Burden", "RIF.Result", "UseCase", "rad.highly.TB", "rad.TB", "rad.abn", "CAD4TB6", "qXRv2", "LunitScore", "JF1", "IF1", "IF2")
 
 #Define categorical variables
-catVars <- c( "Gender", "Cough", "Fever", "Active.Breathing.Shortness", "Weight.Loss","Haemoptysis", "Symptoms", "TB.Medication.History", "Xpert2Outcome_num", "MTB.Burden", "RIF.Result", "Referral", "rad.highly.TB", "rad.TB", "rad.abn")
+catVars <- c( "Gender", "Cough", "Fever", "Active.Breathing.Shortness", "Weight.Loss","Haemoptysis", "Symptoms", "TB.Medication.History", "Xpert2Outcome_num", "MTB.Burden", "RIF.Result", "UseCase", "rad.highly.TB", "rad.TB", "rad.abn")
 
 
 table1 <- CreateTableOne(vars = listVar, strata=c("Xpert2Outcome_num"), data = MDF, factorVars = catVars)
-tableType <- CreateTableOne(vars = listVar, strata=c("Referral"), data = MDF, factorVars = catVars)
+tableType <- CreateTableOne(vars = listVar, strata=c("UseCase"), data = MDF, factorVars = catVars)
 
 table1.all <- CreateTableOne(vars = listVar, data = MDF, factorVars = catVars)
 
@@ -28,10 +28,10 @@ T1 <- cbind(table1DF, table1allDF, tabletypeDF)
 # colnames(T1) <- c("", "Xpert Positive", "Xpert Negative", "p test", "Overall")
 
[…]

### 2020-03-11 CutoffTable.R

@@ -1,506 +1,420 @@
-## Cutoff Table (Full)
-source("DataWrangling/GlobalOption.R")
-source("radiologist.R")
-Radiologist$Specificity <- paste(round(Radiologist$Spec, 3), "(", round(Radiologist$Spec_L, 3), "-", round(Radiologist$Spec_H,3), ")", sep = "")
-
-
-###### Qure.AI Score by 0.01 #########
-qure_ai_score <- seq(0,1, by = 0.01)
-
-mylist <- NULL
-mylist <- as.list(mylist)
-
-for (i in 1:101){
-  myfunction <- function(CountryX, car.cutoff){
-    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
-    colnames(dat) <- c("Dis+","Dis-")
-    rownames(dat) <- c("Test+","Test-")
-    rval <- epi.tests(dat, conf.level = 0.95)
-    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
-    specificity <- as.vector(round((rval$elements$specificity),4))
-    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
-    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
-    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
-    
-    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
-    Score <- qure_ai_score[i]
-    
-    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
-    
-    return(accuracy)
-  }
-  
-  accuracy <- myfunction(MDF, qure_ai_score[i])
-  mylist[[i]] <- list(accuracy)
-  
-}
-
[…]

### 2020-03-11 DataWrangling/GlobalOption.R

@@ -24,21 +24,35 @@ Mode <- function(x) {
 }
 
 MDF <- read.csv("DataWrangling/MDF.csv")
+MDF <- MDF[!MDF$UseCase %in% c("Community screening", "Contacts"), ]
+sum(is.na(MDF$GXP.Result)==T)
+MDF <- MDF[is.na(MDF$Radiology.Result)==F, ]
+MDF <- MDF[MDF$Age >=15, ]
+
 
 # Make it long
 # MDF_long <- gather(MDF, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv2_100, IF1_100, IF2_100)
 # MDF_long <- gather(MDF, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv2_100, LunitScore_100, JF1_100, JF2_100, IF1_100, IF2_100, IF3_100)
 MDF_long <- gather(MDF, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv2_100, LunitScore_100, JF1_100, IF2_100)
 
+MDF_long$DeepLearningSystem <- as.character(MDF_long$DeepLearningSystem)
+MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "IF2_100"] <- "InferReadDR"
+MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "LunitScore_100"] <- "Lunit INSIGHT CXR"
 MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "CAD4TB6"] <- "CAD4TB"
 MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "qXRv2_100"] <- "qXR"
-MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "LunitScore_100"] <- "Lunit"
 MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "JF1_100"] <- "JF CXR-1"
+
 MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "JF2_100"] <- "JF2"
-MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "IF1_100"] <- "Infervision_TB 1 (product name??)"
-MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "IF2_100"] <- "Infervision"
[…]

### 2020-03-11 Extreme AI score.R

@@ -92,21 +92,21 @@ CAD_Xpert_plot <- CAD_Xpert_plot[, -1]
 CAD_Xpert_plot2 <- CAD_Xpert_plot
 
 CAD_Xpert_plot <- CAD_Xpert_plot2[CAD_Xpert_plot2$DeepLearningSystem %in% "CAD4TB", ]
-cutoff <- CAD_Xpert_plot$Score[which(abs(CAD_Xpert_plot$Sens -0.95)==min(abs(CAD_Xpert_plot$Sens -0.95)))]
-length(MDF[MDF$CAD4TB < cutoff & MDF$Xpert2Outcome_num %in% "1", 2])
-MDF$CADMissed[MDF$CAD4TB < cutoff & MDF$Xpert2Outcome_num %in% "1"] <- "Missed by CAD4TB"
+cutoff <- CAD_Xpert_plot$Score[which(abs(CAD_Xpert_plot$Sens -0.95)==min(abs(CAD_Xpert_plot$Sens -0.95)))]*100
+length(MDF[MDF$CAD4TB6 < cutoff & MDF$Xpert2Outcome_num %in% "1", 2])
+MDF$CADMissed[MDF$CAD4TB6 < cutoff & MDF$Xpert2Outcome_num %in% "1"] <- "Missed by CAD4TB"
 
-CAD_Xpert_plot <- CAD_Xpert_plot2[CAD_Xpert_plot2$DeepLearningSystem %in% "IF2", ]
+CAD_Xpert_plot <- CAD_Xpert_plot2[CAD_Xpert_plot2$DeepLearningSystem %in% "InferReadDR", ]
 cutoff <- CAD_Xpert_plot$Score[which(abs(CAD_Xpert_plot$Sens -0.95)==min(abs(CAD_Xpert_plot$Sens -0.95)))]
-MDF$IF2Missed[MDF$IF2 < cutoff & MDF$Xpert2Outcome_num %in% "1"] <- "Missed by IF2"
+MDF$IF2Missed[MDF$IF2 < cutoff & MDF$Xpert2Outcome_num %in% "1"] <- "Missed by InferReadDR"
 
-CAD_Xpert_plot <- CAD_Xpert_plot2[CAD_Xpert_plot2$DeepLearningSystem %in% "JF1", ]
[…]

### 2020-03-11 SubGroup.R

@@ -1,81 +1,0 @@
-## All
-
-library(precrec)
-library(ggplot2)
-
-ROCPRC <- function(dataset, dataset_long){
-  attr <- attributes(evalmod(scores = dataset$CAD4TB6, labels = dataset$Xpert2Outcome_num))
-  aucT1 <- c("CAD4TB ", round(attr$auc[4],3))
-  
-  attr <- attributes(evalmod(scores = dataset$qXRv2, labels = dataset$Xpert2Outcome_num))
-  aucT2 <- c("qXR ", round(attr$auc[4],3))
-  
-  attr <- attributes(evalmod(scores = dataset$LunitScore, labels = dataset$Xpert2Outcome_num))
-  aucT3 <- c("Lunit  ", round(attr$auc[4],3))
-  
-  attr <- attributes(evalmod(scores = dataset$JF1, labels = dataset$Xpert2Outcome_num))
-  aucT4 <- c("JF1 ", round(attr$auc[4],3))
-  
-  attr <- attributes(evalmod(scores = dataset$IF2, labels = dataset$Xpert2Outcome_num))
-  aucT5 <- c("Infervision ", round(attr$auc[4],3))
-  
-  # return(mmcurves)
-  # return(autoplot(mmcurves))
-  aucT <- c(aucT1, aucT2, aucT3, aucT4, aucT5)
-  return(aucT)
-}
-
-l <- ROCPRC(MDF, MDF_long)
-all <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-all$subgroup <- "all"
-
-
-## New only
-l <- ROCPRC(New, New_long)
-New <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-New$subgroup <- "New"
-
-## Old only
-l <- ROCPRC(Old, Old_long)
-Old <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-Old$subgroup <- "Old"
-
-## Young
-l <- ROCPRC(Young, Young_long)
-Young <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-Young$subgroup <- "Young"
-
-## Middle
-l <- ROCPRC(Middle, Middle_long)
-Middle <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-Middle$subgroup <- "Middle"
-
-## Senior
-l <- ROCPRC(Senior, Senior_long)W
[…]

### 2020-03-11 radiologist.R

@@ -61,57 +61,14 @@ HumanReader <- function (dataset){
 
 
 allReferral <- HumanReader(MDF)
-Private <- HumanReader(subset(MDF, MDF$Referral %in% "Private Provider"))
-Public <- HumanReader(subset(MDF, MDF$Referral %in% "Public DOTS Facilities"))
-WalkIn <- HumanReader(subset(MDF, MDF$Referral %in% "Walk-in"))
-Missing <- HumanReader(subset(MDF, is.na(MDF$Referral)==T))
+Referral <- HumanReader(subset(MDF, MDF$UseCase %in% "PrivatePublicReferral"))
+DOTS <- HumanReader(subset(MDF, MDF$UseCase %in% "PublicDOTSRetesting"))
+WalkIn <- HumanReader(subset(MDF, MDF$UseCase %in% "WalkIn"))
+Missing <- HumanReader(subset(MDF, is.na(MDF$UseCase)==T))
 
-Radiologist <- rbind(allReferral, Private, Public, WalkIn, Missing)
-rm(allReferral, Private, Public, WalkIn, Missing)
-Radiologist$Sensitivity <- paste0(percent(Radiologist$Sens), ", (", percent(Radiologist$Sens_L), " - ", percent(Radiologist$Sens_H), ")")
-Radiologist$Specificity <- paste0(percent(Radiologist$Spec), ", (", percent(Radiologist$Spec_L), " - ", percent(Radiologist$Spec_H), ")")
+Radiologist <- rbind(allReferral, Referral, DOTS, WalkIn, Missing)
+rm(allReferral, Referral, DOTS, WalkIn, Missing)
+Radiologist$Sensitivity <- paste0(percent(Radiologist$Sens), ", (", percent(Radiologist$Sens_L, suffix = ""), "-", percent(Radiologist$Sens_H), ")")
+Radiologist$Specificity <- paste0(percent(Radiologist$Spec), ", (", percent(Radiologist$Spec_L, suffix = ""), "-", percent(Radiologist$Spec_H), ")")
 
-
-########### Human vs AI ####################
-SubgroupPlot <- read.csv("Chapter/Subgroup Table/SubgroupTable.csv")
-SubgroupPlot <- SubgroupPlot[, -1]
-
[…]

### 2020-03-22 SubGroup.Rmd
update

@@
 SubgroupTable <- rbind(CAD_Xpert_plot_New, CAD_Xpert_plot_Old, CAD_Xpert_plot_Young, CAD_Xpert_plot_Middle, CAD_Xpert_plot_Senior, CAD_Xpert_plot_Referral, CAD_Xpert_plot_DOTS, CAD_Xpert_plot_WalkIn)
-write.csv(SubgroupTable, "Chapter/Subgroup Table/SubgroupTable.csv", row.names = F)
-rm(list=(ls()))
+# write.csv(SubgroupTable, "Chapter/Subgroup Table/SubgroupTable.csv", row.names = F)
+# rm(list=(ls()))
 ```
@@
 New <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-New$subgroup <- "New"
+New$subgroup <- "New cases"
 
@@
 Old <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-Old$subgroup <- "Old"
+Old$subgroup <- "Previously treated cases"
 
@@
 Young <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-Young$subgroup <- "Young"
+Young$subgroup <- "Young age"
 
@@
 Middle <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-Middle$subgroup <- "Middle"
+Middle$subgroup <- "Middle age"
 
@@
 Senior <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-Senior$subgroup <- "Senior"
+Senior$subgroup <- "Old age"
 
@@
 Referral <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-Referral$subgroup <- "Referral"
+Referral$subgroup <- "Referred"
 
@@
 DOTS <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-DOTS$subgroup <- "DOTS"
+DOTS$subgroup <- "DOTS retested"
 
@@
 write.csv(aucTable, "Results/aucTable.csv")
-rm(list=(ls()))
+# rm(list=(ls()))
 
@@
 ### AUC
-age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young", "Middle", "Senior"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
 
-referral<-ggplot(aucTable[aucTable$Subgroup %in% c("Referral", "DOTS", "WalkIn"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+referral<-ggplot(aucTable[aucTable$Subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
 
-history<-ggplot(aucTable[aucTable$Subgroup %in% c("New", "Old"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+history<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
 
 ### PRC
-agePC<-ggplot(aucTable[aucTable$Subgroup %in% c("Young", "Middle", "Senior"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
+agePC<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
 
-referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("Referral", "DOTS", "WalkIn"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
+referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
 
-historyPC<-ggplot(aucTable[aucTable$Subgroup %in% c("New", "Old"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
+historyPC<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
 

### 2020-03-22 Chapter/4 Curves.R

@@ -1,70 +1,0 @@
-source("DataWrangling/GlobalOption.R")
-
-CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE.csv")
-# CAD_Xpert_plot <- CAD_Xpert_plot[, -1]
-
-
-CAD_Xpert_plot <- subset(CAD_Xpert_plot, CAD_Xpert_plot$Site %in% "BGD")
-
-### Sensitivity vs Score --------------------
-base <- ggplot(CAD_Xpert_plot, aes(Score, Sens)) + geom_path(aes(color = DeepLearningSystem)) + 
-  geom_ribbon(aes(x = Score, ymin = Sens_L, ymax = Sens_H, color = DeepLearningSystem, fill = DeepLearningSystem), alpha= 0.2) 
-
-sensCurve <- base + theme_light() + coord_equal() + labs(x = "Abnormality Score", y= "Sensitivity", subtitle = paste0("The Sensitivity vs abnormality score (n=", length(MDF$PID_OMRS), ")")) +theme(legend.position = c(0.05,0.05),legend.justification = c("left", "bottom")) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_x_continuous(minor_breaks = seq(0 , 1, 0.1), breaks = seq(0, 1, 0.1))+ scale_y_continuous(minor_breaks = seq(0 , 1, 0.1), breaks = seq(0, 1, 0.1)) + geom_vline(xintercept = c(0.8, 0.7, 0.6), linetype="dotted", color = "blue", size=1) +theme(legend.position = "none")
-# sensCurveZoomIn <- sensCurve + coord_cartesian(xlim = c(0.5, 0.9), ylim = c(0.90, 1) ) +
-# ggtitle("Figure 2b: Zoomed-in view of the square marked part of Fig. 2a")+theme_light()
-
-
-
-### NNT --------------------
-base <- ggplot(CAD_Xpert_plot, aes(Score, NNT)) + geom_path(aes(color = DeepLearningSystem)) 
-# + geom_ribbon(data = CAD_Xpert_plot %>% filter(Score <0.95), aes(x = Score, ymin = NNT_L, ymax = NNT_H, color = DeepLearningSystem, fill = DeepLearningSystem), alpha= 0.2) 
-
[…]

### 2020-03-22 Chapter/5 Curves.R

@@ -1,0 +1,74 @@
+source("DataWrangling/GlobalOption.R")
+
+CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE.csv")
+
+
+CAD_Xpert_plot <- subset(CAD_Xpert_plot, CAD_Xpert_plot$Site %in% "BGD")
+
+### Sensitivity vs Score --------------------
+base <- ggplot(CAD_Xpert_plot, aes(Score, Sens)) + geom_path(aes(color = DeepLearningSystem)) 
+# + geom_ribbon(aes(x = Score, ymin = Sens_L, ymax = Sens_H, color = DeepLearningSystem, fill = DeepLearningSystem), alpha= 0.2) 
+
+sensCurve <- base + theme_light() + coord_equal() + labs(x = "Abnormality Score", y= "Sensitivity", subtitle = paste0("The Sensitivity vs abnormality score (n=", length(MDF$PID_OMRS), ")")) +theme(legend.position = c(0.05,0.05),legend.justification = c("left", "bottom")) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_x_continuous(minor_breaks = seq(0 , 1, 0.1), breaks = seq(0, 1, 0.1))+ scale_y_continuous(minor_breaks = seq(0 , 1, 0.1), breaks = seq(0, 1, 0.1)) + geom_vline(xintercept = c(0.8, 0.7), linetype="dotted", color = "blue", size=1) +theme(legend.position = "none")
+# sensCurveZoomIn <- sensCurve + coord_cartesian(xlim = c(0.5, 0.9), ylim = c(0.90, 1) ) +
+# ggtitle("Figure 2b: Zoomed-in view of the square marked part of Fig. 2a")+theme_light()
+
+
+
+### NNT --------------------
+base <- ggplot(CAD_Xpert_plot, aes(Score, NNT)) + geom_path(aes(color = DeepLearningSystem)) 
+# + geom_ribbon(data = CAD_Xpert_plot %>% filter(Score <0.95), aes(x = Score, ymin = NNT_L, ymax = NNT_H, color = DeepLearningSystem, fill = DeepLearningSystem), alpha= 0.2) 
+
[…]

### 2020-03-22 Chapter/roc.R

@@ -25,27 +25,34 @@ base <- ggplot(CAD_Xpert_plot, aes(X, Sens)) + geom_path(aes(color = DeepLearnin
   geom_ribbon(aes(x = X, ymin = Sens_L, ymax = Sens_H, color = DeepLearningSystem, fill = DeepLearningSystem), alpha= 0.2) 
 
 
-ggROC <- base + theme_minimal() + geom_abline(slope=1, intercept = 0, linetype = "dashed", alpha=0.7, color = "grey") + coord_equal()+ annotate("text", x = .75, y = .15, label = paste(" CAD4TB: ", round(roc_CAD6[2],2), " (95% CI:", round(roc_CAD6[1],2), "-", round(roc_CAD6[3],2), ")", "\n", "InferReadDR: ", round(roc_IF2[2],2), " (95% CI:", round(roc_IF2[1],2), "-", round(roc_IF2[3],2), ")", "\n",
-                                                                                                                                                              # "IF3: ", round(roc_IF3[2],2), " (95% CI:", round(roc_IF3[1],2), "-", round(roc_IF3[3],2), ")", "\n",
-                                                                                                                                                              "JF CXR-1: ", round(roc_JF1[2],2), " (95% CI:", round(roc_JF1[1],2), "-", round(roc_JF1[3],2), ")", "\n",
-                                                                                                                                                              # "JF2: ", round(roc_JF2[2],2), " (95% CI:", round(roc_JF2[1],2), "-", round(roc_JF2[3],2), ")", "\n",
-                                                                                                                                                              # "IF1: ", round(roc_IF1[2],2), " (95% CI:", round(roc_IF1[1],2), "-", round(roc_IF1[3],2), ")", "\n",
[…]

### 2020-03-22 Draft.Rmd
update

@@
 ```{r Global_options, include=FALSE}
-knitr::opts_chunk$set(fig.width=15, fig.height=12, echo=FALSE, warning=FALSE, message=FALSE)
+knitr::opts_chunk$set(fig.width=15, fig.height=18, echo=FALSE, warning=FALSE, message=FALSE)
 library(moments)
@@
 All DL systems produce a continuous abnormality score (from 0 to 100 or from 0% to 100%) presenting the probability of presence of TB.
+
+## Data Analysis 
 We assess the 5 DL systems firstly by describing the distribution of AI scores disaggregated by Xpert status and by prior history of TB.
@@
 
-Instead of depending on the pre-defined threshold scored selected by some vendors, we choose the threshold cutoff to be comparative to the three categories used by the human readers (reading criteria described below).
-For example, for highly suggestive of TB, we chose the cutoff score to produce the same dichotomized screening decisions in terms of sensitivity and we compare the difference in specificity using McNemar test for paired proportions.
+To compare the performance of the radiologists and the 5 DL systems, we choose the threshold scores to produce the same dichotomized decisions as the radiologists in terms of sensitivity and we compared the difference in specificity using McNemar test for paried proportions.
 
 We evaluated and compared the overall performance of the 5 DL systems using threshold-free measurements.
-In additional to the area under receiver operating characteristic (ROC) curves (AUC), which shows the tradeoff between sensitivity and specificity with varying thresholds, we also calculated and compared the area under Precision-Recall (PRC) curve (PRAUC), which shows precision values for corresponding sensitivity values and is more informative than the ROC curve when evaluating binary classifier on imbalanced datasets.
-[Saito 2015].
-We also plotted sensitivity, specificity, and PPV with varying AI scores to understand the influence of the selection of cutoff threshold scores on programmatic performance.
-We plotted the proportion of Xpert saved  against sensitivity to understand the sensitivity loss as further testing is triaged
+We calculated the area under receiver operating characteristic (ROC) curves (AUC), which shows the tradeoff between sensitivity and specificity with varying thresholds.
+However, since the occurance of TB and not TB is imbalanced, we also calculated the area under Precision-Recall (PRC) curve (PRAUC), which shows precision values for corresponding sensitivity values and is more informative than the ROC curve when evaluating binary classifier on imbalanced datasets [Saito 2015].
+
+In this paper, we also proposed a new analytic framework to evaluate screening and triage tests with continous output and understand threshold selection by factoring in the ability of reduce subsequent confirmation testing and its trade off with sensitivity.
+We used two parameters to measure the ability of triage following testings: 1) the porportion of Xpert saved where  0% saved represents everyone receive a Xpert test regardless of CXR results and 2) umber of subsequent Xpert needed to test (NNT) to find one Bac+ patient.
+The dynamic among sensitivity, proportion of Xpert saved and NNT was visualized by ploting them with varying decision threshold in a three-way plot.
 
@@
 The most common symptoms are cough (`r paste0(substr(as.character(T1$Overall[[4]]), 8,11), "%")`), fever (`r paste0(substr(as.character(T1$Overall[[5]]), 8,11), "%")`), weight loss  (`r paste0(substr(as.character(T1$Overall[[7]]), 8,11), "%")`), and shorteness of breath (`r paste0(substr(as.character(T1$Overall[[6]]), 8,11), "%")`).
-Hemoptysis was only reported in `r paste0(substr(as.character(T1$Overall[[8]]), 8,11), "%")` participants.
+Hemoptysis was only reported in `r paste0(substr(as.character(T1$Overall[[8]]), 8,10), "%")` participants.
 Noticeably, there were `r paste0(substr(as.character(T1$Overall[[10]]), 7,10), "%")` participants suspected of having TB already had prior TB history.
@@
 
-There are three sources of patients: the greatest proportion of test results came from people who were referred by either public sector or private sector health providers (n=`r T1$Overall[22]`);  `r T1$Overall[23]` individuals were tested in NTP DOTS facilities after an inital negative smear; and `r T1$Overall[24]` individuals walked-in / self-presented (Table 1).
-Across all referral groups,  `r T1$Overall[11]` MTB-positive TB patients were detected; the prevalence of Xpert positive TB was lowest among walk-ins: `r T1$WalkIn[11]`, highest in the NTP DOTS retested subgroup (`r T1[6, 11]`).
+Three general types of patients visited the TB screening and test centre.
+The greatest proportion of test results came from people who were referred by either public sector or private sector health providers (n=`r T1$Overall[22]`);  `r T1$Overall[23]` individuals were tested in NTP DOTS facilities after an inital negative smear; and `r T1$Overall[24]` individuals walked-in / self-presented (Table 1).
+Across the three groups, the prevalence of Xpert positive TB was lowest among walk-ins: `r T1$WalkIn[11]`, highest in the NTP DOTS retested subgroup (`r T1[11,6]`).
 
-### Histogram 
+### Density plot 
 ![](Results/density.tif){width=900px}
 
-The stacked density plot in Fig-X shows the distributions of the 5 DL systems' scores disaggregated by Xpert outcomes and by prior TB history.
+The stacked density plot in Fig-X shows the distributions of the 5 DL systems’ scores disaggregated by Xpert outcomes and by prior TB history.
 The dark and light red bars were Bac negative and the dark and light green bars were Bac positive.
+The distributions of the 5 DL systems differ, indicating the underlying models are different.
 An ideal test should have a density plot with all the red bars left skewed (positive skew) and all green bars right skewed with no overlap.
-Lunit's, qXR's and InferReadDR's density plot showed the dichomization pattern.
-Although almost all Bac positive patients received high abnormality scores (95-100) from JF CXR-1, so were many Bac negative patients, of which, mostly were healthy people but with a prior TB history (dark red), leading to excessive recall.
-When separately examine the distribution of the abnormality scores from the health people but with priro TB history, the distrbutions of all DL systems were right skewed, instead of left skewed (InferReadDR: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 33]),3)`,  qXR: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 28]),3)`, Lunit INSIGHT CXR: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 29]),3)`, CAD4TB: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 27]),3)`, and JF CXR-1: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 30]),3)`), which we postulated resulted from issues in the algorithms' ability to differentiate between old scarrings and active lesions.
+Lunit’s, qXR’s and InferReadDR’s density plot demonstrated this dichotomization pattern.
+Although almost all Bac positive patients received high abnormality scores (95-100) from JF CXR-1, so were many Bac negative patients, of which, mostly were healthy people but with a prior TB history (dark red), which can lead to excessive recall.
+When separately examine the distribution of the abnormality scores from the health people but with prior TB history, none of the DL systems has a left skewed distribution (InferReadDR: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 33]),3)`,  qXR: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 28]),3)`, Lunit INSIGHT CXR: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 29]),3)`, CAD4TB: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 27]),3)`, and JF CXR-1: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 30]),3)`), which we postulated resulted from issues in the algorithms' ability to differentiate between old scarrings and active lesions.
 
@@
 
-###  Overall performance of 5 DL products
+###  ROC & PRC
+```{r Overall performance}
+source("Chapter/roc.R")
 
-![](Results/Figure-2 ROCs.tif){width=900px}
-We summarized the ROC curves by computing the area under the curve (AUC).
+Supp_Tab <- read_csv("Results/Supp Tab.csv")
+Supp_Tab$Score[Supp_Tab$DeepLearningSystem %in% "CAD4TB"] <- Supp_Tab$Score[Supp_Tab$DeepLearningSystem %in% "CAD4TB"]/100
+Supp_Tab <- subset(Supp_Tab, Supp_Tab$Site %in% "BGD")
+# View(Supp_Tab)
+Supp_Tab <- Supp_Tab[Supp_Tab$Score %in% c(0.6, 0.7, 0.8), c(2:4, 8, 9)]
+knitr::kable(Supp_Tab)
+```
 
-The area under the curve (AUC) for all referral groups is 0.74 (95% CI: 0.73-0.75).
-The CAD4TB software performed significantly better among walk-ins (AUC 0.84, 95% CI: 0.81-0.87) compared to people referred from NTP facilities (AUC 0.77, 95% CI: 0.74-0.79) and private providers (AUC 0.72, 95% CI: 0.70-0.73).
+![](Results/5 Curves.tif){width=900px}
 
-To rule out normal cases with high confidence, we used a very-low decision threshold. For the UK data, we achieved a negative predictive value (NPV) of 99.99% while retaining a specificity of 41.15%.
+The tradeoffs between sensitivity and specificity of the 5 DL systems can be visualized in the ROC graphs in Figure X.
+The area under the ROC curve (AUCs) from high to low are AUC.
+The differneces in AUCs of Lunit INSIGHT, qXR and CAD4TB are statistically significant, but there is no statistic significance in the difference between JF CXR-1 and InferReadDR.
+The ROC curves and precision recall curves of InferReadDR and JF CXR-1 almost completely overlap.
+However, for most of the decision thresholds (approximately above 0.15), JF CXR-1 has higher sensitivity, but less following Xpert saving ability and higher required NNT than InferReadDR.
+For instance, at 0.8 cutoff theshold, JF CXR-1 has the highest sensitivity, `r Supp_Tab[12,3]`, but the lowest proprotion of Xpert saved, `r Supp_Tab[12,5]`,  and the highest NNT `r Supp_Tab[12,4]`.
+However, InferReadDR has the lowest sensitivity, `r Supp_Tab[9,3]`, but has significantly saving (`r Supp_Tab[9,5]`) of triaged testing; the NNT is reduced to `r Supp_Tab[9,4]`.
 
-###  Threthold Selection
+Figure x shows that all 5 DL systems can reduce at least 50% of the follow-on testing and still keeping high sensitivity above 90%.
+However, as more follow-on tests are triaged (especially >60%), the 5 DL systems demonstrated difference in sensitivity.
+For instance, when the follow-on testing is reduced by 2/3, the sensitivity is between 85%-77% with Lunit INSIGHT CXR and qXR have the highest sensitivity, followed by JF CXR-1 and InferReadDR and CAD4TB.
 
-![](Results/4 Curves.tif){width=900px}
+At the cutoff point 0.7, using CAD4TB, Lunit INSIGHT CXR and qXR can save similar proportion of following xpert testing (60%), however, the sensitivity of CAD4TB is less than qXR & Lunit.
 
-To rule out normal cases with high confidence, we used a very-low decision threshold. For the UK data, we achieved a negative predictive value (NPV) of 99.99% while retaining a specificity of 41.15%.
+### Thresholding 
+The sensitivity of CAD4TB decreased slowly between 100% and around 95% at around 0.5 cutoff threshold, then the sensitivity descresed sharply as the cutoff score increases.
+JF CXR-1's sensitivity remains above 90% for most of the decision points which then decrease greatly as the cutoff score greater than 0.93.
+Both Lunit INSIGHT CXR and qXR have similar pattern, sensitivity is maintained above 80% for most of the cutoff thresholds and as decision scores increases from 0.8, the sensitivities sharply decreased.
 
-### Results across age and prior TB history
+It is also clear that there is no universal cutoff point that can be applied to all products.
+for example, to achevie at least 90% sensitivity, the required cutoff scores for InferReadDR must be below 0.35, Lunit 0.59, CAD4TB & qXR 0.62, JF CXR-1 can be any poitn below 0.93.
+
+<!-- Furthermore, to better map a probablity score to a TB/not TB binary category by thresholding,  -->
+### Subgroup Analysis
 
@@
 
-We compared that the performance of 5 DL systems varies across age groups.
-We also find that all DL systems perform worse on XXX than on, which is consistent with the decreased sensitivity of radiologists for patients...
-Differences in the model’s performance in benign/not benign classification is larger than in malignant/not malignant classification.
-We hypothesize that this is due to age and prior TB hisotry there are more abnormality on the chest or old scaring influenced the detection of active TB.
+We compared that the performance of the 5 DL systems across age groups, sources of patient and prior TB history.
+We find that all 5 DL systems perform worse in old age (above 65 year old) than in yong age (15-25 year old) and middle age (25-65 year old).
+The difference in the DL systems' performance in people with and without prior TB history is profound.
+We hypothesize that the abnormalities on the chest due to age and prior TB hisotry influenced the classification of active TB.
 

### 2020-04-04 Draft.Rmd
update

@@
 library(moments)
+library(scales)
 ```
@@
 # Introduction
+
 The improved theoretical understanding in AI technology, the ubiquity of large annotated datasets, and the advance in computer power have fostered a rapid expansion of the AI industry in medical diagnosis.
-Until recently, the most accurate AI methods for image analysis require feature manual segmentation of anatomic structures, detection or computation of specific features annotated by experts.
-The breakthrough in the ImageNet 2012 Challenges popularized the use of deep learning in neural networks to analyse medical images.
+Until recently, the most accurate AI methods for image analysis required manual segmentation and computation of specific features annotated by experts.
+Since 2012, deep learning in neural networks is increasingly being used to analyse medical images, such as chest x-rays (CXR).
+
+CXR is recommended by the World Health Organization (WHO) as a screening and triage tool for tuberculosis (TB), a disease which kills more people than any single infectious disease world-wide.
+However, the use of CXR is limited due to high inter-and intra-reader variability and low specificity.
+Additionally, there is a lack of qualified radiologists who can quickly read CXR films in high TB burden countries.
+AI technology presents a promising solution to overcome these obstacles.
+Such technology makes use of neural networks and deep learning to identify TB-related abnormalities on chest radiographs.
 Inspired by the human nervous system, neural networks are interconnected functions, each comprised of a weight and a bias coefficient.
 In deep learning, the networks are trained using large sets of known positive and negative data (ground truth) in multiple hidden layers.
-The networks “learn” by adjusting the weights and biases of the underlying functions based on the difference between predictions and ground, a process called back-propagation.
-The increased computational power makes it possible for a complex deep learning network to modify itself using a large training dataset so that the resulting trained algorithms can identify new and unseen data.
+The networks “learn” by adjusting the weights and biases of the underlying functions based on the difference between predictions and ground truth, a process called back-propagation.
+A complex deep learning network can modify and ‘train’ itself using a large training dataset, enabling it to identify new and unseen data.
 
-These AI algorithms provide opportunities for new solutions to tackle tuberculosis (TB), a disease kills more people world-wide than any single infectious disease.
-Immediately identifying TB presumptives or patients is critical to prevent further spread of the infection.
-Chest x-ray is recommended by the World Health Organization (WHO) as a screening and triage test prior to the use of Xpert MTB/RIF.
-However, there is a lack of qualified radiologists who can quickly read CXR films in many high TB burden countries.
-Several AI companies have emerged in recent years promising to quickly screen digital chest-radiographs to identify people in need of further diagnostic testing for TB.
+How exactly AI algorithms detect TB abnormality is unclear, even to those who developed them, and how the algorithms were constructed is a fiercely guarded trade secret, earning AI the “black box” reputation.
+Furthermore, often the marketed accuracy of AI software is done on the same data superset for training, testing and validation and cannot be generalized to other settings.
 
-However, like most AI algorithms, no one knows how exactly the resulting algorithms work, not even the engineers who developed them, earning AI the “black boxes” reputation.
-Companies are not eager to share how exactly they built their algorithms as this is extremely valuable and it is a fiercely guarded trade secret.
-Often the marketed accuracy is done on the same data superset for training, testing and validation and cannot be generalized to other setting.
-Current scientific evidence is limited and mostly available for one product, CAD4TB (Delft Imaging Systems, Netherlands).
-However, significant changes have been made to the latest version (v6) of CAD4TB and it has limited publication.
-There is only one peer-reviewed publication on the performance of other DL systems for detecting TB abnormalities with a relatively small dataset.
+Several AI companies have emerged in recent years promising to quickly screen digital chest-radiographs to identify people in need of further confirmation testing for TB.
+However, current scientific evidence is limited and mostly available for an earlier version of one product, CAD4TB (Delft Imaging Systems, Netherlands).
+There is one peer-reviewed publication on the performance of other AI software for detecting TB abnormalities with a relatively small dataset.
 WHO has not made a recommendation on the use of automated reading systems for TB due to the current lack of evidence [WHO].
-In response to this, we evaluated multiple DL systems available for TB screening and triage using a large dataset unseen by any AI developers to help National TB Programmes, medical professionals and patients to assess the true diagnostics accuracy of these algorithms.
+In response to this, we evaluated multiple AI software available for TB screening and triage using a large dataset unseen by any AI developers to help National TB Programmes, medical professionals and patients to assess the true diagnostics accuracy of these algorithms.
 
 # Methods
-In this retrospective study, we used data consecutively from all adults (> 15 years) presented any of the three TB Screening Centres (SCs), which were established by icddr,b with funding from the Stop TB Partnership's TB REACH Initiative, between 15 May 2014 and 4 October 2016.
-The three SCs cover a vast network of more than 2,000 private providers and 133 NTP facilities across Dhaka.
+In this retrospective study, we used data consecutively from all adults (> 15 years), presented in any of the three TB Screening Centres established by icddr,b, with funding from the Stop TB Partnership’s TB REACH Initiative, between 15 May 2014 and 4 October 2016.
+The three TB centres cover a vast network of more than 2,000 private providers and 133 NTP facilities across Dhaka.
 After providing informed consent, each participant was verbally screened for symptoms and received a posterior-anterior CXR using digital X-ray machines (Delft EZ DR X-ray) and was asked to submit a sputum sample for a free Xpert test.
@@
 The final Xpert results were used as the bacteriological evidence and the reference standard in this evaluation.
-A group of 3 Bangladeshi, board-certified radiologists (all with MD/MBSS degree in radiology and X,Y,Z years of experience??) read all of the CXR images remotely.
-The radiologists were blinded to all testing and clinical (and demographic data??
-icddr,b please confirm) data and provided standard radiology reports and graded each CXR as follows (criteria to be attached): a.
-Highly Suggestive: including highly suggestive of TB only, b.
-Possibly TB: including abnormality highly suggestive of TB and possibly associated with TB, c.
+A group of 3 Bangladeshi, board-certified radiologists (all with MD/MBSS degree in radiology and X,Y,Z  years of experience) read all of the CXR images remotely.
+The radiologists were blinded to all testing and clinical (and demographic data ) data and provided standard radiology reports.
+They graded each CXR as follows (criteria to be attache d): a.
+Highly Suggestive of TB: including highly suggestive of TB only, b.
+Possibly TB: including abnormality highly suggestive of TB and abnormality possibly associated with TB, c.
 Any Abnormality: including abnormality highly suggestive of TB, possibly associated with TB and non-TB abnormality, d.
@@
 
-Through the network and the database of innovators developed under the TB REACH initiatives and the Accelerator for Impact project at Stop TB Partnership, we identified and selected five DL systems, all have stable version control, to be included in this study: CAD4TB (v6), qXR (v2) developed by Qure.ai (India), Lunit INSIGHT for Chest Radiography (v4.7.2) developed by Lunit (South Korea), JF CXR-1 (v2) developed by JF Healthcare (China) and InferRead®DR (v2) by Infervision (China).
+We identified five DL systems with stable version control through the network and the database of innovators developed under the TB REACH initiatives and the Accelerator for Impact (a4i) project at Stop TB Partnership.
+to  include in this study: CAD4TB (v6), qXR (v2) developed by Qure.ai (India), Lunit INSIGHT for Chest Radiography (v4.7.2) developed by Lunit (South Korea), JF CXR-1 (v2) developed by JF Healthcare (China) and InferRead®DR (v2) by Infervision (China).
 The 5 DL systems scored the images remotely through Secured File Transfer Protocol from the Stop TB repository except for Delft, in which case the data was shared through cloud transfer.
-All machine reading was performed independently with the developers blinded to all testing, clinical and demographic data.
-All DL systems produce a continuous abnormality score (from 0 to 100 or from 0% to 100%) presenting the probability of presence of TB.
+All machine reading was performed independently, with the developers blinded to all testing, clinical and demographic data.
+All DL systems produce a continuous abnormality score (from 0 to 100 or from 0% to 100%) which presents/represents the probability of presence of TB.
 
 ## Data Analysis 
-We assess the 5 DL systems firstly by describing the distribution of AI scores disaggregated by Xpert status and by prior history of TB.
+We first compared the performance of the group of Bangladeshi radiologists and the 5 DL systems, using bacteriological results as the ground truth.
+We calculated the sensitivity and specificity of the following radiologists’ reading, 1) Highly Suggestive of TB, 2) Possibly TB: , and 3) Any Abnormality.
+The threshold scores of the DL systems were chosen to produce the same dichotomized decisions as the radiologists in terms of sensitivity for each human reading category.
+We compared the difference in specificity of the human reading and of the predictions from the 5 DL systems using McNemar test for paired proportions.
+
+We compared the overall performance of the 5 DL systems using the area under receiver operating characteristic (ROC) curves (AUC), which shows the tradeoff between sensitivity and specificity with varying thresholds.
+However, since the occurrence of TB and not TB is imbalanced, we also calculated the area under Precision-Recall (PRC) curve (PRAUC), which shows precision values for corresponding sensitivity values and is more informative than the ROC curve when evaluating binary classifier on imbalanced datasets [Saito 2015].
+
+We proposed a new analytic framework to evaluate screening and triage tests with continuous output and understand threshold selection by factoring in the ability of reduce subsequent confirmation testing which is measured by 1) the proportion of subsequent Xpert saved where 0% saved represents everyone receive a Xpert test regardless of CXR results and 2) the number of subsequent Xpert needed to test (NNT) to find one Bac+ patient.
+We plotted the sensitivity against the proportion of Xpert saved to show the tradeoff between finding as many Bac+ patients as possible and the cost saving of each DL systems.
+Additionally, to help our understanding in threshold selection, we plotted the dynamic among sensitivity, proportion of Xpert saved and NNT was visualized with varying decision threshold in a three-way plot.
+We then assess the distribution of abnormality scores disaggregated by Xpert status and by prior history of TB.
 Mann-Whitney U test was used to compared non-normal distribution.
 
-To compare the performance of the radiologists and the 5 DL systems, we choose the threshold scores to produce the same dichotomized decisions as the radiologists in terms of sensitivity and we compared the difference in specificity using McNemar test for paried proportions.
-
-We evaluated and compared the overall performance of the 5 DL systems using threshold-free measurements.
-We calculated the area under receiver operating characteristic (ROC) curves (AUC), which shows the tradeoff between sensitivity and specificity with varying thresholds.
-However, since the occurance of TB and not TB is imbalanced, we also calculated the area under Precision-Recall (PRC) curve (PRAUC), which shows precision values for corresponding sensitivity values and is more informative than the ROC curve when evaluating binary classifier on imbalanced datasets [Saito 2015].
-
-In this paper, we also proposed a new analytic framework to evaluate screening and triage tests with continous output and understand threshold selection by factoring in the ability of reduce subsequent confirmation testing and its trade off with sensitivity.
-We used two parameters to measure the ability of triage following testings: 1) the porportion of Xpert saved where  0% saved represents everyone receive a Xpert test regardless of CXR results and 2) umber of subsequent Xpert needed to test (NNT) to find one Bac+ patient.
-The dynamic among sensitivity, proportion of Xpert saved and NNT was visualized by ploting them with varying decision threshold in a three-way plot.
-
-Furthermore, we divided the test set by patient age, prior TB history and referral types to evaluate the performance of the 5 DL systems in each subpopulation in terms of AUC and PRAUC.
+Finally, we divided the test population by patient age, prior TB history and referral types to evaluate the performance of the 5 DL systems in each subpopulation in terms of AUC.
 
@@
 
-A total of 24,031 people were consecutively recruited from the three TB SCs.
+A total of 24,031 people were consecutively recruited from the three TB SCscentres.
 Excluding 17 individuals without a CXR and 107 individuals aged 15 or less, a total of `r sum(MDF$Age>=15)`  individuals were included in this analysis.
@@
 Across the three groups, the prevalence of Xpert positive TB was lowest among walk-ins: `r T1$WalkIn[11]`, highest in the NTP DOTS retested subgroup (`r T1[11,6]`).
-
-### Density plot 
-![](Results/density.tif){width=900px}
-
-The stacked density plot in Fig-X shows the distributions of the 5 DL systems’ scores disaggregated by Xpert outcomes and by prior TB history.
-The dark and light red bars were Bac negative and the dark and light green bars were Bac positive.
-The distributions of the 5 DL systems differ, indicating the underlying models are different.
-An ideal test should have a density plot with all the red bars left skewed (positive skew) and all green bars right skewed with no overlap.
-Lunit’s, qXR’s and InferReadDR’s density plot demonstrated this dichotomization pattern.
-Although almost all Bac positive patients received high abnormality scores (95-100) from JF CXR-1, so were many Bac negative patients, of which, mostly were healthy people but with a prior TB history (dark red), which can lead to excessive recall.
-When separately examine the distribution of the abnormality scores from the health people but with prior TB history, none of the DL systems has a left skewed distribution (InferReadDR: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 33]),3)`,  qXR: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 28]),3)`, Lunit INSIGHT CXR: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 29]),3)`, CAD4TB: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 27]),3)`, and JF CXR-1: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 30]),3)`), which we postulated resulted from issues in the algorithms' ability to differentiate between old scarrings and active lesions.
 
@@
 ###  ROC & PRC
+
+![](Results/5 Curves.tif){width=900px}
+
 ```{r Overall performance}
@@
 
-![](Results/5 Curves.tif){width=900px}
+The tradeoffs between sensitivity and specificity of the 5 DL systems can be visualized in the ROC  (Figure xxx) and Precision-Recall (Figure xxx) graphs.
+The AUCs under the ROC curve from high to low are Lunit INSIGHT CXR: 0.89 (95% CI:0.88-0.89), qXR: 0.87 (95% CI:0.87-0.88), InferReadDR: 0.85 (95% CI:0.84-0.86), JF CXR-1: 0.85 (95% CI:0.84-0.85), CAD4TB: 0.82 (95% CI:0.82-0.83).
+The differneces in AUCs of Lunit INSIGHT, qXR and CAD4TB are statistically significant, but the difference between JF CXR-1 and InferReadDR is not statistically significant.
+The ROC curves and precision recall curves of InferReadDR and JF CXR-1 are almost completely overlap.
 
-The tradeoffs between sensitivity and specificity of the 5 DL systems can be visualized in the ROC graphs in Figure X.
-The area under the ROC curve (AUCs) from high to low are AUC.
-The differneces in AUCs of Lunit INSIGHT, qXR and CAD4TB are statistically significant, but there is no statistic significance in the difference between JF CXR-1 and InferReadDR.
-The ROC curves and precision recall curves of InferReadDR and JF CXR-1 almost completely overlap.
-However, for most of the decision thresholds (approximately above 0.15), JF CXR-1 has higher sensitivity, but less following Xpert saving ability and higher required NNT than InferReadDR.
-For instance, at 0.8 cutoff theshold, JF CXR-1 has the highest sensitivity, `r Supp_Tab[12,3]`, but the lowest proprotion of Xpert saved, `r Supp_Tab[12,5]`,  and the highest NNT `r Supp_Tab[12,4]`.
-However, InferReadDR has the lowest sensitivity, `r Supp_Tab[9,3]`, but has significantly saving (`r Supp_Tab[9,5]`) of triaged testing; the NNT is reduced to `r Supp_Tab[9,4]`.
+Regarding the trade off between sensitivity and ability to triage, figure x shows that all 5 DL systems can at least half follow-on testing while still keep a high sensitivity above 90%.
+However, as more follow-on tests are triaged (especially >60%), the 5 DL systems demonstrated difference in sensitivity.
+For instance, when the follow-on testing is reduced by 2/3 (blue dotted line), the sensitivity is between 85%-77% with Lunit INSIGHT CXR and qXR have the highest sensitivity, followed by JF CXR-1 and InferReadDR and CAD4TB.
 
-Figure x shows that all 5 DL systems can reduce at least 50% of the follow-on testing and still keeping high sensitivity above 90%.
-However, as more follow-on tests are triaged (especially >60%), the 5 DL systems demonstrated difference in sensitivity.
-For instance, when the follow-on testing is reduced by 2/3, the sensitivity is between 85%-77% with Lunit INSIGHT CXR and qXR have the highest sensitivity, followed by JF CXR-1 and InferReadDR and CAD4TB.
+Atlhough there is no difference between InferReadDR and JF CXR-1 in terms of ROC and PR curves, Figure xxx -xxx, show the two tests have distinct performance: for most of the decision thresholds (approximately above 0.15), JF CXR-1 has a higher sensitivity, but less ability to save follow-on testing ability and required higher NNT than InferReadDR.
+For instance, at 0.8 cutoff theshold, JF CXR-1 is `r Supp_Tab[12,3]` sensitive, can save `r (Supp_Tab[12,5])` of follow-on Xpert testing, and has a NNT of `r Supp_Tab[12,4]`.
+At the same decision threshold however, InferReadDR has a much lower sensitivity, `r Supp_Tab[9,3]`, but can significantly triage (`r (Supp_Tab[9,5])`) follow-on testing and the required NNT is reduced to `r Supp_Tab[9,4]`.
 
-At the cutoff point 0.7, using CAD4TB, Lunit INSIGHT CXR and qXR can save similar proportion of following xpert testing (60%), however, the sensitivity of CAD4TB is less than qXR & Lunit.
+It is useful thresholding technique to examine the performance -- sensitivity, saving of following-on testing, NNT -- with across varying cutoff points to better dichotomize probability scores to a TB/not TB binary category.
+We observed that as cutoff threshold increases from 0, the sensitivity of CAD4TB only slowly decreases to 95%, the proportion of Xpert saved increased to 30% and NNT slowly descreases to 5.5 as threshold point reaches 0.5; however a further increases in threshold point from 0.5 results in a sharp descrease in sensitivity and NNT and increases in Xpert saved.
+We also observe that the sensitivity and NNT of JF CXR-1 remain above 90% and 3 respectively for the most of threshold scores (between 0-0.9).
+The sensitivity and NNT of Lunit and qXR remain above around 80% before quickly decreases.
 
-### Thresholding 
-The sensitivity of CAD4TB decreased slowly between 100% and around 95% at around 0.5 cutoff threshold, then the sensitivity descresed sharply as the cutoff score increases.
-JF CXR-1's sensitivity remains above 90% for most of the decision points which then decrease greatly as the cutoff score greater than 0.93.
-Both Lunit INSIGHT CXR and qXR have similar pattern, sensitivity is maintained above 80% for most of the cutoff thresholds and as decision scores increases from 0.8, the sensitivities sharply decreased.
+From Figure x, it is clear that there is no decision threshold that is universally applicable to all DL products.
+For example, the threshold to achevie at least 90% sensitivity for InferReadDR must be below 0.35, Lunit 0.59, CAD4TB and qXR 0.62, and JF CXR-1 anywhere below 0.93.
 
-It is also clear that there is no universal cutoff point that can be applied to all products.
-for example, to achevie at least 90% sensitivity, the required cutoff scores for InferReadDR must be below 0.35, Lunit 0.59, CAD4TB & qXR 0.62, JF CXR-1 can be any poitn below 0.93.
+![](Results/ROC_AUC plot.tif){width=900px}
 
-<!-- Furthermore, to better map a probablity score to a TB/not TB binary category by thresholding,  -->
-### Subgroup Analysis
-
-![](Results/AUC plot.tif){width=900px}
-
-We compared that the performance of the 5 DL systems across age groups, sources of patient and prior TB history.
-We find that all 5 DL systems perform worse in old age (above 65 year old) than in yong age (15-25 year old) and middle age (25-65 year old).
+We compared the performance of the 5 DL systems across age groups, sources of patient and prior TB history.
+We find that all 5 DL systems perform worse in old age (above 65 years old) than in yong age (15-25 years old) and middle age (25-65 years old).
 The difference in the DL systems' performance in people with and without prior TB history is profound.
@@
 
+### Density plot 
+![](Results/density.tif){width=900px}
+
+The stacked density plot in Fig-X shows the distributions of the 5 DL systems’ scores disaggregated by Xpert outcomes and by prior TB history.
+The dark and light red bars were Bac negative and the dark and light green bars were Bac positive.
+The distributions of the 5 DL systems differ, indicating the underlying models are different.
+An ideal test should have a density plot with all the red bars left skewed (positive skew) and all green bars right skewed with no overlap.
+Lunit’s, qXR’s and InferReadDR’s density plot demonstrated this dichotomization pattern.
+Although almost all Bac positive patients received high abnormality scores (95-100) from JF CXR-1, so were many Bac negative patients, of which, mostly were healthy people but with a prior TB history (dark red), which can lead to excessive recall.
+When separately examine the distribution of the abnormality scores from the health people but with prior TB history, none of the DL systems has a left skewed distribution (InferReadDR: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 33]),3)`,  qXR: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 28]),3)`, Lunit INSIGHT CXR: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 29]),3)`, CAD4TB: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 27]),3)`, and JF CXR-1: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 30]),3)`), which we postulated resulted from issues in the algorithms' ability to differentiate between old scarrings and active lesions.
+
 # Discussion
 
-The study show that the 5 DL prdocuts had clinical potential.
-The classificaitions made by the DL system coul be used to when skilled radiologists are scare in high TB burden countries which improve the standard of care.
-The AI system could also be used to provide automated, immediate feedback in the screening setting.
+To our knowledge, this is the largest independent study of multiple AI algorithms for detecting TB abnormalities in CXR and the first published evaluation of JF CXR-1 and InferReadDR for detecting TB.
+
+This is the first evaluation of multiple DL systems for detecting TB abnormalities in CXR.
+We observed that all three systems performed significantly better than human radiologists and had higher AUCs than most of the current published literature on previous versions of CAD4TB 6.
+Our results also document the first published evaluation of qXR and Lunit for detecting TB.
+There was no statistical difference among the AUCs of CAD4TB, Lunit, and qXR across the study sites, in pooled analysis, and when only smear negative individuals were considered.
+The point estimate for CAD4TB met the TPP target for a community-based triage test.
+However, there was no statistical difference between the specificity of CAD4TB and Lunit at the sensitivity level of 95% and a marginal difference with qXR.
+At the 94% or 96% sensitivity point estimate, none of the three DL systems were significantly different.
+These results did not hold at the site level where there was no statistically significant difference.
+The overall performance of the three DL systems was similar in multiple analyses and stratifications.
+Implementers considering using DL systems for CXR reading should take into account other factors including service, ease of use, maintenance and price - all important considerations in any new technology implementation 25.
+
+While the current WHO guidance for these computer-aided detection software for TB emphasizes the need of predefined threshold scores 8, our results clearly indicate the need for implementers  to conduct their own pilot on the specific population being tested.
+A previous study found differences in performance by age and by referral site 13.
+With large datasets, it may be possible to tailor specific thresholds depending on the characteristics of individuals screened.
+In some published literature, specific threshold scores for different versions of CAD4TB have been used 30 and following these scores or manufactures default settings may produce different results across settings.
+
+There are a number of limitations in our study.
+Due to logistic and budgetary constraints, we did not use culture as the reference standard.
+We were not able to obtain the HIV status of some of the participants in both sites, limiting our ability to analyze the products in this population.
+Lastly, since we retrospectively collected and analyzed the radiographs in the sites where CAD4TB was implemented, the radiographs have been seen by CAD4TB.
+However, neither qXR nor Lunit had seen the images prior to this study.

### 2020-04-04 SubGroup.Rmd
update

@@
 Old <- MDF[MDF$TB.Medication.History %in% "Yes",]
+
+Female <- MDF[MDF$Gender %in% "F", ]
+Male <- MDF[MDF$Gender %in% "M", ]
 
@@
 WalkIn_long  <- subset(MDF_long, MDF_long$UseCase %in% "WalkIn")
+# 
+# 
+# New_Yong <- MDF[MDF$TB.Medication.History %in% "No" & MDF$AgeGroup %in% "[15,25)",]
+# Old_Yong <- MDF[MDF$TB.Medication.History %in% "Yes"& MDF$AgeGroup %in% "[15,25)",]
+# 
+# New_Middle <- MDF[MDF$TB.Medication.History %in% "No" & MDF$AgeGroup %in% "[25,60)",]
+# Old_Middle <- MDF[MDF$TB.Medication.History %in% "Yes"& MDF$AgeGroup %in% "[25,60)",]
+# 
+# New_Senior <- MDF[MDF$TB.Medication.History %in% "No" & MDF$AgeGroup %in% "[60,108]",]
+# Old_Senior <- MDF[MDF$TB.Medication.History %in% "Yes"& MDF$AgeGroup %in% "[60,108]",]
+
 # Missing_long  <- subset(MDF, is.na(MDF$UseCase)==T)
@@
 
-CAD_Xpert_plot_Middle <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Middle.csv")
-CAD_Xpert_plot_Young <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Young.csv")
-CAD_Xpert_plot_Senior <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Senior.csv")
-CAD_Xpert_plot_DOTS <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_DOTS.csv")
-CAD_Xpert_plot_WalkIn <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_WalkIn.csv")
-CAD_Xpert_plot_Referral <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Referral.csv")
-CAD_Xpert_plot_New <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_New.csv")
-CAD_Xpert_plot_Old <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Old.csv")
-
-SubgroupTable <- rbind(CAD_Xpert_plot_New, CAD_Xpert_plot_Old, CAD_Xpert_plot_Young, CAD_Xpert_plot_Middle, CAD_Xpert_plot_Senior, CAD_Xpert_plot_Referral, CAD_Xpert_plot_DOTS, CAD_Xpert_plot_WalkIn)
+# CAD_Xpert_plot_Middle <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Middle.csv")
+# CAD_Xpert_plot_Young <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Young.csv")
+# CAD_Xpert_plot_Senior <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Senior.csv")
+# CAD_Xpert_plot_DOTS <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_DOTS.csv")
+# CAD_Xpert_plot_WalkIn <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_WalkIn.csv")
+# CAD_Xpert_plot_Referral <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Referral.csv")
+# CAD_Xpert_plot_New <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_New.csv")
+# CAD_Xpert_plot_Old <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Old.csv")
+# 
+# 
+# SubgroupTable <- rbind(CAD_Xpert_plot_New, CAD_Xpert_plot_Old, CAD_Xpert_plot_Young, CAD_Xpert_plot_Middle, CAD_Xpert_plot_Senior, CAD_Xpert_plot_Referral, CAD_Xpert_plot_DOTS, CAD_Xpert_plot_WalkIn)
 # write.csv(SubgroupTable, "Chapter/Subgroup Table/SubgroupTable.csv", row.names = F)
@@
 
-```{r AUC}
+```{r 2 AUC}
 ## All
@@
 
-ROCPRC <- function(dataset, dataset_long){
+ROCPRC <- function(dataset){
   attr <- attributes(evalmod(scores = dataset$CAD4TB6, labels = dataset$Xpert2Outcome_num))
@@
   attr <- attributes(evalmod(scores = dataset$LunitScore, labels = dataset$Xpert2Outcome_num))
-  aucT3 <- c("Lunit INSIGHT CXR  ", round(attr$auc[4],3))
+  aucT3 <- c("Lunit INSIGHT CXR", round(attr$auc[4],3))
 
   attr <- attributes(evalmod(scores = dataset$JF1, labels = dataset$Xpert2Outcome_num))
-  aucT4 <- c("JF CXR-1 ", round(attr$auc[4],3))
+  aucT4 <- c("JF CXR-1", round(attr$auc[4],3))
 
@@
 
-l <- ROCPRC(MDF, MDF_long)
+l <- ROCPRC(MDF)
 all <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
@@
 ## New only
-l <- ROCPRC(New, New_long)
+l <- ROCPRC(New)
 New <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
@@
 ## Old only
-l <- ROCPRC(Old, Old_long)
+l <- ROCPRC(Old)
 Old <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
@@
 ## Young
-l <- ROCPRC(Young, Young_long)
+l <- ROCPRC(Young)
 Young <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
@@
 ## Middle
-l <- ROCPRC(Middle, Middle_long)
+l <- ROCPRC(Middle)
 Middle <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
@@
 ## Senior
-l <- ROCPRC(Senior, Senior_long)
+l <- ROCPRC(Senior)
 Senior <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
@@
 ## Referral only
-l <- ROCPRC(Referral, Referral_long)
+l <- ROCPRC(Referral)
 Referral <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
@@
 ## DOTS only
-l <- ROCPRC(DOTS, DOTS_long)
+l <- ROCPRC(DOTS)
 DOTS <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
@@
 ## Walk-in only
-l <- ROCPRC(WalkIn, WalkIn_long)
+l <- ROCPRC(WalkIn)
 WalkIn <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
@@
 
-# ## Missing 
-# l <- ROCPRC(Missing, Missing_long)
-# Missing <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-# Missing$subgroup <- "Missing"
+## Female
+l <- ROCPRC(Female)
+Female <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+Female$subgroup <- "Female"
 
-aucTable <- rbind(all, New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn)
+## Male
+l <- ROCPRC(Male)
+Male <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+Male$subgroup <- "Male"
+#### stratification by age AND prior TB history
+
+# l <- ROCPRC(New_Yong)
+# New_Yong <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+# New_Yong$subgroup <- "New_Yong"
+# 
+# 
+# l <- ROCPRC(New_Middle)
+# New_Middle <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+# New_Middle$subgroup <- "New_Middle"
+# 
+# 
+# l <- ROCPRC(New_Senior)
+# New_Senior <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+# New_Senior$subgroup <- "New_Senior"
+# 
+# 
+# 
+# l <- ROCPRC(Old_Yong)
+# Old_Yong <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+# Old_Yong$subgroup <- "Old_Yong"
+# 
+# 
+# l <- ROCPRC(Old_Middle)
+# Old_Middle <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+# Old_Middle$subgroup <- "Old_Middle"
+# 
+# 
+# 
+# l <- ROCPRC(Old_Senior)
+# Old_Senior <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+# Old_Senior$subgroup <- "Old_Senior"
+# 
+# 
+# temp <- rbind(New_Yong, New_Middle, New_Senior, Old_Yong, Old_Middle, Old_Senior)
+# colnames(temp) <- c("DL.System", "AUC", "PCAUC", "Subgroup")
+# temp$AUC <- as.numeric.factor(temp$AUC)
+# temp$PCAUC <- as.numeric.factor(temp$PCAUC)
+
+# View(temp)
+
+# ggplot(temp, aes(x=DL.System, y=AUC, fill=Subgroup))+  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+
+aucTable <- rbind(all, New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn, Female, Male)
 colnames(aucTable) <- c("DL System", "AUC", "PCAUC", "Subgroup")
@@
 # rm(list=(ls()))
+```
+
+```{r ROC AUC with CI}
+
+library(pROC)
+ROC <- function(dataset){
+  roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, dataset)
+  roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv2_100, dataset)
+  roc_Lunit <- ci.auc(Xpert2Outcome_num ~ LunitScore_100, dataset)
+  roc_JF1 <- ci.auc(Xpert2Outcome_num ~ JF1_100, dataset)
+  roc_IF2 <- ci.auc(Xpert2Outcome_num ~ IF2_100, dataset)
+
+  aucT <- as.data.frame(matrix(c(roc_CAD6[2], roc_CAD6[1], roc_CAD6[3], roc_qure[2], roc_qure[1], roc_qure[3], roc_Lunit[2], roc_Lunit[1], roc_Lunit[3], roc_JF1[2], roc_JF1[1], roc_JF1[3], roc_IF2[2], roc_IF2[1], roc_IF2[3]),  byrow=TRUE, ncol =  3))
+  names(aucT) <- c("AUC", "AUCL", "AUCH")
+  aucT$DL.System <- c("CAD4TB", "qXR", "Lunit INSIGHT CXR", "JF CXR-1", "InferReadDR")
+
+  return(aucT)
+}
+
+## New only
+New <- ROC(New)
+New$subgroup <- "New cases"
+
+## Old only
+Old <- ROC(Old)
+Old$subgroup <- "Previously treated cases"
+
+## Young
+Young <- ROC(Young)
+Young$subgroup <- "Young age"
+
+## Middle
+Middle <- ROC(Middle)
+Middle$subgroup <- "Middle age"
+
+## Senior
+Senior <- ROC(Senior)
+Senior$subgroup <- "Old age"
+
+## Referral only
+Referral <- ROC(Referral)
+Referral$subgroup <- "Referred"
+
+## DOTS only
+DOTS <- ROC(DOTS)
+DOTS$subgroup <- "DOTS retested"
+
+## Walk-in only
+WalkIn <- ROC(WalkIn)
+WalkIn$subgroup <- "WalkIn"
+
+ROCaucTable <- rbind(New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn)
+View(ROCaucTable)
+write.csv(ROCaucTable, "Results/ROCaucTable.csv", row.names = F)
 
@@
 
+gender <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+
 ### PRC
@@
 
-tiff("Results/AUC plot.tif", width = 18, height = 8, units = "in", res = 100)
+genderPC <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+
+tiff("Results/PRC ROC AUC plot.tif", width = 18, height = 8, units = "in", res = 100)
 require(gridExtra)
-grid.arrange(age, referral, history, agePC, referralPC, historyPC, ncol=3)
+
+grid.arrange(age, referral, history, gender, agePC, referralPC, historyPC, genderPC, ncol=4)
+# grid.arrange(age, referral, history, ncol=3)
 
 dev.off()
-rm(age, referral, history, agePC, referralPC, historyPC)
+# rm(age, referral, history, agePC, referralPC, historyPC, gender, genderPC)
+
+tiff("Results/PRC AUC plot.tif", width = 9, height = 8, units = "in", res = 100)
+grid.arrange(agePC, referralPC, historyPC, genderPC, ncol=2)
+dev.off()
+
 ```
+
+```{r}
+ROCaucTable <- read.csv("Results/ROCaucTable.csv")
+ROCaucTable$subgroup <- factor(ROCaucTable$subgroup, levels = c("Young age", "Middle age", "Old age", "Referred", "DOTS retested", "WalkIn", "New cases", "Previously treated cases"))
+### AUC
+age <-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=DL.System, y=AUC, fill=subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge()) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.7)) + theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+age
+
+referral<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=DL.System, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))
+referral
+
+history<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=DL.System, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))
+
+tiff("Results/ROC_AUC plot.tif", width = 13, height = 3, units = "in", res = 100)
+require(gridExtra)
+
+grid.arrange(age, referral, history, ncol=3)
+
+dev.off()
+rm(age, referral, history)
+```

### 2020-04-04 Chapter/5 Curves.R

@@ -5,63 +5,64 @@ CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE.csv")
 
 CAD_Xpert_plot <- subset(CAD_Xpert_plot, CAD_Xpert_plot$Site %in% "BGD")
 
-### Sensitivity vs Score --------------------
-base <- ggplot(CAD_Xpert_plot, aes(Score, Sens)) + geom_path(aes(color = DeepLearningSystem)) 
+### d. Sensitivity vs Score --------------------
+base <- ggplot(CAD_Xpert_plot, aes(Score, Sens)) + geom_path(aes(color = DeepLearningSystem)) + scale_fill_manual(values=c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00")) +  scale_color_manual(values=c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00")) 
 # + geom_ribbon(aes(x = Score, ymin = Sens_L, ymax = Sens_H, color = DeepLearningSystem, fill = DeepLearningSystem), alpha= 0.2) 
 
-sensCurve <- base + theme_light() + coord_equal() + labs(x = "Abnormality Score", y= "Sensitivity", subtitle = paste0("The Sensitivity vs abnormality score (n=", length(MDF$PID_OMRS), ")")) +theme(legend.position = c(0.05,0.05),legend.justification = c("left", "bottom")) + theme(panel.grid.minor = element_line(colour="grey", size=0.5)) + scale_x_continuous(minor_breaks = seq(0 , 1, 0.1), breaks = seq(0, 1, 0.1))+ scale_y_continuous(minor_breaks = seq(0 , 1, 0.1), breaks = seq(0, 1, 0.1)) + geom_vline(xintercept = c(0.8, 0.7), linetype="dotted", color = "blue", size=1) +theme(legend.position = "none")
-# sensCurveZoomIn <- sensCurve + coord_cartesian(xlim = c(0.5, 0.9), ylim = c(0.90, 1) ) +
-# ggtitle("Figure 2b: Zoomed-in view of the square marked part of Fig. 2a")+theme_light()
[…]

### 2020-04-04 Chapter/roc.R

@@ -43,16 +43,16 @@ ggROC <- ggROC + geom_point(data = Radiologist, mapping = aes(X, Sens, shape = A
 # dev.off()
 
 
-AUC <- paste("Lunit INSIGHT CXR: ", round(roc_Lunit[2],2), " (95% CI:", round(roc_Lunit[1],2), "-", round(roc_Lunit[3],2), ")", ", ", 
+AUC <- paste("Lunit INSIGHT CXR: ", round(roc_Lunit[2],4), " (95% CI:", round(roc_Lunit[1],4), "-", round(roc_Lunit[3],4), ")", ", ", 
              
-             "qXR: ", round(roc_qure[2],2), " (95% CI:", round(roc_qure[1],2), "-", round(roc_qure[3],2), ")", ", ",
+             "qXR: ", round(roc_qure[2],4), " (95% CI:", round(roc_qure[1],4), "-", round(roc_qure[3],4), ")", ", ",
              
-             "InferReadDR: ", round(roc_IF2[2],2), " (95% CI:", round(roc_IF2[1],2), "-", round(roc_IF2[3],2), ")", ", ", 
+             "InferReadDR: ", round(roc_IF2[2],4), " (95% CI:", round(roc_IF2[1],4), "-", round(roc_IF2[3],4), ")", ", ", 
              
-             "JF CXR-1: ", round(roc_JF1[2],2), " (95% CI:", round(roc_JF1[1],2), "-", round(roc_JF1[3],2), ")", ", ",  
+             "JF CXR-1: ", round(roc_JF1[2],4), " (95% CI:", round(roc_JF1[1],4), "-", round(roc_JF1[3],4), ")", ", ",  
              
-             "CAD4TB: ", round(roc_CAD6[2],2), " (95% CI:", round(roc_CAD6[1],2), "-", round(roc_CAD6[3],2), ")",sep = "")
+             "CAD4TB: ", round(roc_CAD6[2],4), " (95% CI:", round(roc_CAD6[1],4), "-", round(roc_CAD6[3],4), ")",sep = "")
 
 
 
-rm(roc_CAD6, roc_JF1, roc_JF2, roc_qure, roc_Lunit, roc_IF1, roc_IF2, roc_IF3, dat)
+# rm(roc_CAD6, roc_JF1, roc_JF2, roc_qure, roc_Lunit, roc_IF1, roc_IF2, roc_IF3, dat)

### 2020-04-04 Chapter/table1.R

@@ -1,13 +1,21 @@
 source("DataWrangling/GlobalOption.R")
 
+MDF$qXRv2 <- MDF$qXRv2*100
+MDF$LunitScore <- MDF$LunitScore*100
+
+MDF$IF2 <- MDF$IF2*100
+
+MDF$JF1 <- MDF$JF1*100
+
+
 # MDF <- subset(MDF, MDF$Age > 15)
 library(tableone)
 
 # Define numeric variables
-listVar <- c("Age", "Gender", "Cough", "Fever", "Active.Breathing.Shortness", "Weight.Loss","Haemoptysis", "Symptoms", "TB.Medication.History", "Xpert2Outcome_num", "MTB.Burden", "RIF.Result", "UseCase", "rad.highly.TB", "rad.TB", "rad.abn", "CAD4TB6", "qXRv2", "LunitScore", "JF1", "IF1", "IF2")
+listVar <- c("Age", "AgeGroup", "Gender", "Cough", "Fever", "Active.Breathing.Shortness", "Weight.Loss","Haemoptysis", "Symptoms", "TB.Medication.History", "Xpert2Outcome_num", "MTB.Burden", "RIF.Result", "UseCase", "rad.highly.TB", "rad.TB", "rad.abn", "CAD4TB6", "qXRv2", "LunitScore", "JF1", "IF1", "IF2")
 
 #Define categorical variables
-catVars <- c( "Gender", "Cough", "Fever", "Active.Breathing.Shortness", "Weight.Loss","Haemoptysis", "Symptoms", "TB.Medication.History", "Xpert2Outcome_num", "MTB.Burden", "RIF.Result", "UseCase", "rad.highly.TB", "rad.TB", "rad.abn")
+catVars <- c( "AgeGroup", "Gender", "Cough", "Fever", "Active.Breathing.Shortness", "Weight.Loss","Haemoptysis", "Symptoms", "TB.Medication.History", "Xpert2Outcome_num", "MTB.Burden", "RIF.Result", "UseCase", "rad.highly.TB", "rad.TB", "rad.abn")
 
 
 table1 <- CreateTableOne(vars = listVar, strata=c("Xpert2Outcome_num"), data = MDF, factorVars = catVars)

### 2020-04-22 SubGroup.Rmd
update

@@
 WalkIn_long  <- subset(MDF_long, MDF_long$UseCase %in% "WalkIn")
-# 
-# 
-# New_Yong <- MDF[MDF$TB.Medication.History %in% "No" & MDF$AgeGroup %in% "[15,25)",]
-# Old_Yong <- MDF[MDF$TB.Medication.History %in% "Yes"& MDF$AgeGroup %in% "[15,25)",]
-# 
-# New_Middle <- MDF[MDF$TB.Medication.History %in% "No" & MDF$AgeGroup %in% "[25,60)",]
-# Old_Middle <- MDF[MDF$TB.Medication.History %in% "Yes"& MDF$AgeGroup %in% "[25,60)",]
-# 
-# New_Senior <- MDF[MDF$TB.Medication.History %in% "No" & MDF$AgeGroup %in% "[60,108]",]
-# Old_Senior <- MDF[MDF$TB.Medication.History %in% "Yes"& MDF$AgeGroup %in% "[60,108]",]
 
-# Missing_long  <- subset(MDF, is.na(MDF$UseCase)==T)
-
-# source("Chapter/Subgroup Table/Young.R")
-# source("Chapter/Subgroup Table/Middle.R")
-# source("Chapter/Subgroup Table/Senior.R")
-# source("Chapter/Subgroup Table/Referral.R")
-# source("Chapter/Subgroup Table/DOTS.R")
-# write.csv(CAD_Xpert_plot_Middle, "Chapter/Subgroup Table/CAD_Xpert_plot_Middle.csv")
-# write.csv(CAD_Xpert_plot_Young, "Chapter/Subgroup Table/CAD_Xpert_plot_Young.csv")
-# write.csv(CAD_Xpert_plot_Senior, "Chapter/Subgroup Table/CAD_Xpert_plot_Senior.csv")
-# write.csv(CAD_Xpert_plot_Referral, "Chapter/Subgroup Table/CAD_Xpert_plot_Referral.csv")
-# write.csv(CAD_Xpert_plot_DOTS, "Chapter/Subgroup Table/CAD_Xpert_plot_DOTS.csv")
-# write.csv(CAD_Xpert_plot_WalkIn, "Chapter/Subgroup Table/CAD_Xpert_plot_WalkIn.csv")
-# write.csv(CAD_Xpert_plot_New, "Chapter/Subgroup Table/CAD_Xpert_plot_New.csv")
-# write.csv(CAD_Xpert_plot_Old, "Chapter/Subgroup Table/CAD_Xpert_plot_Old.csv")
-
-# CAD_Xpert_plot_Middle <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Middle.csv")
-# CAD_Xpert_plot_Young <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Young.csv")
-# CAD_Xpert_plot_Senior <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Senior.csv")
-# CAD_Xpert_plot_DOTS <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_DOTS.csv")
-# CAD_Xpert_plot_WalkIn <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_WalkIn.csv")
-# CAD_Xpert_plot_Referral <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Referral.csv")
-# CAD_Xpert_plot_New <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_New.csv")
-# CAD_Xpert_plot_Old <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Old.csv")
-# 
-# 
-# SubgroupTable <- rbind(CAD_Xpert_plot_New, CAD_Xpert_plot_Old, CAD_Xpert_plot_Young, CAD_Xpert_plot_Middle, CAD_Xpert_plot_Senior, CAD_Xpert_plot_Referral, CAD_Xpert_plot_DOTS, CAD_Xpert_plot_WalkIn)
-# write.csv(SubgroupTable, "Chapter/Subgroup Table/SubgroupTable.csv", row.names = F)
-# rm(list=(ls()))
 ```
@@
 
-# l <- ROCPRC(New_Yong)
-# New_Yong <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-# New_Yong$subgroup <- "New_Yong"
-# 
-# 
-# l <- ROCPRC(New_Middle)
-# New_Middle <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-# New_Middle$subgroup <- "New_Middle"
-# 
-# 
-# l <- ROCPRC(New_Senior)
-# New_Senior <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-# New_Senior$subgroup <- "New_Senior"
-# 
-# 
-# 
-# l <- ROCPRC(Old_Yong)
-# Old_Yong <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-# Old_Yong$subgroup <- "Old_Yong"
-# 
-# 
-# l <- ROCPRC(Old_Middle)
-# Old_Middle <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-# Old_Middle$subgroup <- "Old_Middle"
-# 
-# 
-# 
-# l <- ROCPRC(Old_Senior)
-# Old_Senior <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-# Old_Senior$subgroup <- "Old_Senior"
-# 
-# 
-# temp <- rbind(New_Yong, New_Middle, New_Senior, Old_Yong, Old_Middle, Old_Senior)
-# colnames(temp) <- c("DL.System", "AUC", "PCAUC", "Subgroup")
-# temp$AUC <- as.numeric.factor(temp$AUC)
-# temp$PCAUC <- as.numeric.factor(temp$PCAUC)
-
-# View(temp)
-
-# ggplot(temp, aes(x=DL.System, y=AUC, fill=Subgroup))+  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
-
 aucTable <- rbind(all, New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn, Female, Male)
 colnames(aucTable) <- c("DL System", "AUC", "PCAUC", "Subgroup")
-write.csv(aucTable, "Results/aucTable.csv")
+# write.csv(aucTable, "Results/aucTable.csv")
 # rm(list=(ls()))
@@
 
+aucTable$Subgroup <- factor(aucTable$Subgroup, levels = c("Young age", "Middle age", "Old age", "Referred", "DOTS retested", "WalkIn", "New cases", "Previously treated cases", "Female", "Male"))
 ### AUC

### 2020-04-22 BGD_cleaning.py

@@ -5,13 +5,14 @@ import matplotlib.pylab as plt
 from pandas import Series, DataFrame
 
 ## Importing MDF.csv ---------------------------------------------------------------------------------------
-address = 'C:/Users/zhizh/OneDrive - Stop TB Partnership/UNOPS/10 Paper Writing/CAR software/02 Bangladesh/CAR-Bangladesh/CAR_BGD/MDF.csv'
+address = 'C:/Users/zhizh/OneDrive - Stop TB Partnership/UNOPS/10 Paper Writing/CAR software/02 Bangladesh/MachineBGD/DataWrangling/MDF.csv'
 
 # Making a list of missing value types
-missing_values = ["n/a", "na", "--", "N/A", "-"]
+missing_values = ["n/a", "na", "--", "N/A", "-", ""]
 BGD = pd.read_csv(address, na_values= missing_values)
-BGD = BGD.drop(['Given', 'FamilyName', 'Patient.BD', 'Filename', 'Radiology.Result.Date'], axis=1)
+BGD = BGD.drop(['Radiology.Result.Date'], axis=1)
 print(BGD.info())
+del(address)
 
 ## checking missing symptom values ---------------------------------------------------------------------------------------
 print (BGD['Cough'].isnull())

### 2020-04-22 CutoffTable.R

@@ -1,418 +1,424 @@
-# Nepal_Cameroon <- read.csv(file = "C:/Users/zhizh/OneDrive - Stop TB Partnership/UNOPS/10 Paper Writing/CAR software/03 Nepal_Cameroon/CAR -- 03 Nepal_Cameroon/Clean/Nepal_Cameroon.csv", header = T)
-# Nepal_Cameroon <- Nepal_Cameroon[, -1]
-# NPL <- Nepal_Cameroon[Nepal_Cameroon$Country %in% "NPL", ]
-# CAM <- Nepal_Cameroon[Nepal_Cameroon$Country %in% "CAM", ]
-# 
+Nepal_Cameroon <- read.csv(file = "C:/Users/zhizh/OneDrive - Stop TB Partnership/UNOPS/10 Paper Writing/CAR software/03 Nepal_Cameroon/CAR -- 03 Nepal_Cameroon/Clean/Nepal_Cameroon.csv", header = T)
+Nepal_Cameroon <- Nepal_Cameroon[, -1]
+NPL <- Nepal_Cameroon[Nepal_Cameroon$Country %in% "NPL", ]
+CAM <- Nepal_Cameroon[Nepal_Cameroon$Country %in% "CAM", ]
+
 # maxV <- 10001
 # sep <- 0.0001
 # sepdeflt <- 0.01
-# 
-# # maxV<- 101
-# # sep <- 0.01
-# # sepdeflt <- 1
-# 
-# ### Set up a function 
-# myfunction <- function(CountryX, DL.System, car.cutoff){
-#   a <- sum(DL.System >= car.cutoff & CountryX$XPERT_pos =="1")
-#   b <- sum(DL.System >= car.cutoff & CountryX$XPERT_pos =="0")
-#   c <- sum(DL.System < car.cutoff & CountryX$XPERT_pos =="1")
-#   d <- sum(DL.System < car.cutoff & CountryX$XPERT_pos =="0")
-#   dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
-#   rval <- epi.tests(dat, conf.level = 0.95)
-#   sensitivity <- as.vector(round((rval$elements$sensitivity),8))
-#   specificity <- as.vector(round((rval$elements$specificity),8))
-#   pv.positive <- as.vector(round((rval$elements$pv.positive),8))
[…]

### 2020-04-22 DataWrangling/GlobalOption.R

@@ -56,3 +56,11 @@ MDF_long$XpertHistory[MDF_long$TB.Medication.History %in% "No" & MDF_long$Xpert2
 MDF_long$XpertHistory[MDF_long$TB.Medication.History %in% "Yes" & MDF_long$Xpert2Outcome_num %in% "1"] <- "Bac Pos - with TB History"
 
 
+ML <- MDF[, c('PID_OMRS', 'Gender', 'Age', 'Cough', 'Fever', 'Active.Breathing.Shortness', 'Weight.Loss', 'Haemoptysis', 'TB.Medication.History', 'qXRv2', 'CAD4TB6', 'JF1', 'IF2','Xpert2Outcome_num')]
+
+ML_training <- ML[sample(nrow(ML), 18853), ]
+ML_testing <- subset(ML, !(ML$PID_OMRS %in% ML_training$PID_OMRS))
+
+write.csv(ML, "DataWrangling/ML.csv", row.names = F)
+write.csv(ML_training, "DataWrangling/ML_training.csv", row.names = F)
+write.csv(ML_testing, "DataWrangling/ML_testing.csv", row.names = F)

### 2020-07-28 Chapter/Tele.Rmd
CAD6.3

```{r}
library(readxl)
Teleradiology <- read_excel("C:/Users/zhizh/OneDrive - Stop TB Partnership/UNOPS/10 Paper Writing/CAR software/02 Bangladesh/MachineBGD/DataWrangling/TeleradiologyReportsUpdated.xlsx")
# names(Teleradiology)
colnames(Teleradiology)[1] <- "TID_OMRS"

Teleradiology$`Abnormality/TB`[Teleradiology$`Abnormality/TB` == "Abnormality consistent with TB" ] <- "TB_Abnormality"
Teleradiology$`Abnormality/TB`[Teleradiology$`Abnormality/TB` == "Abnormality NOT consistent with TB" ] <- "All_Abnormality"

Teleradiology[!Teleradiology$TID_OMRS %in% Tele$TID_OMRS, 1]

Tele <- merge(Teleradiology, MDF[, c(1, 3, 13, 46:52)], by="TID_OMRS")

# write.csv(Tele, "Tele.csv")
t1 <- table(Tele$Comment, Tele$`Abnormality/TB`)
# ftable(addmargins(t1))
# t1[4, ]  <- t1[4, ] +t1[6, ]
# t1[2, ]  <- t1[2, ] +t1[4, ]
# 
# t1[7, ]  <- t1[7, ] +t1[8, ]
# t1[5, ]  <- t1[5, ] +t1[7, ]
# t1[3, ]  <- t1[3, ] +t1[5, ]

t1 <- t1[c(2,4,6,8,10, 3,5,7,9,11, 12), ]
addmargins(t1)
# teleTable <- as.data.frame()
teleTable <- matrix(addmargins(t1), nrow = 12, ncol=4, byrow = FALSE)

row.names(teleTable) <- c("Missed by 1 AI AND by human" ,  "Missed by 2 AI AND human ", "Missed by 3 AI AND human ", "Missed by 4 AI AND human ",  "Missed by 5 AI AND human ", "Missed by 1 AI but NOT human",  "Missed by 2 AI but NOT human ", "Missed by 3 AI but NOT human ", "Missed by 4 AI but NOT human ", "Missed by 5 AI but NOT human", "Missed by human ONLY ", "Total")
colnames(teleTable) <- c("All_Abnormality", "Normal", "TB_Abnormality", "Total")

teleTable <- as.data.frame(teleTable)

MarginTable <- percent(matrix(prop.table(t1, margin = 1), nrow = 11, ncol=3, byrow = FALSE))
MarginTable <- matrix(MarginTable, nrow = 11, ncol=3, byrow = FALSE)
row.names(MarginTable) <- c("Missed by 1 AI AND by human" ,  "Missed by 2 AI AND human ", "Missed by 3 AI AND human ", "Missed by 4 AI AND human ",  "Missed by 5 AI AND human ", "Missed by 1 AI but NOT human",  "Missed by 2 AI but NOT human ", "Missed by 3 AI but NOT human ", "Missed by 4 AI but NOT human ", "Missed by 5 AI but NOT human", "Missed by human ONLY ")

colnames(MarginTable) <- c("All_Abnormality", "Normal", "TB_Abnormality")
MarginTable <- as.data.frame(MarginTable)

MarginTable[nrow(MarginTable)+1, ] = c("", "", "")
row.names(MarginTable)[12] <- "Total"

TeleTable <- cbind(teleTable, MarginTable)
rm(teleTable, MarginTable)

TeleTable <- TeleTable[, c(3,7,1,5,2,6,4)]
TeleTable
# write.csv(TeleTable, "TeleTable.csv")
```

## Rradiologist Accuracy
```{r Rradiologist Accuracy}
MDF$USHuman <- Tele$`Abnormality/TB`[match(MDF$TID_OMRS, Tele$TID_OMRS)]
USOnly <- MDF[is.na(MDF$USHuman)==FALSE, ]

## BGD radiologists
  ###  High+possible ----------------------------
  TP <- sum(USOnly$rad.TB %in% "1" & USOnly$Xpert2Outcome_num==1)
  FP <- sum(USOnly$rad.TB %in% 1 & USOnly$Xpert2Outcome_num==0)
  TN <- sum(USOnly$rad.TB %in% 0 & USOnly$Xpert2Outcome_num==0)
  FN <- sum(USOnly$rad.TB %in% 0 & USOnly$Xpert2Outcome_num==1)

  dat <- as.table(matrix(c(TP, FP, FN, TN), nrow=2, byrow=TRUE))
  colnames(dat) <- c("Xpert+","Xpert-")
  rownames(dat) <- c("CXR+","CXR-")
  rval <- epi.tests(dat, conf.level = 0.95)
  Probably <- rval$elements[c(59, 55)]
  rm(TP, FP, TN, FN)

  ### Any Abnormalities ------------------------------
  TP <- sum(USOnly$rad.abn %in% "1" & USOnly$Xpert2Outcome_num==1)
  FP <- sum(USOnly$rad.abn %in% 1 & USOnly$Xpert2Outcome_num==0)
  TN <- sum(USOnly$rad.abn %in% 0 & USOnly$Xpert2Outcome_num==0)
  FN <- sum(USOnly$rad.abn %in% 0 & USOnly$Xpert2Outcome_num==1)

  dat <- as.table(matrix(c(TP, FP, FN, TN), nrow=2, byrow=TRUE))
  colnames(dat) <- c("Xpert+","Xpert-")
  rownames(dat) <- c("CXR+","CXR-")
  rval <- epi.tests(dat, conf.level = 0.95)
  Any <- rval$elements[c(59, 55)]
  rm(TP, FP, TN, FN)

  BGDReader <- data.frame(matrix(unlist(c(Probably, Any)), nrow = 2, byrow = T))
  colnames(BGDReader) <- c("Sens", "Sens_L", "Sens_H", "Spec", "Spec_L", "Spec_H")
  BGDReader$X <- 1-BGDReader$Spec
  BGDReader$BGDReaderCategory <- c("Probably TB", "Any Abnormality")

## US radiologists
###  TB Abnormality ----------------------------
  TP <- sum(USOnly$USHuman %in% "TB_Abnormality" & USOnly$Xpert2Outcome_num==1)
  FP <- sum(USOnly$USHuman %in% "TB_Abnormality" & USOnly$Xpert2Outcome_num==0)
  TN <- sum(USOnly$USHuman != "TB_Abnormality" & USOnly$Xpert2Outcome_num==0)
  FN <- sum(USOnly$USHuman != "TB_Abnormality" & USOnly$Xpert2Outcome_num==1)

  dat <- as.table(matrix(c(TP, FP, FN, TN), nrow=2, byrow=TRUE))
  colnames(dat) <- c("Xpert+","Xpert-")
  rownames(dat) <- c("CXR+","CXR-")
  rval <- epi.tests(dat, conf.level = 0.95)
  TB <- rval$elements[c(59, 55)]
  rm(TP, FP, TN, FN)

###  All Abnormality ----------------------------
  TP <- sum(USOnly$USHuman != "Normal" & USOnly$Xpert2Outcome_num==1)
  FP <- sum(USOnly$USHuman != "Normal" & USOnly$Xpert2Outcome_num==0)
  TN <- sum(USOnly$USHuman == "Normal" & USOnly$Xpert2Outcome_num==0)
  FN <- sum(USOnly$USHuman == "Normal" & USOnly$Xpert2Outcome_num==1)

  dat <- as.table(matrix(c(TP, FP, FN, TN), nrow=2, byrow=TRUE))
  colnames(dat) <- c("Xpert+","Xpert-")
  rownames(dat) <- c("CXR+","CXR-")
  rval <- epi.tests(dat, conf.level = 0.95)
  All <- rval$elements[c(59, 55)]

  USReader <- data.frame(matrix(unlist(c(TB, All)), nrow = 2, byrow = T))
  colnames(USReader) <- c("Sens", "Sens_L", "Sens_H", "Spec", "Spec_L", "Spec_H")
  USReader$X <- 1-USReader$Spec
  rm(TP, FP, TN, FN)

USReader
BGDReader
```

## ROC
```{r ROC}
library(ggplot2)
library(scales)
library(epiR)
library(ggthemes)
library(RColorBrewer)
library(plyr)
library(reshape2)
library(pROC)
library(tidyverse)
library(dplyr)
library(lubridate)
library(readxl)
library(plotROC)
library(flextable)
library(DataExplorer)

roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, USOnly)
roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv3_100, USOnly)
roc_Lunit <- ci.auc(Xpert2Outcome_num ~ LunitScore_100, USOnly)
roc_JF1 <- ci.auc(Xpert2Outcome_num ~ JF1_100, USOnly)
roc_JF2 <- ci.auc(Xpert2Outcome_num ~ JF2_100, USOnly)
roc_IF1 <- ci.auc(Xpert2Outcome_num ~ IF1_100, USOnly)
roc_IF2 <- ci.auc(Xpert2Outcome_num ~ IF2_100, USOnly)
roc_IF3 <- ci.auc(Xpert2Outcome_num ~ IF3_100, USOnly)

USOnly_long <- gather(USOnly, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv3_100, LunitScore_100, JF1_100, IF2_100)

ggROC <- ggplot(USOnly_long, aes(d = Xpert2Outcome_num, m = AbnormalityScore, color = DeepLearningSystem)) + geom_roc(cutoffs.at = c(50,80)) + style_roc(xlab = "1 - Specificity", ylab = "Sensitivity")

ggROC <- ggROC + annotate("text", x = .75, y = .15, label = paste("Lunit INSIGHT CXR: ", round(roc_Lunit[2],2), " (95% CI:", round(roc_Lunit[1],2), "-", round(roc_Lunit[3],2), ")", "\n", "qXR: ", round(roc_qure[2],2), " (95% CI:", round(roc_qure[1],2), "-", round(roc_qure[3],2), ")", "\n", "InferReadDR: ", round(roc_IF2[2],2), " (95% CI:", round(roc_IF2[1],2), "-", round(roc_IF2[3],2), ")", "\n", "JF CXR-1: ", round(roc_JF1[2],2), " (95% CI:", round(roc_JF1[1],2), "-", round(roc_JF1[3],2), ")", "\n",  "CAD4TB: ", round(roc_CAD6[2],2), " (95% CI:", round(roc_CAD6[1],2), "-", round(roc_CAD6[3],2), ")", sep = ""), size = 3)
# 
# ggROC <- ggROC + geom_hline(yintercept = 0.8096192, linetype="dotted", color = "blue", size=0.5) + geom_vline(xintercept = 0.2105263, linetype="dotted", color = "blue", size=0.5)
# ggROC <- ggROC + geom_hline(yintercept = 0.7134269, linetype="dotted", color = "red", size=0.5) + geom_vline(xintercept = 0.1578947, linetype="dotted", color = "red", size=0.5)

ggROC <- ggROC + geom_hline(yintercept =  0.5030060, linetype="dotted", color = "blue", size=0.5) + geom_vline(xintercept = 0.1578947, linetype="dotted", color = "blue", size=0.5)
ggROC <- ggROC + geom_hline(yintercept = 0.8096192, linetype="dotted", color = "red", size=0.5) + geom_vline(xintercept = 0.2105263, linetype="dotted", color = "red", size=0.5)

ggROC
```

### 2020-07-28 Draft.Rmd
CAD6.3

@@
 Supp_Tab <- read_csv("Results/Supp Tab.csv")
+Supp_Tab_4digits <- read_csv("Results/Supp Tab 4digits.csv")
 Supp_Tab$Score[Supp_Tab$DeepLearningSystem %in% "CAD4TB"] <- Supp_Tab$Score[Supp_Tab$DeepLearningSystem %in% "CAD4TB"]/100
@@
 # View(Supp_Tab)
-Supp_Tab <- Supp_Tab[Supp_Tab$Score %in% c(0.6, 0.7, 0.8), c(2:4, 8, 9)]
+# Supp_Tab <- Supp_Tab[Supp_Tab$Score %in% c(0.6, 0.7, 0.8), c(2:4, 8, 9)]
 knitr::kable(Supp_Tab)

### 2020-07-28 ROCs.Rmd
CAD6.3

@@
 # make it long
-Adult_Valid$qXRv2_100 <- Adult_Valid$qXRv2*100
+Adult_Valid$qXRv3_100 <- Adult_Valid$qXRv3*100
 
-Adult_Valid_long <- gather(Adult_Valid, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv2_100)
+Adult_Valid_long <- gather(Adult_Valid, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv3_100)
 
 # p <- ggplot(Adult_Valid,aes(CAD4TB6))
-# p <- ggplot(Adult_Valid,aes(qXRv2))
+# p <- ggplot(Adult_Valid,aes(qXRv3))
 # p <- ggplot(Adult_Valid,aes(DrCADxScore))
@@
 # library(moments)
-# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==1, 28]) #28 CAD4TB6, 29 qXRv2, 33 Lunit
-# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==1, 29]) #29 qXRv2, 33 Lunit
+# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==1, 28]) #28 CAD4TB6, 29 qXRv3, 33 Lunit
+# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==1, 29]) #29 qXRv3, 33 Lunit
 # skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==1, 33]) #33 Lunit
 # 
-# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==0, 28]) #28 CAD4TB6, 29 qXRv2, 33 Lunit
-# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==0, 29]) #29 qXRv2, 33 Lunit
+# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==0, 28]) #28 CAD4TB6, 29 qXRv3, 33 Lunit
+# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==0, 29]) #29 qXRv3, 33 Lunit
 # skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==0, 33]) #33 Lunit
@@
 # make it long
-Adult_Valid$qXRv2_100 <- Adult_Valid$qXRv2*100
+Adult_Valid$qXRv3_100 <- Adult_Valid$qXRv3*100
 
-Adult_Valid_long <- gather(Adult_Valid, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv2_100)
+Adult_Valid_long <- gather(Adult_Valid, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv3_100)
 
@@
 roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, Adult_Valid)
-roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv2_100, Adult_Valid)
+roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv3_100, Adult_Valid)
 # roc_Lunit <- ci.auc(Xpert2Outcome_num ~ Lunit, Adult_Valid)
@@
 Adult_Valid_long$DeepLearningSystem[Adult_Valid_long$DeepLearningSystem %in% "CAD4TB6"] <- "CAD4TB"
-Adult_Valid_long$DeepLearningSystem[Adult_Valid_long$DeepLearningSystem %in% "qXRv2_100"] <- "qXR"
+Adult_Valid_long$DeepLearningSystem[Adult_Valid_long$DeepLearningSystem %in% "qXRv3_100"] <- "qXR"
 
@@
 myfunction <- function(CountryX, car.cutoff){
-a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
-b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
-c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
-d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
+a <- sum(CountryX$qXRv3 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
+b <- sum(CountryX$qXRv3 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
+c <- sum(CountryX$qXRv3 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
+d <- sum(CountryX$qXRv3 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
 dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
@@
 
-perc_above_CAR_Score<- sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
+perc_above_CAR_Score<- sum(CountryX$qXRv3 >= car.cutoff)/length(CountryX$TID_OMRS)
 Score <- qure_ai_score[i]

### 2020-07-28 SubGroup.Rmd
CAD6.3

@@
 
-  attr <- attributes(evalmod(scores = dataset$qXRv2, labels = dataset$Xpert2Outcome_num))
+  attr <- attributes(evalmod(scores = dataset$qXRv3, labels = dataset$Xpert2Outcome_num))
   aucT2 <- c("qXR ", round(attr$auc[4],3))
@@
 aucTable <- rbind(all, New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn, Female, Male)
-colnames(aucTable) <- c("DL System", "AUC", "PCAUC", "Subgroup")
-# write.csv(aucTable, "Results/aucTable.csv")
-# rm(list=(ls()))
+colnames(aucTable) <- c("AI.Algorithm", "AUC", "PCAUC", "Subgroup")
+write.csv(aucTable, "Results/aucTable.csv")
+rm(list=(ls()))
+```
+
+```{r PRAUC CI}
+data(P10N10)
+
+s1 <- c(1, 2, 3, 4)
+s2 <- c(5, 6, 7, 8)
+s3 <- matrix(1:8, 4, 2)
+
+# Join two score vectors
+scores1 <- join_scores(s1, s2)
+
+# Join two vectors and a matrix
+scores2 <- join_scores(s1, s2, s3)
+
+l1 <- c(1, 0, 1, 1)
+l2 <- c(1, 0, 1, 1)
+l3 <- c(1, 0, 1, 0)
+
+# Join two label vectors
+labels1 <- join_labels(l1, l2)
+labels2 <- join_labels(l1, l3)
+
+# A dataset with 20 samples for the good early retrieval performance level
+samps3 <- create_sim_samples(20, 10, 10, "good_er")
+
+# Calculate ROC and Precision-Recall curves
+sscurves <- evalmod(scores = P10N10$scores, labels = P10N10$labels)
+
+# Specify test dataset IDs names
+smmdat1 <- mmdata(scores1, labels2, dsids = c(1,2))
+
+# Use a sample dataset created by the create_sim_samples function
+smmdat2 <- mmdata(samps3[["scores"]], samps3[["labels"]], dsids = samps3[["dsids"]])
+
+# Calculate curves for multiple test datasets and keep all the curves
+smcurves <- evalmod(smmdat2, raw_curves = TRUE)
+
+autoplot(smcurves, "PRC", show_cb = TRUE)
 ```
@@
   roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, dataset)
-  roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv2_100, dataset)
+  roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv3_100, dataset)
   roc_Lunit <- ci.auc(Xpert2Outcome_num ~ LunitScore_100, dataset)
@@
   names(aucT) <- c("AUC", "AUCL", "AUCH")
-  aucT$DL.System <- c("CAD4TB", "qXR", "Lunit INSIGHT CXR", "JF CXR-1", "InferReadDR")
+  aucT$AI.Algorithm <- c("CAD4TB", "qXR", "Lunit INSIGHT CXR", "JF CXR-1", "InferReadDR")
 
@@
 ### AUC
-age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
 
-referral<-ggplot(aucTable[aucTable$Subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+referral<-ggplot(aucTable[aucTable$Subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
 
-history<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+history<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
 
-gender <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+gender <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
 
 ### PRC
-agePC<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
+agePC<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
 
-referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
+referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
 
-historyPC<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
+historyPC<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
 
-genderPC <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+genderPC <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
 
@@
 dev.off()
-
 ```
@@
 ### AUC
-age <-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=DL.System, y=AUC, fill=subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge()) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.7)) + theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+age <-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge()) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.7)) + theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
 age
 
-referral<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=DL.System, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))
+referral<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))
 referral
 
-history<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=DL.System, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))
+history<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))
 

### 2020-07-28 Chapter/5 Curves.R

@@ -1,45 +1,52 @@
-source("DataWrangling/GlobalOption.R")
+source("01_Data_Prep/clean.R")
+Radiologist <- read.csv("09_Results/Radiologist.csv")
+CAD_Xpert_plot_lunit <- read.csv("09_Results/CutoffTable/CAD_Xpert Cutoffs TABLE_lunit.csv")
+CAD_Xpert_plot_qXR2 <- read.csv("09_Results/CutoffTable/CAD_Xpert Cutoffs TABLE_qXR2.csv")
+CAD_Xpert_plot_qXR3 <- read.csv("09_Results/CutoffTable/CAD_Xpert Cutoffs TABLE_qXR3.csv")
+CAD_Xpert_plot_CAD4TB <- read.csv("09_Results/CutoffTable/CAD_Xpert Cutoffs TABLE_CAD4TB.csv")
 
-CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE.csv")
+CAD_Xpert_plot <- rbind(CAD_Xpert_plot_qXR2, CAD_Xpert_plot_lunit, CAD_Xpert_plot_qXR3, CAD_Xpert_plot_CAD4TB)
+rm(CAD_Xpert_plot_qXR2, CAD_Xpert_plot_lunit, CAD_Xpert_plot_qXR3, CAD_Xpert_plot_CAD4TB)
 
-
-CAD_Xpert_plot <- subset(CAD_Xpert_plot, CAD_Xpert_plot$Site %in% "BGD")
+CAD_Xpert_plot <- subset(CAD_Xpert_plot, CAD_Xpert_plot$Site %in% "ALL")
 
 ### d. Sensitivity vs Score --------------------
-base <- ggplot(CAD_Xpert_plot, aes(Score, Sens)) + geom_path(aes(color = DeepLearningSystem)) + scale_fill_manual(values=c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00")) +  scale_color_manual(values=c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00")) 
-# + geom_ribbon(aes(x = Score, ymin = Sens_L, ymax = Sens_H, color = DeepLearningSystem, fill = DeepLearningSystem), alpha= 0.2) 
[…]

### 2020-07-28 Chapter/histogram.R

@@ -12,11 +12,11 @@ hist
 dev.off()
 
 ## Density plot
-p <- ggplot(MDF_long,aes(x=AbnormalityScore, fill=XpertHistory,))+ geom_histogram(position = 'stack', alpha=0.5, breaks=seq(0,100, by=5), aes(y = ..density.., fill = XpertHistory)) + xlab("Abnormality Scores of the Deep Learning Systems") 
-density <- p + facet_wrap(~DeepLearningSystem) + theme_minimal() + theme(legend.position = "top") +scale_fill_manual(values=c("#f7f7f7", "#fbb4b9", "#91003f", "#a1dab4", "#006d2c"))+ scale_x_continuous(minor_breaks = seq(0 , 100, 10), breaks = seq(0 , 100, 10)) 
+p <- ggplot(MDF_long,aes(x=AbnormalityScore, fill=XpertHistory,))+ geom_histogram(position = 'stack', alpha=0.5, breaks=seq(0,100, by=5), aes(y = ..density.., fill = XpertHistory)) + xlab("Abnormality Scores of the AI products") 
+density <- p + facet_wrap(~DeepLearningSystem) + theme_minimal() + theme(legend.position = "bottom") +scale_fill_manual(values=c("#f7f7f7", "#fbb4b9", "#91003f", "#a1dab4", "#006d2c"))+ scale_x_continuous(minor_breaks = seq(0 , 100, 10), breaks = seq(0 , 100, 10)) 
 density
 
-tiff("Results/density.tif", width = 14, height = 8, units = "in", res = 100)
+tiff("Results/density.tif", width = 7, height = 6, units = "in", res = 100)
 density
 dev.off()
 
@@ -42,13 +42,16 @@ dev.off()
 # hist_Old
 # dev.off()
 
-# print("Xpert Positive vs Negative")
-# paste(colnames(MDF)[27], ": ",round(skewness(MDF[MDF$Xpert2Outcome_num ==1, 27]),4), "vs", round(skewness(MDF[MDF$Xpert2Outcome_num ==0, 27]),4))
[…]

### 2020-07-28 Chapter/humanAI.R

@@ -1,13 +1,7 @@
 source("radiologist.R")
 
 ########### Human vs AI ####################
-SubgroupPlot <- read.csv("Chapter/Subgroup Table/SubgroupTable.csv")
-SubgroupPlot <- SubgroupPlot[, -1]
-
-CAD_Xpert_plot <- read.csv("Results/CAD_Xpert_Precise.csv")
-
-CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% c("IF1", "JF2", "IF3"), ]
-CAD_Xpert_plot <- CAD_Xpert_plot[CAD_Xpert_plot$Site %in% "BGD", ]
+CAD_Xpert_plot <- read.csv("Results/CAD_Xpert_lunit.csv")
 
 # knitr::kable(Radiologist[(Radiologist$Referral %in% "MDF"), c(8, 10, 11)])
 Human <- Radiologist[(Radiologist$Referral %in% "MDF"), c(8, 10, 11, 4)]

### 2020-07-28 Chapter/roc.R

@@ -10,7 +10,8 @@ Radiologist <- Radiologist[Radiologist$Referral %in% "MDF", ]
 CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% c("IF1", "JF2", "IF3"), ]
 
 roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, MDF)
-roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv2_100, MDF)
+roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv3_100, MDF)
+
 roc_Lunit <- ci.auc(Xpert2Outcome_num ~ LunitScore_100, MDF)
 roc_JF1 <- ci.auc(Xpert2Outcome_num ~ JF1_100, MDF)
 roc_JF2 <- ci.auc(Xpert2Outcome_num ~ JF2_100, MDF)
@@ -18,6 +19,11 @@ roc_IF1 <- ci.auc(Xpert2Outcome_num ~ IF1_100, MDF)
 roc_IF2 <- ci.auc(Xpert2Outcome_num ~ IF2_100, MDF)
 roc_IF3 <- ci.auc(Xpert2Outcome_num ~ IF3_100, MDF)
 
+# library(pROC)
+# roc1 <- roc(Xpert2Outcome_num ~ CAD4TB6, MDF)
+# roc2 <- roc(Xpert2Outcome_num ~ qXRv3_100, MDF)
+# cov(roc1, roc2, method="obuchowski")
+# cov(roc1, roc2, method="delong")
 
 # base <- ggplot(CAD_Xpert_plot, aes(X, Sens, color = DeepLearningSystem)) + geom_path()+ geom_ribbon(aes(x = X, ymin = Sens_L, ymax = Sens_H), fill = "red", alpha= 0.2)
 

### 2020-07-28 Chapter/update qXRv3 Results.R

@@ -1,0 +1,40 @@
+colnames(BGD.qXR3)[1] <- "Sens"
+colnames(BGD.qXR3)[2] <- "Sens_L"
+colnames(BGD.qXR3)[3] <- "Sens_H"
+colnames(BGD.qXR3)[4] <- "Spec"
+colnames(BGD.qXR3)[5] <- "Spec_L"
+colnames(BGD.qXR3)[6] <- "Spec_H"
+colnames(BGD.qXR3)[7] <- "ppv"
+colnames(BGD.qXR3)[8] <- "PPV_L"
+colnames(BGD.qXR3)[9] <- "PPV_H"
+colnames(BGD.qXR3)[10] <- "npv"
+colnames(BGD.qXR3)[11] <- "NPV_L"
+colnames(BGD.qXR3)[12] <- "NPV_H"
+colnames(BGD.qXR3)[13] <- "%XpertSaved"
+colnames(BGD.qXR3)[14] <- "Score"
+colnames(BGD.qXR3)[15] <- "accuracy"
+colnames(BGD.qXR3)[16] <- "Site"
+
+BGD.qXR3$X <- 1-BGD.qXR3$Spec
+
+BGD.qXR3$Sen_95CI <- paste(percent(BGD.qXR3[, 2], suffix = ""), "-", percent(BGD.qXR3[, 3]), sep = "")
+BGD.qXR3$Spe_95CI <- paste(percent(BGD.qXR3[, 5], suffix = ""), "-", percent(BGD.qXR3[, 6]), sep = "")
+BGD.qXR3$PPV_95CI <- paste(percent(BGD.qXR3[, 8], suffix = ""), "-", percent(BGD.qXR3[, 9]), sep = "")
+BGD.qXR3$NPV_95CI <- paste(percent(BGD.qXR3[, 11], suffix = ""), "-", percent(BGD.qXR3[, 12]), sep = "")
+BGD.qXR3$NNT <- 1/BGD.qXR3$ppv
+BGD.qXR3$NNT_H <- 1/BGD.qXR3$PPV_L
+BGD.qXR3$NNT_L <- 1/BGD.qXR3$PPV_H
+
+
+
+BGD.qXR3$Sensitivity <- paste(percent(BGD.qXR3$Sens, accuracy = 0.1), " (", BGD.qXR3$Sen_95CI, ")", sep = "")
[…]

### 2020-07-28 CutoffTable.R

@@ -41,23 +41,23 @@ mylist <- NULL
 mylist <- as.list(mylist)
 
 
-# NPL_qXR2
+# NPL_qXR3
 for (i in 1 : maxV){
-  cutoff.accuracy <- myfunction(NPL, NPL$qXR2, DL.score[i])
+  cutoff.accuracy <- myfunction(NPL, NPL$qXR3, DL.score[i])
   mylist[[i]] <- list(cutoff.accuracy)
 }
-NPL.qXR2 <- data.frame(matrix(unlist(mylist), nrow=maxV, byrow=T))
-NPL.qXR2$Country  <- paste("NPL")
-NPL.qXR2$DeepLearningSystem <- paste("qXR")
+NPL.qXR3 <- data.frame(matrix(unlist(mylist), nrow=maxV, byrow=T))
+NPL.qXR3$Country  <- paste("NPL")
+NPL.qXR3$DeepLearningSystem <- paste("qXR")
 
-NPL.qXR2$Comment <- ""
-NPL.qXR2$Comment[which(abs(NPL.qXR2$X13-0.5) == min(abs(NPL.qXR2$X13-0.5)))] <- "1/2 Xpert Saved"
-NPL.qXR2$Comment[which(abs(NPL.qXR2$X13-2/3) == min(abs(NPL.qXR2$X13-2/3)))] <- "2/3 Xpert Saved"
-NPL.qXR2$Comment[which(abs(NPL.qXR2$X13-0.75) == min(abs(NPL.qXR2$X13-0.75)))] <- "3/4 Xpert Saved"
+NPL.qXR3$Comment <- ""
+NPL.qXR3$Comment[which(abs(NPL.qXR3$X13-0.5) == min(abs(NPL.qXR3$X13-0.5)))] <- "1/2 Xpert Saved"
+NPL.qXR3$Comment[which(abs(NPL.qXR3$X13-2/3) == min(abs(NPL.qXR3$X13-2/3)))] <- "2/3 Xpert Saved"
+NPL.qXR3$Comment[which(abs(NPL.qXR3$X13-0.75) == min(abs(NPL.qXR3$X13-0.75)))] <- "3/4 Xpert Saved"
 
-# NPL.qXR2$Comment[which(abs(NPL.qXR2$X1-Radiologist$Sens[1]) == min(abs(NPL.qXR2$X1-Radiologist$Sens[1])))] <- paste("Radiologists' specificity = ", Radiologist$Specificity[1], sep = "")
[…]

### 2020-07-28 DataWrangling/Cleaning.R

@@ -14,10 +14,10 @@ library(readxl)
 library(plotROC)
 library(flextable)
 library(DataExplorer)
-library("readxl")
+library(readxl)
 as.numeric.factor <- function(x) {as.numeric(levels(x))[x]}
 
-Master_df <- read.csv(file = "DataWrangling/Master_60K_OpenMRS_08_11_2018.csv", header=T)
+Master_df <- read.csv(file = "DataWrangling/BGD.csv", header=T)
 Master_df$Result.Date <- mdy(Master_df$Radiology.Result.Date)
 Master_df$Result.Year <- quarter(Master_df$Result.Date)
 
@@ -33,13 +33,18 @@ SymptomData <- read_excel("DataWrangling/ScreeningData.xlsx")
 
 Master_df <- merge(Master_df, SymptomData, by.x = "PID_OMRS", by.y = "OpenMRS Identification Number", all.x = TRUE)
 
+# # Delft 6.0.0
+# CAD6_delft <- read.table(file = "DataWrangling/CAD_delft_2018.csv", sep = ",", header = T, fill = T) 
+# colnames(CAD6_delft)[7] <- "TID_Delft"
+# CAD6_delft <- CAD6_delft[, -2]
+# CAD6_delft <- CAD6_delft[, c(1, 2, 6, 9, 10)]
 
-CAD6_delft <- read.table(file = "DataWrangling/CAD_delft_2018.csv", sep = ",", header = T, fill = T) 
-colnames(CAD6_delft)[7] <- "TID_Delft"
-CAD6_delft <- CAD6_delft[, -2]
-CAD6_delft <- CAD6_delft[, c(1, 2, 6, 9, 10)]
+# Delft 6.3.0
+CAD6_delft <- read.table(file = "DataWrangling/Delft 6.3.0.csv", sep = ",", header = T, fill = T) 
+names(CAD6_delft)[1] <- "TID_Delft"
 
-QA.BGD <- read.csv(file = "./AI Scores/qXRv2.csv", header=T, sep=",")
+
+QA.BGD <- read.csv(file = "./AI Scores/qXRv3.csv", header=T, sep=",")
 
 #### Radiologist TB, not TB ####
 # Highly TB Suggestive 
[…]

### 2020-07-28 DataWrangling/GlobalOption.R

@@ -23,7 +23,9 @@ Mode <- function(x) {
   ux[which.max(tabulate(match(x, ux)))]
 }
 
-MDF <- read.csv("DataWrangling/MDF.csv")
+# MDF <- read.csv("DataWrangling/MDF.csv")
+MDF <- read.csv("DataWrangling/MDF.6.3.csv")
+
 MDF <- MDF[!MDF$UseCase %in% c("Community screening", "Contacts"), ]
 sum(is.na(MDF$GXP.Result)==T)
 MDF <- MDF[is.na(MDF$Radiology.Result)==F, ]
@@ -31,15 +33,15 @@ MDF <- MDF[MDF$Age >=15, ]
 
 
 # Make it long
-# MDF_long <- gather(MDF, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv2_100, IF1_100, IF2_100)
-# MDF_long <- gather(MDF, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv2_100, LunitScore_100, JF1_100, JF2_100, IF1_100, IF2_100, IF3_100)
-MDF_long <- gather(MDF, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv2_100, LunitScore_100, JF1_100, IF2_100)
+# MDF_long <- gather(MDF, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv3_100, IF1_100, IF2_100)
+# MDF_long <- gather(MDF, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv3_100, LunitScore_100, JF1_100, JF2_100, IF1_100, IF2_100, IF3_100)
+MDF_long <- gather(MDF, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv3_100, LunitScore_100, JF1_100, IF2_100)
 
 MDF_long$DeepLearningSystem <- as.character(MDF_long$DeepLearningSystem)
 MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "IF2_100"] <- "InferReadDR"
 MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "LunitScore_100"] <- "Lunit INSIGHT CXR"
 MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "CAD4TB6"] <- "CAD4TB"
[…]

### 2020-07-28 Extreme AI score.R

@@ -1,84 +1,84 @@
-library(tableone)
-
-MDF[MDF$Xpert2Outcome_num %in% "1" & MDF$qXRv2_100 <0, c(1, 3, 7, 9, 14:19, 26:29)]
-
-LowQXR <- MDF[MDF$Xpert2Outcome_num %in% "1" & MDF$qXRv2_100 <45, c(1, 3, 7, 9, 14:19, 26:29)]
-# LowLunit <- MDF[MDF$Xpert2Outcome_num %in% "1" & MDF$LunitScore_100 <20, c(1, 5, 9,11, 16:21, 28, 31, 32)]
-LowCAD4TB <- MDF[MDF$Xpert2Outcome_num %in% "1" & MDF$CAD4TB6 <45, c(1, 3, 7, 9, 14:19, 26:29)]
-HighJF <- MDF[MDF$Xpert2Outcome_num %in% "0" & MDF$qXRv2_100 >80, c(1, 3, 7, 9, 14:19, 26:29)]
-
-
-## High JF score, false positive ------------------
-MDF$HighJF <- "Normal"
-MDF$HighJF[MDF$Xpert2Outcome_num %in% "0" & MDF$qXRv2_100 >80] <- "FP"
-
-# Define numeric variables
-listVar <- c("Age", "Gender",  "Xpert2Outcome_num", "MTB.Burden", "RIF.Result", "Radiology.Result", "rad.highly.TB", "rad.TB", "rad.abn", "CAD4TB6", "qXRv2", "LunitScore", "JF1", "HighJF")
-
-#Define categorical variables
-catVars <- c("Gender", "MTB.Burden", "Xpert2Outcome_num","RIF.Result",  "Radiology.Result", "rad.highly.TB", "rad.TB", "rad.abn", "HighJF")
-table1 <- CreateTableOne(vars = listVar, strata=c("HighJF"), data = MDF, factorVars = catVars)
-print(table1)
-
-
-# Every 5 point incremental ----------------
-MDF$CAD4TB_C <- cut(MDF$CAD4TB6, breaks = 50)
-MDF$qXR_C <- cut(MDF$qXRv2_100, breaks = 50)
-MDF$Lunit_C <- cut(MDF$LunitScore_100, breaks = 50)
-MDF$JF1_C <- cut(MDF$JF1_100, breaks = 50)
-MDF$JF2_C <- cut(MDF$JF2_100, breaks = 50)
-
-
[…]

### 2020-07-28 SpecificSampling.R

@@ -1,0 +1,34 @@
+# Specific sampling methods - 1.5 non-TB cases per TB case
+
+Bp <- MDF[MDF$GXP.Result %in% "MTB Detected", ]
+Bn <- MDF[MDF$GXP.Result %in% "MTB Not Detected", ]
+
+BnS <- Bn[Bn$TID_OMRS %in% sample(Bn$TID_OMRS, 5450, replace = F), ]
+
+Resampled <- rbind(Bp, BnS)
+rm(Bp, Bn, BnS)
+
+# Summary of the resampled dataset
+summary(Resampled)
+names(Resampled)
+
+
+
+#### Qure.AI in the resampled dataset
+paste("Qure.AI in the resampled dataset", "AUC=", round(ci.auc(Xpert2Outcome_num ~ qXRv3, Resampled), 3))
+
+#### QureAI in the original bangladesh dataset ########
+paste("QureAI in the original bangladesh dataset", "AUC=", round(ci.auc(Xpert2Outcome_num ~ qXRv3, MDF), 3))
+
+#### CAD4TB in the resampled dataset ####
+paste("CAD4TB in the resampled dataset","AUC=", round(ci.auc(Xpert2Outcome_num ~ CAD4TB6, Resampled), 3))
+
+#### CAD4TB in the original bangladesh dataset ########
+paste("CAD4TB in the original bangladesh dataset","AUC=", round(ci.auc(Xpert2Outcome_num ~ CAD4TB6, MDF), 3))
+
+#### Lunit in the resampled dataset ####
+paste("Lunit in the resampled dataset","AUC=", round(ci.auc(Xpert2Outcome_num ~ LunitScore, Resampled), 3))
+
+#### Lunit in the original bangladesh dataset ########
+paste("Lunit in the original bangladesh dataset", "AUC=", round(ci.auc(Xpert2Outcome_num ~ LunitScore, MDF), 3))
+

### 2020-07-28 radiologist.R

@@ -72,3 +72,4 @@ Radiologist$Sensitivity <- paste0(percent(Radiologist$Sens), ", (", percent(Radi
 Radiologist$Specificity <- paste0(percent(Radiologist$Spec), ", (", percent(Radiologist$Spec_L, suffix = ""), "-", percent(Radiologist$Spec_H), ")")
 
 
+

### 2020-09-28 SubGroup.Rmd
no subgroup update

@@
 
-```{r PRAUC CI}
-data(P10N10)
-
-s1 <- c(1, 2, 3, 4)
-s2 <- c(5, 6, 7, 8)
-s3 <- matrix(1:8, 4, 2)
-
-# Join two score vectors
-scores1 <- join_scores(s1, s2)
-
-# Join two vectors and a matrix
-scores2 <- join_scores(s1, s2, s3)
-
-l1 <- c(1, 0, 1, 1)
-l2 <- c(1, 0, 1, 1)
-l3 <- c(1, 0, 1, 0)
-
-# Join two label vectors
-labels1 <- join_labels(l1, l2)
-labels2 <- join_labels(l1, l3)
-
-# A dataset with 20 samples for the good early retrieval performance level
-samps3 <- create_sim_samples(20, 10, 10, "good_er")
-
-# Calculate ROC and Precision-Recall curves
-sscurves <- evalmod(scores = P10N10$scores, labels = P10N10$labels)
-
-# Specify test dataset IDs names
-smmdat1 <- mmdata(scores1, labels2, dsids = c(1,2))
-
-# Use a sample dataset created by the create_sim_samples function
-smmdat2 <- mmdata(samps3[["scores"]], samps3[["labels"]], dsids = samps3[["dsids"]])
-
-# Calculate curves for multiple test datasets and keep all the curves
-smcurves <- evalmod(smmdat2, raw_curves = TRUE)
-
-autoplot(smcurves, "PRC", show_cb = TRUE)
-```
-
 ```{r ROC AUC with CI}
@@
 write.csv(ROCaucTable, "Results/ROCaucTable.csv", row.names = F)
-
-```
-
-## Subgroup Curves
-```{r subgroup curves, eval=F}
-# subgroup 4 curves
-
-SubgroupPlot <- read.csv("Chapter/Subgroup Table/SubgroupTable.csv")
-SubgroupPlot <- SubgroupPlot[, -1]
-SubgroupPlot$Score[SubgroupPlot$DeepLearningSystem %in% "CAD4TB"] <- SubgroupPlot$Score[SubgroupPlot$DeepLearningSystem %in% "CAD4TB"]/100
-SubgroupPlot$subgroup <- as.character(SubgroupPlot$subgroup)
-SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "New"] <- "1.New Case"
-SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Old"] <- "2.Previously Treated Case"
-SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Young"] <- "3.Young age [15,25)"
-SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Middle"] <- "4.Middle age [25,60)"
-SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Senior"] <- "5.Old age [60,108]"
-SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "DOTS"] <- "7.Public DOTS Retesting"
-SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Referral"] <-"6.Private Public Referral"
-SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "WalkIn"] <-"8.Walk In"
-SubgroupPlot$subgroup <- as.factor(SubgroupPlot$subgroup)
-
-SubgroupPlotOrigin <- SubgroupPlot
-# SubgroupPlot <- SubgroupPlotOrigin
-# Choose the DL System
-# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "CAD4TB", ]
-# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "IF2", ]
-# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "JF1", ]
-# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "Lunit", ]
-SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "qXR", ]
-
-### GO TO AND RUN source("Chapter/Subgroup Table/SubGroupPlot.R")
-
 ```

### 2020-09-28 Chapter/5 Curves.R

@@ -1,42 +1,57 @@
+# CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE.csv")
+CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE_CAD6.3.csv")
+
+CAD_Xpert_plot <- subset(CAD_Xpert_plot, CAD_Xpert_plot$Site %in% "BGD")
+
+table(CAD_Xpert_plot$DeepLearningSystem)
+CAD_Xpert_plot$DeepLearningSystem <- as.character(CAD_Xpert_plot$DeepLearningSystem)
+
+# CAD_Xpert_plot$DeepLearningSystem[grep("CAD4TB", CAD_Xpert_plot$DeepLearningSystem)] <- "P1"
+# CAD_Xpert_plot$DeepLearningSystem[grep("qXR", CAD_Xpert_plot$DeepLearningSystem)] <- "P3"
+# CAD_Xpert_plot$DeepLearningSystem[grep("Lunit INSIGHT CXR", CAD_Xpert_plot$DeepLearningSystem)] <- "P2"
+
+CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% c("IF1", "JF2", "IF3"), ]
+
 
 
 ### d. Sensitivity vs Score --------------------
-base <- ggplot(CAD_Xpert_plot, aes(Score, Sens)) + geom_path(aes(color = AI)) + scale_fill_manual(values=c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00")) +  scale_color_manual(values=c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00")) 
-# + geom_ribbon(aes(x = Score, ymin = Sens_L, ymax = Sens_H, color = AI, fill = AI), alpha= 0.2) 
+base <- ggplot(CAD_Xpert_plot, aes(Score, Sens)) + geom_path(aes(color = DeepLearningSystem)) + scale_fill_manual(values=c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00")) +  scale_color_manual(values=c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00")) 
+# + geom_ribbon(aes(x = Score, ymin = Sens_L, ymax = Sens_H, color = DeepLearningSystem, fill = DeepLearningSystem), alpha= 0.2) 
 
[…]

### 2020-09-28 Chapter/Subgroup Table/SubGroupPlot.R

@@ -1,3 +1,33 @@
+##################################### Inital ##################
+# subgroup 4 curves
+SubgroupPlot <- read.csv("Chapter/Subgroup Table/SubgroupTable.csv")
+SubgroupPlot <- SubgroupPlot[, -1]
+SubgroupPlot$Score[SubgroupPlot$DeepLearningSystem %in% "CAD4TB"] <- SubgroupPlot$Score[SubgroupPlot$DeepLearningSystem %in% "CAD4TB"]/100
+SubgroupPlot$subgroup <- as.character(SubgroupPlot$subgroup)
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "New"] <- "1.New Case"
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Old"] <- "2.Previously Treated Case"
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Young"] <- "3.Young age [15,25)"
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Middle"] <- "4.Middle age [25,60)"
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Senior"] <- "5.Old age [60,108]"
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "DOTS"] <- "7.Public DOTS Retesting"
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Referral"] <-"6.Private Public Referral"
+SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "WalkIn"] <-"8.Walk In"
+SubgroupPlot$subgroup <- as.factor(SubgroupPlot$subgroup)
+
+SubgroupPlotOrigin <- SubgroupPlot
+# SubgroupPlot <- SubgroupPlotOrigin
+# Choose the DL System
+# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "CAD4TB", ]
+# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "IF2", ]
+# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "JF1", ]
+# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "Lunit", ]
[…]

### 2020-09-28 Chapter/histogram.R

@@ -1,6 +1,16 @@
 source("DataWrangling/GlobalOption.R")
 
 
+table(MDF_long$DeepLearningSystem)
+MDF_long$DeepLearningSystem <- as.character(MDF_long$DeepLearningSystem)
+
+# MDF_long$DeepLearningSystem[grep("CAD4TB", MDF_long$DeepLearningSystem)] <- "P1"
+# MDF_long$DeepLearningSystem[grep("qXR", MDF_long$DeepLearningSystem)] <- "P3"
+# MDF_long$DeepLearningSystem[grep("Lunit INSIGHT CXR", MDF_long$DeepLearningSystem)] <- "P2"
+
+MDF_long <- MDF_long[!MDF_long$DeepLearningSystem %in% c("IF1", "JF2", "IF3"), ]
+
+
 
 ## Histogram
 p <- ggplot(MDF_long,aes(x=AbnormalityScore, fill=XpertHistory,))+ geom_histogram(position = 'stack', alpha=0.5, breaks=seq(0,100, by=5), aes(y = ..count.., fill = XpertHistory)) + xlab("Abnormality Scores of the Deep Learning Systems") 
@@ -16,7 +26,7 @@ p <- ggplot(MDF_long,aes(x=AbnormalityScore, fill=XpertHistory,))+ geom_histogra
 density <- p + facet_wrap(~DeepLearningSystem) + theme_minimal() + theme(legend.position = "bottom") +scale_fill_manual(values=c("#f7f7f7", "#fbb4b9", "#91003f", "#a1dab4", "#006d2c"))+ scale_x_continuous(minor_breaks = seq(0 , 100, 10), breaks = seq(0 , 100, 10)) 
 density
 
-tiff("Results/density.tif", width = 7, height = 6, units = "in", res = 100)
+tiff("Results/density.tif", width = 10, height = 6, units = "in", res = 100)
 density
 dev.off()
 
@@ -52,6 +62,6 @@ paste(colnames(MDF)[29], ": ",round(skewness(MDF[MDF$Xpert2Outcome_num ==1, 29])
 paste(colnames(MDF)[30], ": ",round(skewness(MDF[MDF$Xpert2Outcome_num ==1, 30]),4), "vs", round(skewness(MDF[MDF$Xpert2Outcome_num ==0, 30]),4))
[…]

### 2020-09-28 Chapter/humanAI.R

@@ -1,7 +1,9 @@
 source("radiologist.R")
 
 ########### Human vs AI ####################
-CAD_Xpert_plot <- read.csv("Results/CAD_Xpert_lunit.csv")
+CAD_Xpert_plot <- read.csv("Results/CAD_Xpert_CAD6.3.csv")
+CAD_Xpert_plot <- subset(CAD_Xpert_plot, CAD_Xpert_plot$Site %in% "BGD")
+
 
 # knitr::kable(Radiologist[(Radiologist$Referral %in% "MDF"), c(8, 10, 11)])
 Human <- Radiologist[(Radiologist$Referral %in% "MDF"), c(8, 10, 11, 4)]
@@ -9,7 +11,7 @@ Human <- Human[c(3,2,1), ]
 Human <- rbind(Human, Human, Human, Human, Human)
 
 
-AI <- CAD_Xpert_plot[CAD_Xpert_plot$Comment !="" , c(17, 14, 4, 24, 25, 18)]
+AI <- CAD_Xpert_plot[CAD_Xpert_plot$Comment !="" , c(17, 14, 4, 24, 25, 18,27,28)]
 AI$Subject <- paste(AI$DeepLearningSystem, AI$Comment)
 require(data.table)
 AI <- as.data.table(AI)
@@ -17,7 +19,7 @@ AI <- as.data.table(AI)
 AI <- AI[AI[, .I[which.max(Spec)], by=Subject]$V1]
 
 AI <- AI[grep("Radiologists' ", AI$Comment), ]
-humanAI <- cbind(Human, AI[, c(1,2,4, 5, 3)])
+humanAI <- cbind(Human, AI[, c(1,2,7,8, 3)])
 humanAI$Diff <- percent(humanAI[, 9]- humanAI[, 4])
 humanAI <- humanAI[, c(1,2,3,5:8, 10, 9,4)]
 colnames(humanAI) <- c("Human Benchmark", "Sensitivity", "Specificy", "DL Product", "Score", "DL Sensitivity", "DL Specificity", "Difference", "specAI", "specH")
@@ -40,10 +42,10 @@ for (i in 1:15){
 
 
 humanAI$SpecificyIncrease <- paste0(humanAI$Difference, " (", humanAI$CI, ")")
-humanAI <- humanAI[c(3,6,9,12,15, 2,5,8,11,14, 1,4,7,10,13), -c(6, 8:11)]
[…]

### 2020-09-28 Chapter/roc.R

@@ -1,5 +1,5 @@
 source("radiologist.R")
-# CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE.csv")
+CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE.csv")
 CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE_CAD6.3.csv")
 
 
@@ -20,11 +20,13 @@ roc_JF1 <- ci.auc(Xpert2Outcome_num ~ JF1_100, MDF)
 
 roc_IF2 <- ci.auc(Xpert2Outcome_num ~ IF2_100, MDF)
 
-# library(pROC)
-# roc1 <- roc(Xpert2Outcome_num ~ CAD4TB6, MDF)
-# roc2 <- roc(Xpert2Outcome_num ~ qXRv3_100, MDF)
-# cov(roc1, roc2, method="obuchowski")
-# cov(roc1, roc2, method="delong")
+### PRC 
+
+library("PRROC")
+
+pr.curve(scores.class0 = MDF[MDF$Xpert2Outcome_num %in% "0", 29], scores.class1 = MDF[MDF$Xpert2Outcome_num %in% "1", 29])
+  
+
 
 # base <- ggplot(CAD_Xpert_plot, aes(X, Sens, color = DeepLearningSystem)) + geom_path()+ geom_ribbon(aes(x = X, ymin = Sens_L, ymax = Sens_H), fill = "red", alpha= 0.2)
 
@@ -50,7 +52,7 @@ ggROC <- ggROC + geom_point(data = Radiologist, mapping = aes(X, Sens, shape = A
 ggROC
 
 
-  tiff("Results/Figure-2 ROCs.tif", width = 10, height = 7.9, units = "in", res = 100)
+tiff("Results/Figure-2 ROCs.tif", width = 10, height = 7.9, units = "in", res = 100)
 ggROC
 dev.off()
 

### 2020-09-28 CutoffTable.R

@@ -3,13 +3,14 @@
 # NPL <- Nepal_Cameroon[Nepal_Cameroon$Country %in% "NPL", ]
 # CAM <- Nepal_Cameroon[Nepal_Cameroon$Country %in% "CAM", ]
 
-maxV <- 10001
-sep <- 0.0001
-sepdeflt <- 0.01
+source("DataWrangling/GlobalOption.R")
+# maxV <- 10001
+# sep <- 0.0001
+# sepdeflt <- 0.01
 
-# maxV<- 101
-# sep <- 0.01
-# sepdeflt <- 1
+maxV<- 101
+sep <- 0.01
+sepdeflt <- 1
 
 ### Set up a function
 myfunction <- function(CountryX, DL.System, car.cutoff){
@@ -397,7 +398,7 @@ CAD_Xpert$Specificity <- paste(percent(CAD_Xpert$Spec, accuracy = 0.1), " (", CA
 CAD_Xpert$PPV <- paste(percent(CAD_Xpert$ppv, accuracy = 0.1), " (", CAD_Xpert$PPV_95CI, ")", sep = "")
 CAD_Xpert$NPV <- paste(percent(CAD_Xpert$npv, accuracy = 0.1), " (", CAD_Xpert$NPV_95CI, ")", sep = "")
 CAD_Xpert$nnt <- paste(round(CAD_Xpert$NNT, 1), " (", round(CAD_Xpert$NNT_L, 1), "-", round(CAD_Xpert$NNT_H, 1), ")", sep = "")
-CAD_Xpert$`%XpertSaved` <- round(CAD_Xpert$`%XpertSaved`, 8)
+CAD_Xpert$`%XpertSaved%` <- round(CAD_Xpert$`%XpertSaved%`, 8)
 CAD_Xpert$accuracy <- round(CAD_Xpert$accuracy, 3)
 
 CAD_Xpert$DeepLearningSystem <- as.character(CAD_Xpert$DeepLearningSystem)
@@ -427,17 +428,21 @@ SuppTable <- CAD_Xpert %>%
   select(Site, DeepLearningSystem, Score, Sensitivity, Specificity, PPV, NPV,nnt, `XpertSaved%`)
 View(SuppTable)
 
-CAD_Xpert_plot <- CAD_Xpert %>%
[…]

### 2021-01-15 SubGroup.Rmd
lancet

@@
 
-Referral <- subset(MDF, MDF$UseCase %in% "PrivatePublicReferral")
-DOTS <- subset(MDF, MDF$UseCase %in% "PublicDOTSRetesting")
-WalkIn <- subset(MDF, MDF$UseCase %in% "WalkIn")
+PrivateReferral <-subset(MDF, MDF$UseCase %in% "PrivateReferral")
+PublicReferral <-subset(MDF, MDF$UseCase %in% "PublicReferral")
+DOTS <-subset(MDF, MDF$UseCase %in% "PublicDOTSRetesting")
+WalkIn <-subset(MDF, MDF$UseCase %in% "WalkIn")
+Community <-subset(MDF, MDF$UseCase %in% "Community screening")
+Contacts <-subset(MDF, MDF$UseCase %in% "Contacts")
 # Missing <- subset(MDF, is.na(MDF$UseCase)==T)
@@
 
-Referral_long  <- subset(MDF_long, MDF_long$UseCase %in% "PrivatePublicReferral")
-DOTS_long  <- subset(MDF_long, MDF_long$UseCase %in% "PublicDOTSRetesting")
-WalkIn_long  <- subset(MDF_long, MDF_long$UseCase %in% "WalkIn")
+PrivateReferral_long <-subset(MDF_long, MDF_long$UseCase %in% "PrivateReferral")
+PublicReferral_long <-subset(MDF_long, MDF_long$UseCase %in% "PublicReferral")
+DOTS_long <-subset(MDF_long, MDF_long$UseCase %in% "PublicDOTSRetesting")
+WalkIn_long <-subset(MDF_long, MDF_long$UseCase %in% "WalkIn")
+Community_long <-subset(MDF_long, MDF_long$UseCase %in% "Community screening")
+Contacts_long <-subset(MDF_long, MDF_long$UseCase %in% "Contacts")
+# Missing <- subset(MDF_long, is.na(MDF_long$UseCase)==T)
 
@@
 ## All
-
 library(precrec)
@@
 
-## Old only
+## Old on ly
 l <- ROCPRC(Old)
@@
 
-## Referral only
-l <- ROCPRC(Referral)
-Referral <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
-Referral$subgroup <- "Referred"
+## PrivateReferral only
+l <- ROCPRC(PrivateReferral)
+PrivateReferral <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+PrivateReferral$subgroup <- "PrivateReferral"
+
+## PublicReferral only
+l <- ROCPRC(PublicReferral)
+PublicReferral <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+PublicReferral$subgroup <- "PublicReferral"
 
@@
 WalkIn$subgroup <- "WalkIn"
+
+## Community only
+l <- ROCPRC(Community)
+Community <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+Community$subgroup <- "Community"
+
+## Contacts only
+l <- ROCPRC(Contacts)
+Contacts <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
+Contacts$subgroup <- "Contacts"
 
@@
 
-aucTable <- rbind(all, New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn, Female, Male)
+aucTable <- rbind(all, New, Old, Young, Middle, Senior, PrivateReferral, PublicReferral, DOTS, WalkIn,Community, Contacts, Female, Male)
+
 colnames(aucTable) <- c("AI.Algorithm", "AUC", "PCAUC", "Subgroup")
@@
 
-aucTable$Subgroup <- factor(aucTable$Subgroup, levels = c("Young age", "Middle age", "Old age", "Referred", "DOTS retested", "WalkIn", "New cases", "Previously treated cases", "Female", "Male"))
+aucTable$Subgroup <- factor(aucTable$Subgroup, levels = c("All","Young age", "Middle age", "Old age", "PrivateReferral", "PublicReferral", "DOTS", "WalkIn", "Community", "Contacts", "New cases", "Previously treated cases", "Female", "Male"))
 ### AUC
@@
 
-referral<-ggplot(aucTable[aucTable$Subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+referral<-ggplot(aucTable[aucTable$Subgroup %in% c("PrivateReferral", "PublicReferral", "DOTS", "WalkIn", "Community", "Contacts"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
 
@@
 
-referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
+referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("PrivateReferral", "PublicReferral", "DOTS", "WalkIn", "Community", "Contacts"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
 
@@
 
-tiff("Results/PRC ROC AUC plot.tif", width = 18, height = 8, units = "in", res = 100)
+tiff("Results/PRC ROC AUC plot 3.tif", width = 20, height = 8, units = "in", res = 110)
 require(gridExtra)
+grid.arrange(age, referral, history, gender, agePC, referralPC, historyPC, genderPC, ncol=4)
+dev.off()
 
-grid.arrange(age, referral, history, gender, agePC, referralPC, historyPC, genderPC, ncol=4)
-# grid.arrange(age, referral, history, ncol=3)
-
-dev.off()
 # rm(age, referral, history, agePC, referralPC, historyPC, gender, genderPC)

### 2021-01-15 Chapter/humanAI.R

@@ -31,40 +31,44 @@ rm(AI, Human, humanAI)
 humanAI <- read_csv("Results/humanAI.csv")
 
 
-humanAI$specD <- percent(humanAI[, 9]- humanAI[, 4])
+humanAI$specD <- percent(humanAI$AI_Spec- humanAI$Huan_Spec)
+humanAI$PPVD <- percent(humanAI$AI_PPV- humanAI$Huan_PPV)
+humanAI$NPVD <- percent(humanAI$AI_NPV- humanAI$Huan_NPV)
+
+
 # humanAI <- humanAI[, c(1,2,3,5:8, 10, 9,4)]
-# colnames(humanAI) <- c("Human Benchmark", "Sensitivity", "Specificy", "DL Product", "Score", "DL Sensitivity", "DL Specificity", "Difference", "specAI", "specH")
+# colnames(humanAI) <- c("Human Benchmark", "Sensitivity", "Specificy", "DL Product", "Score", "DL Sensitivity", "DL Specificity", "Difference", "AI_Spec", "specH")
 
 
 ### McNemar test specificity 
 healthy <- sum(MDF$Xpert2Outcome_num %in% "0")
 
 # library(readr)
-# humanAI <- read_csv("Results/humanAI.csv", 
-#                     col_types = cols(`Diff.specificity` = col_number()))
+# humanAI <- read_csv("Results/humanAI.csv", col_types = cols(`Diff.specificity` = col_number()))
+
 humanAI$specCI <- ""
 
 for (i in 1:15){
-  test <- prop.test(x=c(humanAI$specAI[i]*healthy, healthy*humanAI$specH[i]), n=c(healthy, healthy))
-  humanAI$CI[i] <- paste0(percent(test$conf.int[1], suffix = ""), "-", percent(test$conf.int[2]))
+  test <- prop.test(x=c(humanAI$AI_Spec[i]*healthy, healthy*humanAI$Huan_Spec[i]), n=c(healthy, healthy))
+  humanAI$specCI[i] <- paste0(percent(test$conf.int[1], suffix = ""), "-", percent(test$conf.int[2]))
   # return(humanAI)
 }
 
 
-humanAI$specCI <- ""
+humanAI$PPVCI <- ""
 
 for (i in 1:15){
[…]

### 2021-06-24 SubGroup.Rmd
lancet publication

@@
 
-```{r eval=F}
+```{r run manually eval=F}
+rm(list = ls())
+
 source("DataWrangling/GlobalOption.R")
@@
 Contacts <-subset(MDF, MDF$UseCase %in% "Contacts")
-# Missing <- subset(MDF, is.na(MDF$UseCase)==T)
-
-New_long <- MDF_long[MDF_long$TB.Medication.History %in% "No",]
-Old_long <- MDF_long[MDF_long$TB.Medication.History %in% "Yes",]
-Young_long <- MDF_long[MDF_long$AgeGroup %in% "[15,25)",]
-Middle_long <- MDF_long[MDF_long$AgeGroup %in% "[25,60)",]
-Senior_long <- MDF_long[MDF_long$AgeGroup %in% "[60,108]",]
-
-PrivateReferral_long <-subset(MDF_long, MDF_long$UseCase %in% "PrivateReferral")
-PublicReferral_long <-subset(MDF_long, MDF_long$UseCase %in% "PublicReferral")
-DOTS_long <-subset(MDF_long, MDF_long$UseCase %in% "PublicDOTSRetesting")
-WalkIn_long <-subset(MDF_long, MDF_long$UseCase %in% "WalkIn")
-Community_long <-subset(MDF_long, MDF_long$UseCase %in% "Community screening")
-Contacts_long <-subset(MDF_long, MDF_long$UseCase %in% "Contacts")
-# Missing <- subset(MDF_long, is.na(MDF_long$UseCase)==T)
-
 ```
 
-```{r 2 AUC}
+```{r 2 AUCs in subgroups}
 ## All
@@
   attr <- attributes(evalmod(scores = dataset$CAD4TB6, labels = dataset$Xpert2Outcome_num))
-  aucT1 <- c("CAD4TB ", round(attr$auc[4],3))
+  aucT1 <- c("CAD4TB ", round(attr$auc[4],4))
 
   attr <- attributes(evalmod(scores = dataset$qXRv3, labels = dataset$Xpert2Outcome_num))
-  aucT2 <- c("qXR ", round(attr$auc[4],3))
+  aucT2 <- c("qXR ", round(attr$auc[4],4))
 
   attr <- attributes(evalmod(scores = dataset$LunitScore, labels = dataset$Xpert2Outcome_num))
-  aucT3 <- c("Lunit INSIGHT CXR", round(attr$auc[4],3))
+  aucT3 <- c("Lunit INSIGHT CXR", round(attr$auc[4],4))
 
   attr <- attributes(evalmod(scores = dataset$JF1, labels = dataset$Xpert2Outcome_num))
-  aucT4 <- c("JF CXR-1", round(attr$auc[4],3))
+  aucT4 <- c("JF CXR-1", round(attr$auc[4],4))
 
   attr <- attributes(evalmod(scores = dataset$IF2, labels = dataset$Xpert2Outcome_num))
-  aucT5 <- c("InferReadDR ", round(attr$auc[4],3))
+  aucT5 <- c("InferReadDR ", round(attr$auc[4],4))
 
@@
 
-## Old on ly
+## Old only
 l <- ROCPRC(Old)
@@
 
-colnames(aucTable) <- c("AI.Algorithm", "AUC", "PCAUC", "Subgroup")
+colnames(aucTable) <- c("AI.Algorithm", "AUC", "PRAUC", "Subgroup")
 write.csv(aucTable, "Results/aucTable.csv")
@@
 ```{r ROC AUC with CI}
-
 library(pROC)
@@
   roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv3_100, dataset)
-  roc_Lunit <- ci.auc(Xpert2Outcome_num ~ LunitScore_100, dataset)
-  roc_JF1 <- ci.auc(Xpert2Outcome_num ~ JF1_100, dataset)
-  roc_IF2 <- ci.auc(Xpert2Outcome_num ~ IF2_100, dataset)
+  roc_Lunit <- ci.auc(Xpert2Outcome_num ~ LunitScore, dataset)
+  roc_JF1 <- ci.auc(Xpert2Outcome_num ~ JF1, dataset)
+  roc_IF2 <- ci.auc(Xpert2Outcome_num ~ IF2, dataset)
 
@@
 
-## Referral only
-Referral <- ROC(Referral)
-Referral$subgroup <- "Referred"
+## PrivateReferral only
+PrivateReferral <- ROC(PrivateReferral)
+PrivateReferral$subgroup <- "PrivateReferral"
+
+## PublicReferral only
+PublicReferral <- ROC(PublicReferral)
+PublicReferral$subgroup <- "PublicReferral"
 
@@
 
-## Walk-in only
+## WalkIn only
 WalkIn <- ROC(WalkIn)
@@
 
-ROCaucTable <- rbind(New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn)
+## Community only
+Community <- ROC(Community)
+Community$subgroup <- "Community"
+
+## Contacts only
+Contacts <- ROC(Contacts)
+Contacts$subgroup <- "Contacts"
+
+## Female only
+Female <- ROC(Female)
+Female$subgroup <- "Female"
+
+## Male only
+Male <- ROC(Male)
+Male$subgroup <- "Male"
+
+ROCaucTable <- rbind(New, Old, Young, Middle, Senior, PrivateReferral, PublicReferral, DOTS, WalkIn,Community, Contacts, Female, Male)
 View(ROCaucTable)
@@
 ```{r Bar chart}
+rm(list = ls())
+
 aucTable <- read.csv("Results/aucTable.csv")
@@
 
-aucTable$Subgroup <- factor(aucTable$Subgroup, levels = c("All","Young age", "Middle age", "Old age", "PrivateReferral", "PublicReferral", "DOTS", "WalkIn", "Community", "Contacts", "New cases", "Previously treated cases", "Female", "Male"))
+aucTable$Subgroup <- factor(aucTable$Subgroup, levels = c("All","Young age", "Middle age", "Old age", "PrivateReferral", "PublicReferral", "DOTS retested", "WalkIn", "Community", "Contacts", "New cases", "Previously treated cases", "Female", "Male"))
 ### AUC
-age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+# age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+ geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+# 
+# 
+# referral<-ggplot(aucTable[aucTable$Subgroup %in% c("PrivateReferral", "PublicReferral", "DOTS retested", "WalkIn", "Community", "Contacts"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+# 
+# history<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90) + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+# 
+# gender <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+ geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90) +theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
 
-referral<-ggplot(aucTable[aucTable$Subgroup %in% c("PrivateReferral", "PublicReferral", "DOTS", "WalkIn", "Community", "Contacts"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+### AUC with CI
+ROCaucTable <- read.csv("Results/ROCaucTable.csv")
+ROCaucTable$AUC <- round(ROCaucTable$AUC, 4)
 
-history<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+ROCaucTable$subgroup <- factor(ROCaucTable$subgroup, levels = c("All","Young age", "Middle age", "Old age", "PrivateReferral", "PublicReferral", "DOTS retested", "WalkIn", "Community", "Contacts", "New cases", "Previously treated cases", "Female", "Male"))
 
-gender <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+age <-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge()) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.7)) + geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90) + theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+age
+
+referral<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("PrivateReferral", "PublicReferral", "DOTS retested", "WalkIn", "Community", "Contacts"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal() + geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))
+referral
+
+history<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+ theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))
+
+gender<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Female", "Male"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+ theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))
 
 ### PRC
-agePC<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
+agePC<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=PRAUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+ geom_text(aes(label=PRAUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
 
-referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("PrivateReferral", "PublicReferral", "DOTS", "WalkIn", "Community", "Contacts"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
+referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("PrivateReferral", "PublicReferral", "DOTS retested", "WalkIn", "Community", "Contacts"), ], aes(x=AI.Algorithm, y=PRAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+ geom_text(aes(label=PRAUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
 
-historyPC<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
+historyPC<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=PRAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+ geom_text(aes(label=PRAUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+theme_minimal() + theme(legend.position = "top") +  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
 
-genderPC <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+genderPC <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=AI.Algorithm, y=PRAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+ geom_text(aes(label=PRAUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
 
-tiff("Results/PRC ROC AUC plot 3.tif", width = 20, height = 8, units = "in", res = 110)
+# 
+# tiff("Results/PRC ROC AUC plot 3.tif", width = 20, height = 8, units = "in", res = 110)
+# require(gridExtra)
+# grid.arrange(age, referral, history, gender, agePC, referralPC, historyPC, genderPC, ncol=4)
+# dev.off()
+
+tiff("Results/Figure3_250.tif", width = 12, height = 14, units = "in", res = 250)
 require(gridExtra)
-grid.arrange(age, referral, history, gender, agePC, referralPC, historyPC, genderPC, ncol=4)
+grid.arrange(age, referral, history, gender, agePC, referralPC, historyPC, genderPC, ncol=2)
 dev.off()
 
-# rm(age, referral, history, agePC, referralPC, historyPC, gender, genderPC)
-
-tiff("Results/PRC AUC plot.tif", width = 9, height = 8, units = "in", res = 100)
-grid.arrange(agePC, referralPC, historyPC, genderPC, ncol=2)
-dev.off()
+# tiff("Results/PRC AUC plot.tif", width = 9, height = 8, units = "in", res = 100)
+# grid.arrange(agePC, referralPC, historyPC, genderPC, ncol=2)
+# dev.off()
 ```
@@
 ROCaucTable <- read.csv("Results/ROCaucTable.csv")
-ROCaucTable$subgroup <- factor(ROCaucTable$subgroup, levels = c("Young age", "Middle age", "Old age", "Referred", "DOTS retested", "WalkIn", "New cases", "Previously treated cases"))
-### AUC
-age <-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge()) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.7)) + theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
+ROCaucTable$AUC <- round(ROCaucTable$AUC, 3)
+
+ROCaucTable$subgroup <- factor(ROCaucTable$subgroup, levels = c("All","Young age", "Middle age", "Old age", "PrivateReferral", "PublicReferral", "DOTS retested", "WalkIn", "Community", "Contacts", "New cases", "Previously treated cases", "Female", "Male"))
+
+### AUC with CI
+age <-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge()) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.7)) + geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90) + theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
 age
 
-referral<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))
+referral<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("PrivateReferral", "PublicReferral", "DOTS retested", "WalkIn", "Community", "Contacts"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal() + geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))
 referral
 
-history<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))
+history<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+ theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))
 
-tiff("Results/ROC_AUC plot.tif", width = 13, height = 3, units = "in", res = 100)
+gender<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Female", "Male"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+ theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))
+
+tiff("Results/Figure4.tif", width = 12, height = 7, units = "in", res = 250)
 require(gridExtra)
+grid.arrange(age, referral, history, gender, ncol=2)
+dev.off()
 
-grid.arrange(age, referral, history, ncol=3)
-
-dev.off()
-rm(age, referral, history)
 ```

### 2021-06-24 Chapter/5 Curves.R

@@ -1,86 +1,0 @@
-# CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE.csv")
-CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE_CAD6.3.csv")
-
-CAD_Xpert_plot <- subset(CAD_Xpert_plot, CAD_Xpert_plot$Site %in% "BGD")
-
-table(CAD_Xpert_plot$DeepLearningSystem)
-CAD_Xpert_plot$DeepLearningSystem <- as.character(CAD_Xpert_plot$DeepLearningSystem)
-
-# CAD_Xpert_plot$DeepLearningSystem[grep("CAD4TB", CAD_Xpert_plot$DeepLearningSystem)] <- "P1"
-# CAD_Xpert_plot$DeepLearningSystem[grep("qXR", CAD_Xpert_plot$DeepLearningSystem)] <- "P3"
-# CAD_Xpert_plot$DeepLearningSystem[grep("Lunit INSIGHT CXR", CAD_Xpert_plot$DeepLearningSystem)] <- "P2"
-
-CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% c("IF1", "JF2", "IF3"), ]
-
-
-
-### d. Sensitivity vs Score --------------------
-base <- ggplot(CAD_Xpert_plot, aes(Score, Sens)) + geom_path(aes(color = DeepLearningSystem)) + scale_fill_manual(values=c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00")) +  scale_color_manual(values=c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00")) 
-# + geom_ribbon(aes(x = Score, ymin = Sens_L, ymax = Sens_H, color = DeepLearningSystem, fill = DeepLearningSystem), alpha= 0.2) 
-
[…]

### 2021-06-24 Chapter/6 Curves.R

@@ -1,0 +1,86 @@
+# CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE.csv")
+CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE_CAD6.3.csv")
+
+CAD_Xpert_plot <- subset(CAD_Xpert_plot, CAD_Xpert_plot$Site %in% "BGD")
+
+table(CAD_Xpert_plot$DeepLearningSystem)
+CAD_Xpert_plot$DeepLearningSystem <- as.character(CAD_Xpert_plot$DeepLearningSystem)
+
+# CAD_Xpert_plot$DeepLearningSystem[grep("CAD4TB", CAD_Xpert_plot$DeepLearningSystem)] <- "P1"
+# CAD_Xpert_plot$DeepLearningSystem[grep("qXR", CAD_Xpert_plot$DeepLearningSystem)] <- "P3"
+# CAD_Xpert_plot$DeepLearningSystem[grep("Lunit INSIGHT CXR", CAD_Xpert_plot$DeepLearningSystem)] <- "P2"
+
+CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% c("IF1", "JF2", "IF3"), ]
+
+
+
+### d. Sensitivity vs Score --------------------
+base <- ggplot(CAD_Xpert_plot, aes(Score, Sens)) + geom_path(aes(color = DeepLearningSystem)) + scale_fill_manual(values=c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00")) +  scale_color_manual(values=c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00")) 
+# + geom_ribbon(aes(x = Score, ymin = Sens_L, ymax = Sens_H, color = DeepLearningSystem, fill = DeepLearningSystem), alpha= 0.2) 
+
[…]

### 2021-06-24 Chapter/Compare AUCs.R

@@ -1,0 +1,134 @@
+source("radiologist.R")
+# CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE_CAD6.3.csv")
+# CAD_Xpert_plot <- subset(CAD_Xpert_plot, CAD_Xpert_plot$Site %in% "BGD")
+# Radiologist <- Radiologist[Radiologist$Referral %in% "MDF", ]
+
+# Creating the subgroups
+New <- MDF[MDF$TB.Medication.History %in% "No",]
+Old <- MDF[MDF$TB.Medication.History %in% "Yes",]
+
+Female <- MDF[MDF$Gender %in% "F", ]
+Male <- MDF[MDF$Gender %in% "M", ]
+
+Young <- MDF[MDF$AgeGroup %in% "[15,25)",]
+Middle <- MDF[MDF$AgeGroup %in% "[25,60)",]
+Senior <- MDF[MDF$AgeGroup %in% "[60,108]",]
+
+PrivateReferral <-subset(MDF, MDF$UseCase %in% "PrivateReferral")
+PublicReferral <-subset(MDF, MDF$UseCase %in% "PublicReferral")
+DOTS <-subset(MDF, MDF$UseCase %in% "PublicDOTSRetesting")
+WalkIn <-subset(MDF, MDF$UseCase %in% "WalkIn")
+Community <-subset(MDF, MDF$UseCase %in% "Community screening")
+Contacts <-subset(MDF, MDF$UseCase %in% "Contacts")
+
+# CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% c("IF1", "JF2", "IF3", "InferReadDR", "JF CXR-1", "Lunit INSIGHT CXR", "qXR"), ]
+
+#### Calculate the CIs of AUC of ROC --------
+# roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, MDF)
+# roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv3_100, MDF)
+# roc_Lunit <- ci.auc(Xpert2Outcome_num ~ LunitScore_100, MDF)
+# roc_JF1 <- ci.auc(Xpert2Outcome_num ~ JF1_100, MDF)
+# roc_IF2 <- ci.auc(Xpert2Outcome_num ~ IF2_100, MDF)
+
+
+
+
+
+##### Subgroup CI  -----
+
[…]

### 2021-06-24 Chapter/roc.R

@@ -1,41 +1,40 @@
 source("radiologist.R")
-# CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE.csv")
 CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE_CAD6.3.csv")
 
+# MDF <- read.csv("DataWrangling/MDF.6.3.csv")
+# MDF <- read.csv(file = "C:/Users/zhizh/OneDrive - Stop TB Partnership/UNOPS/10 Paper Writing/CAR software/03 Nepal_Cameroon/CAR -- 03 Nepal_Cameroon/Nepal_Cameroon.csv")
 
 CAD_Xpert_plot <- subset(CAD_Xpert_plot, CAD_Xpert_plot$Site %in% "BGD")
-
-# MDF <- read.csv(file = "C:/Users/zhizh/OneDrive - Stop TB Partnership/UNOPS/10 Paper Writing/CAR software/03 Nepal_Cameroon/CAR -- 03 Nepal_Cameroon/Nepal_Cameroon.csv")
 
 Radiologist <- Radiologist[Radiologist$Referral %in% "MDF", ]
 
 # CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% c("IF1", "JF2", "IF3"), ]
 
 CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% c("IF1", "JF2", "IF3", "InferReadDR", "JF CXR-1", "Lunit INSIGHT CXR", "qXR"), ]
+
 roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, MDF)
 roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv3_100, MDF)
 roc_Lunit <- ci.auc(Xpert2Outcome_num ~ LunitScore_100, MDF)
 roc_JF1 <- ci.auc(Xpert2Outcome_num ~ JF1_100, MDF)
 roc_IF2 <- ci.auc(Xpert2Outcome_num ~ IF2_100, MDF)
 
-# roc_CAD6 <- roc(Xpert2Outcome_num ~ CAD4TB6, MDF)
[…]

### 2021-06-24 radiologist.R

@@ -131,7 +131,7 @@ rval$elements[c(59, 55, 51, 47)]
 
 Any <- rval$elements[c(59, 55, 51, 47)]
 
-rm(TP, FP, TN, FN)
+rm(TP, FP, TN, FN, Any, rval)
 
 
 

### 2021-08-18 2.0 Version Comparison/Clean.Rmd
Aug 18 update

```{r Clean}
Sys.setenv(LANG = "en")
library(ggplot2)
library(scales)
library(epiR)
library(ggthemes)
library(RColorBrewer)
library(plyr)
library(reshape2)
library(pROC) # contain function roc
library(tidyverse)
library(dplyr)
library(lubridate)
library(readxl)
library(plotROC)
library(flextable)
library(DataExplorer)
library(readxl)
as.numeric.factor <- function(x) {as.numeric(levels(x))[x]}

Master_df <- read.csv(file = "DataWrangling/BGD.csv", header=T)
Master_df$Result.Date <- mdy(Master_df$Radiology.Result.Date)
Master_df$Result.Year <- quarter(Master_df$Result.Date)

Master_df$Xpert2Outcome_num <- as.character(Master_df$GXP.Result)
Master_df$Xpert2Outcome_num[Master_df$GXP.Result %in% "MTB Detected"] <- "1"
Master_df$Xpert2Outcome_num[Master_df$GXP.Result %in% "MTB Not Detected"] <- "0"
Master_df$Xpert2Outcome_num <- as.numeric(Master_df$Xpert2Outcome_num)

Master_df <- Master_df %>%
  filter(Result.Date < as.Date("2017-01-01"))

SymptomData <- read_excel("DataWrangling/ScreeningData.xlsx")

Master_df <- merge(Master_df, SymptomData, by.x = "PID_OMRS", by.y = "OpenMRS Identification Number", all.x = TRUE)

#### Radiologist TB, not TB ####
# Highly TB Suggestive 
Master_df$rad.highly.TB <- "0"
Master_df$rad.highly.TB [Master_df$Radiology.Result == "Highly TB Suggestive" ] <- "1"
Master_df$rad.highly.TB [Master_df$Radiology.Result == "" | Master_df$Radiology.Result == "Image Unclear" ] <- "NA"

# Highly+ possibly
Master_df$rad.TB <- "0"
Master_df$rad.TB [Master_df$Radiology.Result == "Highly TB Suggestive" | Master_df$Radiology.Result =="TB Possible Signs" ] <- "1"
Master_df$rad.TB [Master_df$Radiology.Result == "" | Master_df$Radiology.Result == "Image Unclear"] <- "NA"

# Any abnormality
Master_df$rad.abn <- "0"
Master_df$rad.abn [Master_df$Radiology.Result == "Highly TB Suggestive" | Master_df$Radiology.Result =="TB Possible Signs" | Master_df$Radiology.Result == "Non-TB Abnormality"] <- "1"
Master_df$rad.abn [Master_df$Radiology.Result == "" | Master_df$Radiology.Result == "Image Unclear"] <- "NA"

### Add AI score ------
# Delft CAD4TB6
CAD6_delft <- read.table(file = "DataWrangling/CAD_delft_2018.csv", sep = ",", header = T, fill = T)
colnames(CAD6_delft)[7] <- "TID_Delft"
CAD6_delft <- CAD6_delft[, -2]
CAD6_delft <- CAD6_delft[, c(1, 2, 6, 9, 10)]
# 
# Delft CAD4TB7
CAD7_delft <- read.table(file = "DataWrangling/Delft 6.3.0.csv", sep = ",", header = T, fill = T)
names(CAD7_delft)[1] <- "TID_Delft"
names(CAD7_delft)[2] <- "CAD4TB7"

# qXR V 2 & 3
QA2.BGD <- read.csv(file = "./AI Scores/qXRv2.csv", header=T, sep=",")
QA3.BGD <- read.csv(file = "./AI Scores/qXRv3.csv", header=T, sep=",")

###  Clean MasterDF 
n_occur <- data.frame(table(Master_df$PID_OMRS))
Master_df <- (Master_df[Master_df$PID_OMRS %in% n_occur$Var1[n_occur$Freq < 2], ]) # execute to remove the duplicated PID
n_occur <- data.frame(table(Master_df$TID_OMRS))
MasterDF1TID <- (Master_df[Master_df$TID_OMRS %in% n_occur$Var1[n_occur$Freq == 1], ]) # MasterDF1TID is a subset withOUT duplicated TID

rm(n_occur)
###  Clean Delft
# CAD6_delft <- CAD6_delft[grep("^.{12}$",CAD6_delft$TID_Delft), ]  #TID_Delft is
DeDuDelft_CAD6 <- CAD6_delft[!duplicated(CAD6_delft[c("TID_Delft",  "CAD4TB6")]), ]
n_occur <- data.frame(table(DeDuDelft_CAD6$TID_Delft))
# But I decided to discard all records with the same TID with different CAD6 (due to inability to trace the true identify of them). 1857 are removed
DelftClean <- DeDuDelft_CAD6[DeDuDelft_CAD6$TID_Delft %in% n_occur$Var1[n_occur$Freq == 1], ] # A df with just unique TID from Delft that don't have different CAD6 score --> 26051
rm(DeDuDelft_CAD6)

###  Merge 
MDF_Delft6 <- merge(MasterDF1TID, CAD6_delft, by.x = "TID_OMRS", by.y = "TID_Delft")
MDF_Delft67 <- merge(MDF_Delft6, CAD7_delft, by.x = "TID_OMRS", by.y = "TID_Delft")

MDF_Delft_qxr2 <- merge(MDF_Delft67, QA2.BGD, by.x = "TID_OMRS", by.y = "TID")
MDF_Delft_qxr23 <- merge(MDF_Delft_qxr2, QA3.BGD, by.x = "TID_OMRS", by.y = "TID")
rm(MDF_Delft)

### Save csv ##
MDF <- MDF_Delft_qxr23
write.csv(MDF, "2.0 Version Comparison/MDF.csv", row.names = F)
rm(list = ls(all.names = TRUE))

```

```{r subset}
MDF <- read.csv("2.0 Version Comparison/MDF.csv")

MDF$Symptoms <- "1"
MDF$Symptoms[MDF$Cough %in% "No" & MDF$Fever %in% "No" & MDF$`Active Breathing Shortness` %in% "No" & MDF$`Weight Loss` %in% "No" & MDF$Haemoptysis %in% "No"] <- "0"

MDF$AgeGroup [MDF$Age<25]<- "[15,25)"
MDF$AgeGroup [MDF$Age>=25 & MDF$Age<60]<- "[25,60)"
MDF$AgeGroup [MDF$Age>=60]<- "[60,108]"

MDF <- MDF[, -c(3,4)]

MDF$qXRv3_100 <- MDF$qXRv3*100

MDF <- subset(MDF, is.na(MDF$CAD4TB6)==F)
MDF <- subset(MDF, is.na(MDF$CAD4TB7)==F)
MDF <- subset(MDF, is.na(MDF$qXRv2)==F)
MDF <- subset(MDF, is.na(MDF$qXRv3)==F)
MDF <- MDF[MDF$CAD4TB6 !="-1",]
MDF <- MDF[MDF$CAD4TB7 !="-1",]

Master_df <- read.csv("AI Scores/Master_df.csv")
MDF$Referral <- Master_df$type[match(MDF$PID_OMRS, Master_df$PID)]
MDF_Original <- MDF

#### Referral Source -----------------------
library(readxl)
Referral <- read_excel("DataWrangling/referral_source.xlsx")
Referral <- Referral[, -1]
colnames(Referral)[3] <- "ReferralSource"
Referral$ReferralSource <- tolower(Referral$ReferralSource)

MDF$ReferralSource <- Referral$ReferralSource[match(MDF$TID_OMRS, Referral$TID_OMRS)]

Classification_ZZ <- read_excel("DataWrangling/Classification_ZZ.xlsx")
Classification_ZZ$ReferralUnit <- tolower(Classification_ZZ$ReferralUnit)
MDF$UseCase <- Classification_ZZ$Unit[match(MDF$ReferralSource, Classification_ZZ$ReferralUnit)]
table(MDF$UseCase)

rm(Classification_ZZ, Referral, Master_df)

#### Save  -----------------------
write.csv(MDF, "2.0 Version Comparison/MDF.csv", row.names = F)

```

```{r exclude}
# MDF <- read.csv("2.0 Version Comparison/MDF.csv")
MDF <- read_csv("2.0 Version Comparison/MDF.csv")
sum(is.na(MDF$GXP.Result)==T)
sum(MDF$Age <15)
sum(is.na(MDF$Radiology.Result)==F)
MDF <- MDF[is.na(MDF$Radiology.Result)==F, ]
MDF <- MDF[MDF$Age >=15, ]
summary(MDF$Radiology.Result) # removing 16 images that were marked  unclear
MDF <- MDF[MDF$Radiology.Result != "", ]
MDF <- MDF[MDF$Radiology.Result != "Image Unclear", ]

# Make it long
# MDF_long <- gather(MDF, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv3_100, IF1_100, IF2_100)
# MDF_long <- gather(MDF, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv3_100, LunitScore_100, JF1_100, JF2_100, IF1_100, IF2_100, IF3_100)
MDF_long <- gather(MDF, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv3_100, LunitScore_100, JF1_100, IF2_100)

MDF_long$DeepLearningSystem <- as.character(MDF_long$DeepLearningSystem)
MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "IF2_100"] <- "InferReadDR"
MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "LunitScore_100"] <- "Lunit INSIGHT CXR"
MDF_long$DeepLearningSystem[MDF_long$DeepLearningSystem %in% "CAD4TB6"] <- "CAD4TB"
```

### 2021-08-18 2.0 Version Comparison/CutoffTable.R

@@ -1,0 +1,449 @@
+# Nepal_Cameroon <- read.csv(file = "C:/Users/zhizh/OneDrive - Stop TB Partnership/UNOPS/10 Paper Writing/CAR software/03 Nepal_Cameroon/CAR -- 03 Nepal_Cameroon/Clean/Nepal_Cameroon.csv", header = T)
+# Nepal_Cameroon <- Nepal_Cameroon[, -1]
+# NPL <- Nepal_Cameroon[Nepal_Cameroon$Country %in% "NPL", ]
+# CAM <- Nepal_Cameroon[Nepal_Cameroon$Country %in% "CAM", ]
+
+source("DataWrangling/GlobalOption.R")
+# maxV <- 10001
+# sep <- 0.0001
+# sepdeflt <- 0.01
+
+maxV<- 101
+sep <- 0.01
+sepdeflt <- 1
+
+### Set up a function
+myfunction <- function(CountryX, DL.System, car.cutoff){
+  a <- sum(DL.System >= car.cutoff & CountryX$XPERT_pos =="1")
+  b <- sum(DL.System >= car.cutoff & CountryX$XPERT_pos =="0")
+  c <- sum(DL.System < car.cutoff & CountryX$XPERT_pos =="1")
+  d <- sum(DL.System < car.cutoff & CountryX$XPERT_pos =="0")
+  dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
+  rval <- epi.tests(dat, conf.level = 0.95)
+  sensitivity <- as.vector(round((rval$elements$sensitivity),8))
+  specificity <- as.vector(round((rval$elements$specificity),8))
+  pv.positive <- as.vector(round((rval$elements$pv.positive),8))
+  pv.negative <- as.vector(round((rval$elements$pv.negative),8))
+  correct.rate <- (a+d)/length(CountryX$XPERT_pos)
+
+  XpertSaved<- 1-round(sum(DL.System >= car.cutoff)/length(CountryX$Age), 8)
+  Score <- DL.score[i]
+
+  accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, XpertSaved, Score, correct.rate)
+
+  return(accuracy)
+}
+
[…]

### 2021-08-18 2.0 Version Comparison/clean.R

@@ -1,0 +1,151 @@
+Sys.setenv(LANG = "en")
+library(ggplot2)
+library(scales)
+library(epiR)
+library(ggthemes)
+library(RColorBrewer)
+library(plyr)
+library(reshape2)
+library(pROC) # contain function roc
+library(tidyverse)
+library(dplyr)
+library(lubridate)
+library(readxl)
+library(plotROC)
+library(flextable)
+library(DataExplorer)
+library(readxl)
+as.numeric.factor <- function(x) {as.numeric(levels(x))[x]}
+
+Master_df <- read.csv(file = "DataWrangling/BGD.csv", header=T)
+Master_df$Result.Date <- mdy(Master_df$Radiology.Result.Date)
+Master_df$Result.Year <- quarter(Master_df$Result.Date)
+
+Master_df$Xpert2Outcome_num <- as.character(Master_df$GXP.Result)
+Master_df$Xpert2Outcome_num[Master_df$GXP.Result %in% "MTB Detected"] <- "1"
+Master_df$Xpert2Outcome_num[Master_df$GXP.Result %in% "MTB Not Detected"] <- "0"
+Master_df$Xpert2Outcome_num <- as.numeric(Master_df$Xpert2Outcome_num)
+
+Master_df <- Master_df %>%
+  filter(Result.Date < as.Date("2017-01-01"))
+
+SymptomData <- read_excel("DataWrangling/ScreeningData.xlsx")
+
+Master_df <- merge(Master_df, SymptomData, by.x = "PID_OMRS", by.y = "OpenMRS Identification Number", all.x = TRUE)
+
+#### Radiologist TB, not TB ####
+# Highly TB Suggestive 
+Master_df$rad.highly.TB <- "0"
+Master_df$rad.highly.TB [Master_df$Radiology.Result == "Highly TB Suggestive" ] <- "1"
+Master_df$rad.highly.TB [Master_df$Radiology.Result == "" | Master_df$Radiology.Result == "Image Unclear" ] <- "NA"
+
+# Highly+ possibly
+Master_df$rad.TB <- "0"
+Master_df$rad.TB [Master_df$Radiology.Result == "Highly TB Suggestive" | Master_df$Radiology.Result =="TB Possible Signs" ] <- "1"
[…]

### 2021-08-18 2.0 Version Comparison/histogram.R

@@ -1,0 +1,67 @@
+source("DataWrangling/GlobalOption.R")
+
+
+table(MDF_long$DeepLearningSystem)
+MDF_long$DeepLearningSystem <- as.character(MDF_long$DeepLearningSystem)
+
+# MDF_long$DeepLearningSystem[grep("CAD4TB", MDF_long$DeepLearningSystem)] <- "P1"
+# MDF_long$DeepLearningSystem[grep("qXR", MDF_long$DeepLearningSystem)] <- "P3"
+# MDF_long$DeepLearningSystem[grep("Lunit INSIGHT CXR", MDF_long$DeepLearningSystem)] <- "P2"
+
+MDF_long <- MDF_long[!MDF_long$DeepLearningSystem %in% c("IF1", "JF2", "IF3"), ]
+
+
+
+## Histogram
+p <- ggplot(MDF_long,aes(x=AbnormalityScore, fill=XpertHistory,))+ geom_histogram(position = 'stack', alpha=0.5, breaks=seq(0,100, by=5), aes(y = ..count.., fill = XpertHistory)) + xlab("Abnormality Scores of the Deep Learning Systems") 
+hist <- p + facet_wrap(~DeepLearningSystem) + theme_minimal() + theme(legend.position = "top") +scale_fill_manual(values=c("#f7f7f7", "#fbb4b9", "#91003f", "#a1dab4", "#006d2c"))
+
+
+tiff("Results/Histogram.tif", width = 14, height = 8, units = "in", res = 100)
+hist
+dev.off()
+
+## Density plot
+p <- ggplot(MDF_long,aes(x=AbnormalityScore, fill=XpertHistory,))+ geom_histogram(position = 'stack', alpha=0.5, breaks=seq(0,100, by=5), aes(y = ..density.., fill = XpertHistory)) + xlab("Abnormality Scores of the AI products") 
+density <- p + facet_wrap(~DeepLearningSystem) + theme_minimal() + theme(legend.position = "bottom") +scale_fill_manual(values=c("#f7f7f7", "#fbb4b9", "#91003f", "#a1dab4", "#006d2c"))+ scale_x_continuous(minor_breaks = seq(0 , 100, 10), breaks = seq(0 , 100, 10)) 
+density
+
+tiff("Results/density.tif", width = 10, height = 6, units = "in", res = 100)
+density
+dev.off()
+
+
+
[…]

### 2021-08-18 2.0 Version Comparison/roc.R

@@ -1,0 +1,95 @@
+source("radiologist.R")
+CAD_Xpert_plot <- read.csv("Results/CAD_Xpert Cutoffs TABLE_CAD6.3.csv")
+
+# MDF <- read.csv("DataWrangling/MDF.6.3.csv")
+# MDF <- read.csv(file = "C:/Users/zhizh/OneDrive - Stop TB Partnership/UNOPS/10 Paper Writing/CAR software/03 Nepal_Cameroon/CAR -- 03 Nepal_Cameroon/Nepal_Cameroon.csv")
+
+CAD_Xpert_plot <- subset(CAD_Xpert_plot, CAD_Xpert_plot$Site %in% "BGD")
+
+Radiologist <- Radiologist[Radiologist$Referral %in% "MDF", ]
+
+# CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% c("IF1", "JF2", "IF3"), ]
+
+CAD_Xpert_plot <- CAD_Xpert_plot[!CAD_Xpert_plot$DeepLearningSystem %in% c("IF1", "JF2", "IF3", "InferReadDR", "JF CXR-1", "Lunit INSIGHT CXR", "qXR"), ]
+
+roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, MDF)
+roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv3_100, MDF)
+roc_Lunit <- ci.auc(Xpert2Outcome_num ~ LunitScore_100, MDF)
+roc_JF1 <- ci.auc(Xpert2Outcome_num ~ JF1_100, MDF)
+roc_IF2 <- ci.auc(Xpert2Outcome_num ~ IF2_100, MDF)
+
+roc_CAD6 <- roc(Xpert2Outcome_num ~ CAD4TB6, MDF)
+roc_qure <- roc(Xpert2Outcome_num ~ qXRv3_100, MDF)
+roc_Lunit <- roc(Xpert2Outcome_num ~ LunitScore_100, MDF)
+roc_JF1 <- roc(Xpert2Outcome_num ~ JF1_100, MDF)
+roc_IF2 <- roc(Xpert2Outcome_num ~ IF2_100, MDF)
+
+roc.test(roc_CAD6, roc_qure)
+roc.test(roc_CAD6, roc_Lunit)
[…]

### 2021-08-18 2.0 Version Comparison/table1.R

@@ -1,0 +1,72 @@
+source("DataWrangling/GlobalOption.R")
+
+# MDF$qXRv3 <- MDF$qXRv3*100
+# MDF$LunitScore <- MDF$LunitScore*100
+# MDF$IF1 <- MDF$IF*100
+# MDF$JF1 <- MDF$JF1*100
+
+library(tableone)
+# MDF <- MDF[MDF$Xpert2Outcome_num %in% "1", ]
+
+# Define numeric variables
+listVar <- c("Age", "AgeGroup", "Gender", "Cough", "Fever", "Active.Breathing.Shortness", "Weight.Loss","Haemoptysis", "Symptoms", "TB.Medication.History", "Xpert2Outcome_num", "MTB.Burden", "RIF.Result", "UseCase", "Radiology.Result", "CAD4TB6", "qXRv3", "LunitScore", "JF1", "IF1", "IF2")
+
+#Define categorical variables
+catVars <- c( "AgeGroup", "Gender", "Cough", "Fever", "Active.Breathing.Shortness", "Weight.Loss","Haemoptysis", "Symptoms", "TB.Medication.History", "Xpert2Outcome_num", "MTB.Burden", "RIF.Result", "UseCase", "Radiology.Result")
+
+
+table1 <- CreateTableOne(vars = listVar, strata=c("Xpert2Outcome_num"), data = MDF, factorVars = catVars)
+tableType <- CreateTableOne(vars = listVar, strata=c("Radiology.Result"), data = MDF, factorVars = catVars)
+table1.all <- CreateTableOne(vars = listVar, data = MDF, factorVars = catVars)
+tablethistory <- CreateTableOne(vars = listVar, strata=c("TB.Medication.History"), data = MDF, factorVars = catVars)
+# 
+# 
+# #### p-value ---------
+# summary(table1$CatTable)
+# summary(table1$ContTable)
+# 
+# 
+# summary(tableType$CatTable)
+# summary(tableType$ContTable)
+# 
+# summary(tablethistory$CatTable)
+# summary(tablethistory$ContTable)
+
+
+
+#### ---------
+
+
+table1 <- print(table1, nonnormal = c("Age", "CAD4TB6", "qXRv3", "LunitScore", "JF1", "IF1", "IF2"), cramVars = "Gender", catDigits = 1, contDigits = 1, noSpaces = TRUE)
[…]

### 2021-08-18 Chapter/Subgroup Table/DOTS.R

@@ -1,507 +1,0 @@
-source("DataWrangling/GlobalOption.R")
-source("radiologist.R")
-Radiologist <- Radiologist[c(1:3), ]
-
-Referral <- subset(MDF, MDF$UseCase %in% "PrivatePublicReferral")
-DOTS <- subset(MDF, MDF$UseCase %in% "PublicDOTSRetesting")
-WalkIn <- subset(MDF, MDF$UseCase %in% "WalkIn")
-# Missing <- subset(MDF, is.na(MDF$UseCase)==T)
-
-###### Qure.AI Score by 0.0001 #########
-qure_ai_score <- seq(0,1, by = 0.0001)
-
-mylist <- NULL
-mylist <- as.list(mylist)
-
-for (i in 1:10001){
-  myfunction <- function(CountryX, car.cutoff){
-    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
-    colnames(dat) <- c("Dis+","Dis-")
-    rownames(dat) <- c("Test+","Test-")
-    rval <- epi.tests(dat, conf.level = 0.95)
-    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
-    specificity <- as.vector(round((rval$elements$specificity),4))
-    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
-    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
-    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
-    
-    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
-    Score <- qure_ai_score[i]
-    
-    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
-    
-    return(accuracy)
-  }
-  
[…]

### 2021-08-18 Chapter/Subgroup Table/Middle.R

@@ -1,505 +1,0 @@
-## Cutoff Table (Full)
-source("DataWrangling/GlobalOption.R")
-source("radiologist.R")
-Radiologist <- Radiologist[c(1:3), ]
-
-
-
-###### Qure.AI Score by 0.0001 #########
-qure_ai_score <- seq(0,1, by = 0.0001)
-
-mylist <- NULL
-mylist <- as.list(mylist)
-
-for (i in 1:10001){
-  myfunction <- function(CountryX, car.cutoff){
-    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
-    colnames(dat) <- c("Dis+","Dis-")
-    rownames(dat) <- c("Test+","Test-")
-    rval <- epi.tests(dat, conf.level = 0.95)
-    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
-    specificity <- as.vector(round((rval$elements$specificity),4))
-    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
-    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
-    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
-    
-    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
-    Score <- qure_ai_score[i]
-    
-    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
-    
-    return(accuracy)
-  }
-  
-  accuracy <- myfunction(Middle, qure_ai_score[i])
-  mylist[[i]] <- list(accuracy)
-  
-}
-
-QureDF <- data.frame(matrix(unlist(mylist), nrow=10001, byrow=T))
-QureDF$Country <- paste("Bangladesh")
-
[…]

### 2021-08-18 Chapter/Subgroup Table/Missing.R

@@ -1,509 +1,0 @@
-## Cutoff Table (Full)
-source("DataWrangling/GlobalOption.R")
-source("radiologist.R")
-Radiologist <- Radiologist[c(1:3), ]
-Private <- subset(MDF, MDF$Referral %in% "Private Provider")
-Public <- subset(MDF, MDF$Referral %in% "Public DOTS Facilities")
-WalkIn <- subset(MDF, MDF$Referral %in% "Walk-in")
-Missing <- subset(MDF, is.na(MDF$Referral)==T)
-
-
-
-###### Qure.AI Score by 0.0001 #########
-qure_ai_score <- seq(0,1, by = 0.0001)
-
-mylist <- NULL
-mylist <- as.list(mylist)
-
-for (i in 1:10001){
-  myfunction <- function(CountryX, car.cutoff){
-    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
-    colnames(dat) <- c("Dis+","Dis-")
-    rownames(dat) <- c("Test+","Test-")
-    rval <- epi.tests(dat, conf.level = 0.95)
-    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
-    specificity <- as.vector(round((rval$elements$specificity),4))
-    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
-    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
-    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
-    
-    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
-    Score <- qure_ai_score[i]
-    
-    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
-    
-    return(accuracy)
-  }
-  
[…]

### 2021-08-18 Chapter/Subgroup Table/New.R

@@ -1,504 +1,0 @@
-## Cutoff Table (Full)
-source("DataWrangling/GlobalOption.R")
-source("radiologist.R")
-Radiologist <- Radiologist[c(1:3), ]
-
-
-###### Qure.AI Score by 0.0001 #########
-qure_ai_score <- seq(0,1, by = 0.0001)
-
-mylist <- NULL
-mylist <- as.list(mylist)
-
-for (i in 1:10001){
-  myfunction <- function(CountryX, car.cutoff){
-    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
-    colnames(dat) <- c("Dis+","Dis-")
-    rownames(dat) <- c("Test+","Test-")
-    rval <- epi.tests(dat, conf.level = 0.95)
-    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
-    specificity <- as.vector(round((rval$elements$specificity),4))
-    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
-    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
-    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
-    
-    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
-    Score <- qure_ai_score[i]
-    
-    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
-    
-    return(accuracy)
-  }
-  
-  accuracy <- myfunction(New, qure_ai_score[i])
-  mylist[[i]] <- list(accuracy)
-  
-}
-
-QureDF <- data.frame(matrix(unlist(mylist), nrow=10001, byrow=T))
-QureDF$Country <- paste("Bangladesh")
-
[…]

### 2021-08-18 Chapter/Subgroup Table/Old.R

@@ -1,505 +1,0 @@
-## Cutoff Table (Full)
-source("DataWrangling/GlobalOption.R")
-source("radiologist.R")
-Radiologist <- Radiologist[c(1:3), ]
-
-
-
-###### Qure.AI Score by 0.0001 #########
-qure_ai_score <- seq(0,1, by = 0.0001)
-
-mylist <- NULL
-mylist <- as.list(mylist)
-
-for (i in 1:10001){
-  myfunction <- function(CountryX, car.cutoff){
-    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
-    colnames(dat) <- c("Dis+","Dis-")
-    rownames(dat) <- c("Test+","Test-")
-    rval <- epi.tests(dat, conf.level = 0.95)
-    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
-    specificity <- as.vector(round((rval$elements$specificity),4))
-    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
-    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
-    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
-    
-    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
-    Score <- qure_ai_score[i]
-    
-    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
-    
-    return(accuracy)
-  }
-  
-  accuracy <- myfunction(Old, qure_ai_score[i])
-  mylist[[i]] <- list(accuracy)
-  
-}
-
-QureDF <- data.frame(matrix(unlist(mylist), nrow=10001, byrow=T))
-QureDF$Country <- paste("Bangladesh")
-
[…]

### 2021-08-18 Chapter/Subgroup Table/Referral.R

@@ -1,508 +1,0 @@
-source("DataWrangling/GlobalOption.R")
-source("radiologist.R")
-Radiologist <- Radiologist[c(1:3), ]
-
-Referral <- subset(MDF, MDF$UseCase %in% "PrivatePublicReferral")
-DOTS <- subset(MDF, MDF$UseCase %in% "PublicDOTSRetesting")
-WalkIn <- subset(MDF, MDF$UseCase %in% "WalkIn")
-# Missing <- subset(MDF, is.na(MDF$UseCase)==T)
-
-
-###### Qure.AI Score by 0.0001 #########
-qure_ai_score <- seq(0,1, by = 0.0001)
-
-mylist <- NULL
-mylist <- as.list(mylist)
-
-for (i in 1:10001){
-  myfunction <- function(CountryX, car.cutoff){
-    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
-    colnames(dat) <- c("Dis+","Dis-")
-    rownames(dat) <- c("Test+","Test-")
-    rval <- epi.tests(dat, conf.level = 0.95)
-    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
-    specificity <- as.vector(round((rval$elements$specificity),4))
-    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
-    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
-    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
-    
-    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
-    Score <- qure_ai_score[i]
-    
-    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
-    
-    return(accuracy)
-  }
-  
[…]

### 2021-08-18 Chapter/Subgroup Table/Senior.R

@@ -1,505 +1,0 @@
-## Cutoff Table (Full)
-source("DataWrangling/GlobalOption.R")
-source("radiologist.R")
-Radiologist <- Radiologist[c(1:3), ]
-
-
-
-###### Qure.AI Score by 0.0001 #########
-qure_ai_score <- seq(0,1, by = 0.0001)
-
-mylist <- NULL
-mylist <- as.list(mylist)
-
-for (i in 1:10001){
-  myfunction <- function(CountryX, car.cutoff){
-    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
-    colnames(dat) <- c("Dis+","Dis-")
-    rownames(dat) <- c("Test+","Test-")
-    rval <- epi.tests(dat, conf.level = 0.95)
-    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
-    specificity <- as.vector(round((rval$elements$specificity),4))
-    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
-    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
-    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
-    
-    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
-    Score <- qure_ai_score[i]
-    
-    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
-    
-    return(accuracy)
-  }
-  
-  accuracy <- myfunction(Senior, qure_ai_score[i])
-  mylist[[i]] <- list(accuracy)
-  
-}
-
-QureDF <- data.frame(matrix(unlist(mylist), nrow=10001, byrow=T))
-QureDF$Country <- paste("Bangladesh")
-
[…]

### 2021-08-18 Chapter/Subgroup Table/SubGroupPlot.R

@@ -1,101 +1,0 @@
-##################################### Inital ##################
-# subgroup 4 curves
-SubgroupPlot <- read.csv("Chapter/Subgroup Table/SubgroupTable.csv")
-SubgroupPlot <- SubgroupPlot[, -1]
-SubgroupPlot$Score[SubgroupPlot$DeepLearningSystem %in% "CAD4TB"] <- SubgroupPlot$Score[SubgroupPlot$DeepLearningSystem %in% "CAD4TB"]/100
-SubgroupPlot$subgroup <- as.character(SubgroupPlot$subgroup)
-SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "New"] <- "1.New Case"
-SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Old"] <- "2.Previously Treated Case"
-SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Young"] <- "3.Young age [15,25)"
-SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Middle"] <- "4.Middle age [25,60)"
-SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Senior"] <- "5.Old age [60,108]"
-SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "DOTS"] <- "7.Public DOTS Retesting"
-SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Referral"] <-"6.Private Public Referral"
-SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "WalkIn"] <-"8.Walk In"
-SubgroupPlot$subgroup <- as.factor(SubgroupPlot$subgroup)
-
-SubgroupPlotOrigin <- SubgroupPlot
-# SubgroupPlot <- SubgroupPlotOrigin
-# Choose the DL System
-# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "CAD4TB", ]
-# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "IF2", ]
-# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "JF1", ]
[…]

### 2021-08-18 Chapter/Subgroup Table/WalkIn.R

@@ -1,506 +1,0 @@
-source("DataWrangling/GlobalOption.R")
-source("radiologist.R")
-Radiologist <- Radiologist[c(1:3), ]
-Private <- subset(MDF, MDF$Referral %in% "Private Provider")
-Public <- subset(MDF, MDF$Referral %in% "Public DOTS Facilities")
-WalkIn <- subset(MDF, MDF$Referral %in% "Walkin")
-Missing <- subset(MDF, is.na(MDF$Referral)==T)
-
-###### Qure.AI Score by 0.0001 #########
-qure_ai_score <- seq(0,1, by = 0.0001)
-
-mylist <- NULL
-mylist <- as.list(mylist)
-
-for (i in 1:10001){
-  myfunction <- function(CountryX, car.cutoff){
-    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
-    colnames(dat) <- c("Dis+","Dis-")
-    rownames(dat) <- c("Test+","Test-")
-    rval <- epi.tests(dat, conf.level = 0.95)
-    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
-    specificity <- as.vector(round((rval$elements$specificity),4))
-    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
-    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
-    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
-    
-    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
-    Score <- qure_ai_score[i]
-    
-    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
-    
-    return(accuracy)
-  }
-  
[…]

### 2021-08-18 Chapter/Subgroup Table/Young.R

@@ -1,505 +1,0 @@
-## Cutoff Table (Full)
-# source("DataWrangling/GlobalOption.R")
-# source("radiologist.R")
-Radiologist <- Radiologist[c(1:3), ]
-
-
-
-###### Qure.AI Score by 0.0001 #########
-qure_ai_score <- seq(0,1, by = 0.0001)
-
-mylist <- NULL
-mylist <- as.list(mylist)
-
-for (i in 1:10001){
-  myfunction <- function(CountryX, car.cutoff){
-    a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
-    d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
-    dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
-    colnames(dat) <- c("Dis+","Dis-")
-    rownames(dat) <- c("Test+","Test-")
-    rval <- epi.tests(dat, conf.level = 0.95)
-    sensitivity <- as.vector(round((rval$elements$sensitivity),4))
-    specificity <- as.vector(round((rval$elements$specificity),4))
-    pv.positive <- as.vector(round((rval$elements$pv.positive),4))
-    pv.negative <- as.vector(round((rval$elements$pv.negative),4))
-    accuracy <- round((a+d)/length(CountryX$Xpert2Outcome_num),4)
-    
-    perc_xpert_saved<- 1-sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
-    Score <- qure_ai_score[i]
-    
-    accuracy <- cbind(sensitivity, specificity, pv.positive, pv.negative, perc_xpert_saved, Score, accuracy)
-    
-    return(accuracy)
-  }
-  
-  accuracy <- myfunction(Young, qure_ai_score[i])
-  mylist[[i]] <- list(accuracy)
-  
-}
-
-QureDF <- data.frame(matrix(unlist(mylist), nrow=10001, byrow=T))
-QureDF$Country <- paste("Bangladesh")
-
[…]

### 2021-08-18 Chapter/table1.R

@@ -1,11 +1,10 @@
 source("DataWrangling/GlobalOption.R")
 
-MDF$qXRv3 <- MDF$qXRv3*100
-MDF$LunitScore <- MDF$LunitScore*100
-MDF$IF2 <- MDF$IF2*100
-MDF$JF1 <- MDF$JF1*100
+# MDF$qXRv3 <- MDF$qXRv3*100
+# MDF$LunitScore <- MDF$LunitScore*100
+# MDF$IF1 <- MDF$IF*100
+# MDF$JF1 <- MDF$JF1*100
 
-MDF <- subset(MDF, MDF$Age > 15)
 library(tableone)
 # MDF <- MDF[MDF$Xpert2Outcome_num %in% "1", ]
 
@@ -20,7 +19,22 @@ table1 <- CreateTableOne(vars = listVar, strata=c("Xpert2Outcome_num"), data = M
 tableType <- CreateTableOne(vars = listVar, strata=c("Radiology.Result"), data = MDF, factorVars = catVars)
 table1.all <- CreateTableOne(vars = listVar, data = MDF, factorVars = catVars)
 tablethistory <- CreateTableOne(vars = listVar, strata=c("TB.Medication.History"), data = MDF, factorVars = catVars)
+# 
+# 
+# #### p-value ---------
+# summary(table1$CatTable)
+# summary(table1$ContTable)
+# 
+# 
+# summary(tableType$CatTable)
+# summary(tableType$ContTable)
+# 
+# summary(tablethistory$CatTable)
+# summary(tablethistory$ContTable)
 
+
+
+#### ---------
 
 
 table1 <- print(table1, nonnormal = c("Age", "CAD4TB6", "qXRv3", "LunitScore", "JF1", "IF1", "IF2"), cramVars = "Gender", catDigits = 1, contDigits = 1, noSpaces = TRUE)
@@ -33,9 +47,12 @@ table1allDF <- data.frame(columnNameILike = row.names(table1all), table1all)
 tablethistory <- data.frame(columnNameILike = row.names(tablethistory), tablethistory)
 tabletypeDF <- data.frame(columnNameILike = row.names(tabletype), tabletype)
 
-T1 <- cbind(table1allDF, tablethistory, tabletypeDF)
+T1 <- cbind(table1allDF, table1DF, tablethistory, tabletypeDF)
+
 
 T1 <- T1[, c(1, 2, 5,4,6,10,9,11,14,16,15,17,18)]
+
[…]

### 2021-08-18 DataWrangling/Cleaning.R

@@ -167,7 +167,7 @@ rm(MDF_Delft_qxr, CAD6_delft, DelftClean, Lunit, Master_df, SymptomData, QA.BGD,
 
 ## Subset 
 # MDF <- subset(MDF, MDF$Age > 15)
-MDF <- subset(MDF, is.na(MDF$Xpert2Outcome_num)==F)
+# MDF <- subset(MDF, is.na(MDF$Xpert2Outcome_num)==F)
 MDF <- subset(MDF, is.na(MDF$CAD4TB6)==F)
 MDF <- subset(MDF, is.na(MDF$qXRv3)==F)
 MDF <- MDF[MDF$CAD4TB6 !="-1",]
@@ -199,7 +199,7 @@ table(MDF$UseCase)
 
 #### Save  -----------------------
 # write.csv(MDF, "DataWrangling/MDF.csv", row.names = F)
-write.csv(MDF, "DataWrangling/MDF.6.3.csv", row.names = F)
+# write.csv(MDF, "DataWrangling/MDF.6.3.csv", row.names = F)
 rm(Classification_ZZ, Referral, Master_df)
 
 

### 2021-08-18 DataWrangling/GlobalOption.R

@@ -35,8 +35,8 @@ MDF <- read.csv("DataWrangling/MDF.6.3.csv")
 # RM <- RM[1:48, ]
 # MDF <- MDF[!MDF$PID_OMRS %in% RM$PID_OMRS, ]
 
-summary(MDF$UseCase)
-
+table(MDF$UseCase)
+table(MDF$GXP.Result)
 
 # 
 # MDF <- MDF[!MDF$UseCase %in% c("Community screening", "Contacts"), ]
